---
title: "kidney_disease_60plus"
author: "Gabriel Burcea"
date: "14/09/2020"
output: word_document
---
```{r  include=FALSE, echo=TRUE}

library(tidyverse)
library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(qgraph)
library(report)
library(corrplot)
library(rms)

conflict_prefer("step", "stats")

### ML for Mixed - categorical and numerica data ####

```



```{r sympt-pos}

data_categ_nosev <- readr::read_csv("/Users/gabrielburcea/rprojects/data/your.md/cleaned_data_18_08_2020_fully_cleaned_uniq_comorb.csv")


covid_tested_levels <- c("positive" = "showing symptoms")

data_age_band <- data_categ_nosev %>%
   dplyr::mutate(age_band = dplyr::case_when(
     age == 0 | age <= 19 ~ '0-19',
     age == 20 | age <= 39 ~ '20-39',
     age == 40 | age <= 59 ~ '40-59',
     age >= 60 ~ "60+")) %>%
  dplyr::filter(number_morbidities <= 1) %>%
  dplyr::mutate(covid_tested = forcats::fct_recode(covid_tested, !!!covid_tested_levels))


data_covid_only <- data_age_band %>%
#dplyr::filter(number_morbidities <= 1) %>% # added this line on the 09/09/2020 as I want to check the analysis - do I get a different output, See report delivered  ...  compare this with the previous report generated on the date ....
  dplyr::select(id, age, gender, covid_tested, chills, cough, diarrhoea, fatigue, headache, loss_smell_taste, muscle_ache,
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, loss_appetite, chest_pain, itchy_eyes, joint_pain, 
                asthma, diabetes_type_one, diabetes_type_two, obesity, hypertension, heart_disease, lung_condition, liver_disease, kidney_disease, age_band, number_morbidities)%>% 
  dplyr::filter(covid_tested != "negative") %>%
  tidyr::drop_na()


data_age <- data_covid_only %>% 
  dplyr::filter(age_band == "60+")


data_categ_covid <- data_age %>%
  #dplyr::filter(number_morbidities <= 1) %>% # added this line on the 09/09/2020 as I want to check the analysis - do I get a different output, See report delivered  ...  compare this with the previous report generated on the date ....
 dplyr::select(id, age, gender, covid_tested, chills, cough, diarrhoea, fatigue, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, loss_appetite, chest_pain, itchy_eyes, joint_pain, 
                asthma, diabetes_type_one, diabetes_type_two, obesity, hypertension, heart_disease, lung_condition, liver_disease, kidney_disease) %>%
  dplyr::filter(covid_tested != "negative") %>%
  tidyr::drop_na()


```



```{r}
data_categ_covid$country <- NULL
data_categ_covid$location <- NULL
data_categ_covid$date_completed <- NULL
data_categ_covid$covid_tested <- NULL 
data_categ_covid$age_band <- NULL
data_categ_covid$status_cv <- NULL
data_categ_covid$sneezing <- NULL


###########################################################################################
### Transforming variables in factor format ###############################################
#data_categ_covid$country <- as.factor(data_categ_covid$country)
data_categ_covid$chills <- as.factor(data_categ_covid$chills)
data_categ_covid$cough  <- as.factor(data_categ_covid$cough)
data_categ_covid$gender <- as.factor(data_categ_covid$gender)
#data_categ_covid$covid_tested <- as.factor(data_categ_covid$covid_tested)
data_categ_covid$diarrhoea  <- as.factor(data_categ_covid$diarrhoea)
data_categ_covid$fatigue  <- as.factor(data_categ_covid$fatigue)
data_categ_covid$headache   <- as.factor(data_categ_covid$headache)
data_categ_covid$loss_smell_taste   <- as.factor(data_categ_covid$loss_smell_taste)
data_categ_covid$muscle_ache  <- as.factor(data_categ_covid$muscle_ache)
data_categ_covid$nasal_congestion <- as.factor(data_categ_covid$nasal_congestion)
data_categ_covid$nausea_vomiting  <- as.factor(data_categ_covid$nausea_vomiting)
#data_categ_covid$self_diagnosis <- as.factor(data_categ_covid$self_diagnosis)
data_categ_covid$shortness_breath <- as.factor(data_categ_covid$shortness_breath)
data_categ_covid$sore_throat <- as.factor(data_categ_covid$sore_throat)
data_categ_covid$sputum <- as.factor(data_categ_covid$sputum)
data_categ_covid$temperature  <- as.factor(data_categ_covid$temperature)
data_categ_covid$loss_appetite <- as.factor(data_categ_covid$loss_appetite)
data_categ_covid$chest_pain <- as.factor(data_categ_covid$chest_pain)
data_categ_covid$itchy_eyes <- as.factor(data_categ_covid$itchy_eyes)
data_categ_covid$joint_pain <- as.factor(data_categ_covid$joint_pain)


### Transforming variables in numerical format  #########################################################
data_categ_covid$asthma   <- as.factor(data_categ_covid$asthma)
data_categ_covid$diabetes_type_two <- as.factor(data_categ_covid$diabetes_type_two)
data_categ_covid$obesity <- as.factor(data_categ_covid$obesity)
data_categ_covid$hypertension  <- as.factor(data_categ_covid$hypertension)
data_categ_covid$heart_disease  <- as.factor(data_categ_covid$heart_disease)
data_categ_covid$kidney_disease <- as.factor(data_categ_covid$kidney_disease)
data_categ_covid$lung_condition <- as.factor(data_categ_covid$lung_condition)
data_categ_covid$liver_disease <- as.factor(data_categ_covid$liver_disease)
data_categ_covid$diabetes_type_one <- as.factor(data_categ_covid$diabetes_type_one)
#data_categ_covid$covid_tested <- as.factor(data_categ_nose)
```



```{r}
kidney_disease_data <- data_categ_covid %>%
  dplyr::select(kidney_disease, chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, chest_pain, joint_pain, loss_appetite, itchy_eyes) %>%
  tidyr::drop_na()
```


```{r}
kidney_count <- kidney_disease_data %>%
  tidyr::pivot_longer(cols = 2:17, 
                      names_to = "symptoms", 
                      values_to = "yes_no") %>%
  dplyr::filter(kidney_disease == "Yes" & yes_no == "Yes") %>%
  dplyr::group_by(symptoms) %>%
  dplyr::tally() %>%
  dplyr::mutate(Percentage = n/sum(n)) %>%
  dplyr::arrange(desc(n))

start_date = as.Date("2020-04-09", tz = "Europe/London")
end_date = as.Date("2020-08-18")
title_stub <- "Age Group 60+: Kidney disease across symptoms\n"
start_date_title <- format(as.Date(start_date), format = "%d %B %Y")
end_date_title <- format(as.Date(end_date), format = "%d %B %Y")
chart_title <- paste0(title_stub, start_date_title, " to ", end_date_title)

plot_kidney_sympt <-
  ggplot2::ggplot(kidney_count, ggplot2::aes(x = reorder(symptoms, - Percentage), y = n, fill = n)) +
  ggplot2::coord_flip() +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::scale_fill_viridis_c(option = "magma", direction = -1) +
  ggplot2::scale_x_discrete(limits = unique(kidney_count$symptoms)) +
  #ggplot2::theme(legend.position = "bottom") +
  #ggplot2::guides(fill = ggplot2::guide_legend(nrow = 3)) +
  ggplot2::theme_minimal() +
  ggplot2::labs( title = chart_title,
                 subtitle = "Counts of patients with comorbidities accross symptoms",
                 y = "Counts",
                 x = "Symptoms",
                 caption = "Source: Dataset - Your.md Dataset") +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(margin = ggplot2::margin(
      t = 0,
      r = 21,
      b = 0,
      l = 0
    )),
    plot.title = ggplot2::element_text(size = 10, face = "bold"),
    plot.subtitle = ggplot2::element_text(size = 9),
    axis.text.x = ggplot2::element_text(angle = 55, hjust = 1)
  )

plot_kidney_sympt
```

# Univariate analysis for kidney disease and Covid-19 symptoms

The most Covid symptoms that are associated with kidney disease are shorthness and breath and temperature.


1. Kidney disease and chills


```{r }



kidney_disease_data$kidney_disease <- as.factor(kidney_disease_data$kidney_disease)
kidney_disease_chills <- glm(kidney_disease ~ chills, data = kidney_disease_data, family = binomial)

summary(kidney_disease_chills)


```



```{r}
coef_kidney_disease_chills <- coef(kidney_disease_chills)


```


```{r}
kidney_disease_chills_or_ci <- exp(cbind(OR = coef(kidney_disease_chills), confint(kidney_disease_chills)))
```



P-values adjusted 

```{r}
kidney_disease_chills_pval <- summary(kidney_disease_chills)$coefficients[,4]

kidney_disease_chills_pval <- kidney_disease_chills_pval[-1]

kidney_disease_chills_padj <- p.adjust(kidney_disease_chills_pval, method = "bonferroni")

kidney_disease_chills_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_chills_or_ci_pval <- cbind(kidney_disease_chills_or_ci, data.frame(pvalues = kidney_disease_chills_padj))

knitr::kable(kidney_disease_chills_or_ci_pval)
```


```{r pressure, echo=FALSE}
kidney_disease_cough <- glm(kidney_disease ~ cough, data = kidney_disease_data, family = binomial)

summary(kidney_disease_cough)


coef_kidney_disease_cough <- coef(kidney_disease_cough)

odd_ratios_ob_co <- exp(coef_kidney_disease_cough)

odd_ratios_ob_co 
```


```{r}
kidney_disease_cough_or_ci <- exp(cbind(OR = coef(kidney_disease_cough), confint(kidney_disease_cough)))
```




P-values adjusted 

```{r}
kidney_disease_cough_pval <- summary(kidney_disease_cough)$coefficients[,4]

kidney_disease_cough_pval <- kidney_disease_cough_pval[-1]

kidney_disease_cough_padj <- p.adjust(kidney_disease_cough_pval, method = "bonferroni")

kidney_disease_cough_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_cough_or_ci_pval <- cbind(kidney_disease_cough_or_ci, data.frame(pvalues = kidney_disease_cough_padj))

knitr::kable(kidney_disease_cough_or_ci_pval)
```




```{r}
kidney_disease_diarrhea <- glm(kidney_disease ~ diarrhoea, data = kidney_disease_data, family = binomial)

summary(kidney_disease_diarrhea)


# get coef
coef_ob_diarrhea <- coef(kidney_disease_diarrhea)

# odd ratios
odd_ratio_ob_diar <- exp(coef_ob_diarrhea)

odd_ratio_ob_diar
```


```{r}
kidney_disease_diarrhea_or_ci <- exp(cbind(OR = coef(kidney_disease_diarrhea), confint(kidney_disease_diarrhea)))
```


P-values adjusted 

```{r}
kidney_disease_diarrhea_pval <- summary(kidney_disease_diarrhea)$coefficients[,4]

kidney_disease_diarrhea_pval <- kidney_disease_diarrhea_pval[-1]

kidney_disease_diarrhea_padj <- p.adjust(kidney_disease_diarrhea_pval, method = "bonferroni")

kidney_disease_diarrhea_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_diarrhea_or_ci_pval <- cbind(kidney_disease_diarrhea_or_ci, data.frame(pvalues = kidney_disease_diarrhea_padj))

knitr::kable(kidney_disease_diarrhea_or_ci_pval)
```




```{r}
kidney_disease_headache <- glm(kidney_disease ~ headache, data = kidney_disease_data, family = binomial)

summary(kidney_disease_headache)

```

OR and CI 
```{r}
kidney_disease_headache_or_ci <- exp(cbind(OR = coef(kidney_disease_headache), confint(kidney_disease_headache)))
```



P-values adjusted 

```{r}
kidney_disease_headache_pval <- summary(kidney_disease_headache)$coefficients[,4]

kidney_disease_headache_pval <- kidney_disease_headache_pval[-1]

kidney_disease_headache_padj <- p.adjust(kidney_disease_headache_pval, method = "bonferroni")

kidney_disease_headache_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_headache_or_ci_pval <- cbind(kidney_disease_headache_or_ci, data.frame(pvalues = kidney_disease_headache_padj))

knitr::kable(kidney_disease_headache_or_ci_pval)
```






```{r}

kidney_disease_loss_smell <- glm(kidney_disease ~ loss_smell_taste, data = kidney_disease_data, family = binomial)


summary(kidney_disease_loss_smell)


```


OR and CI 
```{r}
kidney_disease_loss_smell_or_ci <-    exp(cbind(OR = coef(kidney_disease_loss_smell), confint(kidney_disease_loss_smell)))
```





```{r}
kidney_disease_loss_smell_pval <- summary(kidney_disease_loss_smell)$coefficients[,4]

kidney_disease_loss_smell_pval <- kidney_disease_loss_smell_pval[-1]

kidney_disease_loss_smell_padj <- p.adjust(kidney_disease_loss_smell_pval, method = "bonferroni")

kidney_disease_loss_smell_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_loss_smell_or_ci_pval <- cbind(kidney_disease_loss_smell_or_ci, data.frame(pvalues = kidney_disease_loss_smell_padj))

knitr::kable(kidney_disease_loss_smell_or_ci_pval)
```





```{r}
library(fmsb)

kidney_disease_muscle_ache <- glm(kidney_disease ~ muscle_ache, data = kidney_disease_data, family = binomial)
 
summary(kidney_disease_muscle_ache)




coef_ob_muscle_ac <- coef(kidney_disease_muscle_ache)

odd_ratio_ob_los <- exp(coef_ob_muscle_ac)

odd_ratio_ob_los

```


OR and CI 
```{r}
kidney_disease_muscle_ache_or_ci <- exp(cbind(OR = coef(kidney_disease_muscle_ache), confint(kidney_disease_muscle_ache)))
```




```{r}
kidney_disease_muscle_ache_pval <- summary(kidney_disease_muscle_ache)$coefficients[,4]

kidney_disease_muscle_ache_pval <- kidney_disease_muscle_ache_pval[-1]

kidney_disease_muscle_ache_padj <- p.adjust(kidney_disease_muscle_ache_pval, method = "bonferroni")

kidney_disease_muscle_ache_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_muscle_ache_or_ci_pval <- cbind(kidney_disease_muscle_ache_or_ci, data.frame(pvalues = kidney_disease_muscle_ache_padj))

knitr::kable(kidney_disease_muscle_ache_or_ci_pval)
```



```{r}

kidney_disease_nasal_cong <- glm(kidney_disease ~ nasal_congestion, data = kidney_disease_data, family = binomial)

summary(kidney_disease_nasal_cong)


coef_ob_nas_cong <- coef(kidney_disease_nasal_cong)

odd_ratio_ob_nas_cong <- exp(coef_ob_nas_cong)

odd_ratio_ob_nas_cong
```



OR and CI 
```{r}
kidney_disease_nasal_cong_or_ci <- exp(cbind(OR = coef(kidney_disease_nasal_cong), confint(kidney_disease_nasal_cong)))
```



```{r}
kidney_disease_nasal_cong_pval <- summary(kidney_disease_nasal_cong)$coefficients[,4]

kidney_disease_nasal_cong_pval <- kidney_disease_nasal_cong_pval[-1]

kidney_disease_nasal_cong_padj <- p.adjust(kidney_disease_nasal_cong_pval, method = "bonferroni")

kidney_disease_nasal_cong_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_nasal_cong_or_ci_pval <- cbind(kidney_disease_nasal_cong_or_ci, data.frame(pvalues = kidney_disease_nasal_cong_padj))

knitr::kable(kidney_disease_nasal_cong_or_ci_pval)
```




```{r}

kidney_disease_nausea_vomitting <- glm(kidney_disease ~ nausea_vomiting, data = kidney_disease_data, family = binomial)

summary(kidney_disease_nausea_vomitting)


coef_ob_naus_vom <- coef(kidney_disease_nausea_vomitting)

odd_ratio_ob_naus_vom <- exp(coef_ob_naus_vom)

odd_ratio_ob_naus_vom
```


OR and CI 
```{r}
kidney_disease_nausea_vomitting_or_ci <- exp(cbind(OR = coef(kidney_disease_nausea_vomitting), confint(kidney_disease_nausea_vomitting)))
```



```{r}
kidney_disease_nausea_vomitting_pval <- summary(kidney_disease_nausea_vomitting)$coefficients[,4]

kidney_disease_nausea_vomitting_pval <- kidney_disease_nausea_vomitting_pval[-1]

kidney_disease_nausea_vomitting_padj <- p.adjust(kidney_disease_nausea_vomitting_pval, method = "bonferroni")

kidney_disease_nausea_vomitting_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_nausea_vomitting_or_ci_pval <- cbind(kidney_disease_nausea_vomitting_or_ci, data.frame(pvalues = kidney_disease_nausea_vomitting_padj))

knitr::kable(kidney_disease_nausea_vomitting_or_ci_pval)
```





```{r}

kidney_disease_short_breath <- glm(kidney_disease ~ shortness_breath, data = kidney_disease_data, family = binomial)

summary(kidney_disease_short_breath)


```


OR and CI 
```{r}
kidney_disease_short_breath_or_ci <- exp(cbind(OR = coef(kidney_disease_short_breath), confint(kidney_disease_short_breath)))
```




```{r}
kidney_disease_short_breath_pval <- summary(kidney_disease_short_breath)$coefficients[,4]

kidney_disease_short_breath_pval <- kidney_disease_short_breath_pval[-1]

kidney_disease_short_breath_padj <- p.adjust(kidney_disease_short_breath_pval, method = "bonferroni")

kidney_disease_short_breath_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_short_breath_or_ci_pval <- cbind(kidney_disease_short_breath_or_ci, data.frame(pvalues = kidney_disease_short_breath_padj))

knitr::kable(kidney_disease_short_breath_or_ci_pval)
```







```{r}

kidney_disease_sore_thr <- glm(kidney_disease ~ sore_throat, data = kidney_disease_data, family = binomial)

summary(kidney_disease_sore_thr)

```



OR and CI 
```{r}
kidney_disease_sore_thr_or_ci <- exp(cbind(OR = coef(kidney_disease_sore_thr), confint(kidney_disease_sore_thr)))
```




```{r}
kidney_disease_sore_thr_pval <- summary(kidney_disease_sore_thr)$coefficients[,4]

kidney_disease_sore_thr_pval <- kidney_disease_sore_thr_pval[-1]

kidney_disease_sore_thr_padj <- p.adjust(kidney_disease_sore_thr_pval, method = "bonferroni")

kidney_disease_sore_thr_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_sore_thr_or_ci_pval <- cbind(kidney_disease_sore_thr_or_ci, data.frame(pvalues = kidney_disease_sore_thr_padj))

knitr::kable(kidney_disease_sore_thr_or_ci_pval)
```






```{r}
kidney_disease_sputum <- glm(kidney_disease ~ sputum, data = kidney_disease_data, family = binomial)


summary(kidney_disease_sputum)


```



OR and CI 
```{r}
kidney_disease_sputum_or_ci <- exp(cbind(OR = coef(kidney_disease_sputum), confint(kidney_disease_sputum)))
```




```{r}
kidney_disease_sputum_pval <- summary(kidney_disease_sputum)$coefficients[,4]

kidney_disease_sputum_pval <- kidney_disease_sputum_pval[-1]

kidney_disease_sputum_padj <- p.adjust(kidney_disease_sputum_pval, method = "bonferroni")

kidney_disease_sputum_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_sputum_or_ci_pval <- cbind(kidney_disease_sputum_or_ci, data.frame(pvalues = kidney_disease_sputum_padj))

knitr::kable(kidney_disease_sputum_or_ci_pval)
```


```{r}
kidney_disease_temperature <- glm(kidney_disease ~ temperature, data = kidney_disease_data, family = binomial)


summary(kidney_disease_temperature)


```



OR and CI 
```{r}
kidney_disease_temperature_or_ci <- exp(cbind(OR = coef(kidney_disease_temperature), confint(kidney_disease_temperature)))
```




```{r}
kidney_disease_temperature_pval <- summary(kidney_disease_temperature)$coefficients[,4]

kidney_disease_temperature_pval <- kidney_disease_temperature_pval[-1]

kidney_disease_temperature_padj <- p.adjust(kidney_disease_temperature_pval, method = "bonferroni")

kidney_disease_temperature_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_temperature_or_ci_pval <- cbind(kidney_disease_temperature_or_ci, data.frame(pvalues = kidney_disease_temperature_padj))

knitr::kable(kidney_disease_temperature_or_ci_pval)
```



```{r, itchy_eyes}
kidney_disease_itchy_eyes <- glm(kidney_disease ~ itchy_eyes, data = kidney_disease_data, family = binomial)

summary(kidney_disease_itchy_eyes)

```



OR and CI 
```{r}
kidney_disease_itchy_eyes_or_ci <- exp(cbind(OR = coef(kidney_disease_itchy_eyes), confint(kidney_disease_itchy_eyes)))
```



```{r}
kidney_disease_itchy_eyes_pval <- summary(kidney_disease_itchy_eyes)$coefficients[,4]

kidney_disease_itchy_eyes_pval <- kidney_disease_itchy_eyes_pval[-1]

kidney_disease_itchy_eyes_padj <- p.adjust(kidney_disease_itchy_eyes_pval, method = "bonferroni")

kidney_disease_itchy_eyes_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_itchy_eyes_or_ci_pval <- cbind(kidney_disease_itchy_eyes_or_ci, data.frame(pvalues = kidney_disease_itchy_eyes_padj))

knitr::kable(kidney_disease_itchy_eyes_or_ci_pval)
```



```{r, chest_pain}
kidney_disease_chest_pain <- glm(kidney_disease ~ chest_pain, data = kidney_disease_data, family = binomial)

summary(kidney_disease_chest_pain)
```

OR and CI 
```{r}
kidney_disease_chest_pain_or_ci <- exp(cbind(OR = coef(kidney_disease_chest_pain), confint(kidney_disease_chest_pain)))
```




```{r}
kidney_disease_chest_pain_pval <- summary(kidney_disease_chest_pain)$coefficients[,4]

kidney_disease_chest_pain_pval <- kidney_disease_chest_pain_pval[-1]

kidney_disease_chest_pain_padj <- p.adjust(kidney_disease_chest_pain_pval, method = "bonferroni")

kidney_disease_chest_pain_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_chest_pain_or_ci_pval <- cbind(kidney_disease_chest_pain_or_ci, data.frame(pvalues = kidney_disease_chest_pain_padj))

knitr::kable(kidney_disease_chest_pain_or_ci_pval)
```



```{r}
kidney_disease_loss_appetite <- glm(kidney_disease ~ loss_appetite, data = kidney_disease_data, family = binomial)

summary(kidney_disease_loss_appetite)
```


OR and CI 
```{r}
kidney_disease_loss_appetite_or_ci <- exp(cbind(OR = coef(kidney_disease_loss_appetite), confint(kidney_disease_loss_appetite)))
```




```{r}
kidney_disease_loss_appetite_pval <- summary(kidney_disease_loss_appetite)$coefficients[,4]

kidney_disease_loss_appetite_pval <- kidney_disease_loss_appetite_pval[-1]

kidney_disease_loss_appetite_padj <- p.adjust(kidney_disease_loss_appetite_pval, method = "bonferroni")

kidney_disease_loss_appetite_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_loss_appetite_or_ci_pval <- cbind(kidney_disease_loss_appetite_or_ci, data.frame(pvalues = kidney_disease_loss_appetite_padj))

knitr::kable(kidney_disease_loss_appetite_or_ci_pval)
```








```{r, joint_pain}
kidney_disease_joint_pain <- glm(kidney_disease ~ joint_pain, data = kidney_disease_data, family = binomial)


summary(kidney_disease_joint_pain)
```


OR and CI 
```{r}
kidney_disease_joint_pain_or_ci <- exp(cbind(OR = coef(kidney_disease_joint_pain), confint(kidney_disease_joint_pain)))
```



```{r}
kidney_disease_joint_pain_pval <- summary(kidney_disease_joint_pain)$coefficients[,4]

kidney_disease_joint_pain_pval <- kidney_disease_joint_pain_pval[-1]

kidney_disease_joint_pain_padj <- p.adjust(kidney_disease_joint_pain_pval, method = "bonferroni")

kidney_disease_joint_pain_padj
```


OR, CI and pval adjusted  
```{r}

kidney_disease_joint_pain_or_ci_pval <- cbind(kidney_disease_joint_pain_or_ci, data.frame(pvalues = kidney_disease_joint_pain_padj))

knitr::kable(kidney_disease_joint_pain_or_ci_pval)
```


# Multivariate analysis for Kidney disease

The selected variables for the final model are: shortness of breath, temperature. 

In patients showing covid-19 symptoms/of patients with a positive covid test,when adjusting for all relevant variables, in respondents with kidney disease there was a: 
- 64% increase in the odds of experiencing shortness of breaht compared to those who do not have kidney disease 
- 33 % increase in the odds of experiencing 38.1 -39 temperature compared to those who do not have kidney disease
- 305 % ?? not sure - increase in odds of experiencing 39.1-41 temperature compared to those who do not have kidney disease

```{r}
kidney_model <- glm(kidney_disease ~  chills + diarrhoea + temperature + chest_pain + loss_appetite, data = kidney_disease_data, family = binomial)

summary(kidney_model)
```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_model), confint(kidney_model))))
```





```{r}
# odds ratio and 95% CL

kidney_model_or_ci <- exp(cbind(OR = coef(kidney_model), confint(kidney_model)))

kidney_model_or_ci
```



```{r}
kidney_model_pval <- summary(kidney_model)$coefficients[,4]



kidney_model_padj <- p.adjust(kidney_model_pval, method = "bonferroni")

kidney_model_padj
```


OR, CI and pval adjusted  
```{r}

kidney_model_or_ci_pval <- cbind(kidney_model_or_ci, data.frame(pvalues = kidney_model_padj))

knitr::kable(kidney_model_or_ci_pval)
```




Multicolinearity
```{r}
vif(kidney_model)
```


