---
title: "asthma_18_08_2020_data"
author: "Gabriel Burcea"
date: "10/09/2020"
output: word_document
---

```{r  include=FALSE, echo=TRUE}

library(tidyverse)
library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(qgraph)
library(report)
library(corrplot)
library(rms)

conflict_prefer("step", "stats")

### ML for Mixed - categorical and numerica data ####

```



```{r sympt-pos}

data_categ_nosev <- readr::read_csv("/Users/gabrielburcea/rprojects/data/your.md/cleaned_data_18_08_2020_fully_cleaned_uniq_comorb.csv")

data_categ_covid <- data_categ_nosev %>%
  #dplyr::filter(number_morbidities <= 1) %>% # added this line on the 09/09/2020 as I want to check the analysis - do I get a different output, See report delivered  ...  compare this with the previous report generated on the date ....
 dplyr::select(id, age, gender, covid_tested, chills, cough, diarrhoea, fatigue, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, loss_appetite, chest_pain, itchy_eyes, joint_pain, 
                asthma, diabetes_type_one, diabetes_type_two, obesity, hypertension, heart_disease, lung_condition, liver_disease, kidney_disease) %>%
  dplyr::filter(covid_tested != "negative") %>%
  tidyr::drop_na()

covid_tested_levels <- c("positive" = "showing symptoms")

data_transf <- data_select %>% 
  dplyr::mutate(covid_tested = forcats::fct_recode(covid_tested, !!!covid_tested_levels))
```



```{r}
data_categ_covid$country <- NULL
data_categ_covid$location <- NULL
data_categ_covid$date_completed <- NULL
data_categ_covid$covid_tested <- NULL 
data_categ_covid$age_band <- NULL
data_categ_covid$status_cv <- NULL
data_categ_covid$sneezing <- NULL


###########################################################################################
### Transforming variables in factor format ###############################################
#data_categ_covid$country <- as.factor(data_categ_covid$country)
data_categ_covid$chills <- as.factor(data_categ_covid$chills)
data_categ_covid$cough  <- as.factor(data_categ_covid$cough)
data_categ_covid$gender <- as.factor(data_categ_covid$gender)
#data_categ_covid$covid_tested <- as.factor(data_categ_covid$covid_tested)
data_categ_covid$diarrhoea  <- as.factor(data_categ_covid$diarrhoea)
data_categ_covid$fatigue  <- as.factor(data_categ_covid$fatigue)
data_categ_covid$headache   <- as.factor(data_categ_covid$headache)
data_categ_covid$loss_smell_taste   <- as.factor(data_categ_covid$loss_smell_taste)
data_categ_covid$muscle_ache  <- as.factor(data_categ_covid$muscle_ache)
data_categ_covid$nasal_congestion <- as.factor(data_categ_covid$nasal_congestion)
data_categ_covid$nausea_vomiting  <- as.factor(data_categ_covid$nausea_vomiting)
#data_categ_covid$self_diagnosis <- as.factor(data_categ_covid$self_diagnosis)
data_categ_covid$shortness_breath <- as.factor(data_categ_covid$shortness_breath)
data_categ_covid$sore_throat <- as.factor(data_categ_covid$sore_throat)
data_categ_covid$sputum <- as.factor(data_categ_covid$sputum)
data_categ_covid$temperature  <- as.factor(data_categ_covid$temperature)
data_categ_covid$loss_appetite <- as.factor(data_categ_covid$loss_appetite)
data_categ_covid$chest_pain <- as.factor(data_categ_covid$chest_pain)
data_categ_covid$itchy_eyes <- as.factor(data_categ_covid$itchy_eyes)
data_categ_covid$joint_pain <- as.factor(data_categ_covid$joint_pain)


### Transforming variables in numerical format  #########################################################
data_categ_covid$asthma   <- as.factor(data_categ_covid$asthma)
data_categ_covid$diabetes_type_two <- as.factor(data_categ_covid$diabetes_type_two)
data_categ_covid$obesity <- as.factor(data_categ_covid$obesity)
data_categ_covid$hypertension  <- as.factor(data_categ_covid$hypertension)
data_categ_covid$heart_disease  <- as.factor(data_categ_covid$heart_disease)
data_categ_covid$kidney_disease <- as.factor(data_categ_covid$kidney_disease)
data_categ_covid$lung_condition <- as.factor(data_categ_covid$lung_condition)
data_categ_covid$liver_disease <- as.factor(data_categ_covid$liver_disease)
data_categ_covid$diabetes_type_one <- as.factor(data_categ_covid$diabetes_type_one)
#data_categ_covid$covid_tested <- as.factor(data_categ_nose)
```


```{r}
asthma_data <- data_categ_covid %>%
  dplyr::select(asthma, chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, loss_appetite, chest_pain, itchy_eyes, joint_pain) %>%
  tidyr::drop_na()
```


```{r}
asthma_count <- asthma_data %>%
  tidyr::pivot_longer(cols = 2:17, 
                      names_to = "symptoms", 
                      values_to = "yes_no") %>%
  dplyr::filter(asthma == "Yes" & yes_no == "Yes") %>%
  dplyr::group_by(symptoms) %>%
  dplyr::tally() %>%
  dplyr::mutate(Percentage = n/sum(n)) %>%
  dplyr::arrange(desc(n))

start_date = as.Date("2020-04-09", tz = "Europe/London")
end_date = as.Date("2020-08-18")
title_stub <- "Asthma across symptoms\n"
start_date_title <- format(as.Date(start_date), format = "%d %B %Y")
end_date_title <- format(as.Date(end_date), format = "%d %B %Y")
chart_title <- paste0(title_stub, start_date_title, " to ", end_date_title)

plot_asthma_sympt <-
  ggplot2::ggplot(asthma_count, ggplot2::aes(x = reorder(symptoms, - Percentage), y = n, fill = n)) +
  ggplot2::coord_flip() +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::scale_fill_viridis_c(option = "magma", direction = -1) +
  ggplot2::scale_x_discrete(limits = unique(asthma_count$symptoms)) +
  #ggplot2::theme(legend.position = "bottom") +
  #ggplot2::guides(fill = ggplot2::guide_legend(nrow = 3)) +
  ggplot2::theme_minimal() +
  ggplot2::labs( title = chart_title,
                 subtitle = "Counts of patients with comorbidities accross symptoms",
                 y = "Counts",
                 x = "Symptoms",
                 caption = "Source: Dataset - Your.md Dataset") +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(margin = ggplot2::margin(
      t = 0,
      r = 21,
      b = 0,
      l = 0
    )),
    plot.title = ggplot2::element_text(size = 10, face = "bold"),
    plot.subtitle = ggplot2::element_text(size = 9),
    axis.text.x = ggplot2::element_text(angle = 55, hjust = 1)
  )

plot_asthma_sympt
```




## Univariate analysis for asthma

Unvivariate analysis reveal chills, cough, diarrhea, headache, muschle ache, sore throat, nausea and vomiting, shortness of breath, sputum, temperature are the associated Covid symptoms in respondents with asthma. 


1. Asthma and chills
```{r asthma-chills}

asthma_data <- asthma_data %>% drop_na()

asthma_chills <- glm(asthma ~ chills, data = asthma_data, family = binomial)

summary(asthma_chills)


coef_asthma_chills <- coef(asthma_chills)

# odd ratios 
odd_ratios_ob_ch <- exp(coef_asthma_chills)
odd_ratios_ob_ch 

```

```{r}
knitr::kable(exp(cbind(OR = coef(asthma_chills), confint(asthma_chills))))
```


2. Asthma and cough
```{r asthma_cough, echo=FALSE}
asthma_cough <- glm(asthma ~ cough, data = asthma_data, family = binomial)

summary(asthma_cough)
```


```{r}
knitr::kable(exp(cbind(OR = coef(asthma_cough), confint(asthma_cough))))
```






3. Asthma and diarrhea
```{r asthma_diarrhea}
asthma_diarrhea <- glm(asthma ~ diarrhoea, data = asthma_data, family = binomial)

summary(asthma_diarrhea)
```

```{r}
knitr::kable(exp(cbind(OR = coef(asthma_diarrhea), confint(asthma_diarrhea))))
```




4. Asthma and headache

```{r asthma_headache}
asthma_headache <- glm(asthma ~ headache, data = asthma_data, family = binomial)

summary(asthma_headache)

```



```{r}
knitr::kable(exp(cbind(OR = coef(asthma_headache), confint(asthma_headache))))
```



5. Asthma and loss of smell and taste


```{r asthma_loss_smell}

asthma_loss_smell <- glm(asthma ~ loss_smell_taste, data = asthma_data, family = binomial)


summary(asthma_loss_smell)

```


```{r}
knitr::kable(exp(cbind(OR = coef(asthma_loss_smell), confint(asthma_loss_smell))))
```




6. Asthma and muscle ache

```{r asthma_muscle_ache}


asthma_muscle_ache <- glm(asthma ~ muscle_ache, data = asthma_data, family = binomial)
 
summary(asthma_muscle_ache)


```


```{r}
knitr::kable(exp(cbind(OR = coef(asthma_muscle_ache), confint(asthma_muscle_ache))))
```







7. Asthma and nasal congestion

```{r asthma_nasal_cong }

asthma_nasal_cong <- glm(asthma ~ nasal_congestion, data = asthma_data, family = binomial)

summary(asthma_nasal_cong)

```


```{r}
knitr::kable(exp(cbind(OR = coef(asthma_nasal_cong), confint(asthma_nasal_cong))))
```




8. Athma and nausea and vomiting 
```{r asthma_nausea_vomitting}

asthma_nausea_vomitting <- glm(asthma ~ nausea_vomiting, data = asthma_data, family = binomial)

summary(asthma_nausea_vomitting)
```


```{r}
knitr::kable(exp(cbind(OR = coef(asthma_nausea_vomitting), confint(asthma_nausea_vomitting))))
```








9. Asthma and shortness of breath

```{r asthma_short_breath}

asthma_short_breath <- glm(asthma ~ shortness_breath, data = asthma_data, family = binomial)

summary(asthma_short_breath)

coef_ob_sh_br <- coef(asthma_short_breath)


odd_ratio_ob_sh_br <- exp(coef_ob_sh_br)

odd_ratio_ob_sh_br
```

```{r}
knitr::kable(exp(cbind(OR = coef(asthma_short_breath), confint(asthma_short_breath))))
```


10. Asthma and sore throat

```{r asthma_sore_thr}

asthma_sore_thr <- glm(asthma ~ sore_throat, data = asthma_data, family = binomial)

summary(asthma_sore_thr)

```


```{r}
knitr::kable(exp(cbind(OR = coef(asthma_sore_thr), confint(asthma_sore_thr))))
```






11. Asthma and sputum 

```{r asthma_sputum, echo=FALSE}
asthma_sputum <- glm(asthma ~ sputum, data = asthma_data, family = binomial)


summary(asthma_sputum)

vif(asthma_sputum)
```


```{r}
knitr::kable(exp(cbind(OR = coef(asthma_sputum), confint(asthma_sputum))))
```







12. Asthma and temperature
```{r asthma_temperature, echo=FALSE}
asthma_temperature <- glm(asthma ~ temperature, data = asthma_data, family = binomial)

summary(asthma_temperature)

```



```{r}
knitr::kable(exp(cbind(OR = coef(asthma_temperature), confint(asthma_temperature))))
```



```{r}
asthma_itchy <- glm(asthma ~ itchy_eyes, data = asthma_data, family = binomial)

summary(asthma_temperature)

```



```{r}
knitr::kable(exp(cbind(OR = coef(asthma_itchy), confint(asthma_itchy))))
```






```{r}
asthma_joint_pain <- glm(asthma ~ joint_pain, data = asthma_data, family = binomial)

summary(asthma_joint_pain)
```


```{r}
knitr::kable(exp(cbind(OR = coef(asthma_joint_pain), confint(asthma_joint_pain))))
```






```{r}
asthma_chest_pain <- glm(asthma ~ chest_pain, data = asthma_data, family = binomial)

summary(asthma_chest_pain)
```


```{r}
knitr::kable(exp(cbind(OR = coef(asthma_chest_pain), confint(asthma_chest_pain))))
```






```{r}
asthma_loss_appetite <- glm(asthma ~ loss_appetite, data = asthma_data, family = binomial)


summary(asthma_loss_appetite)
```



```{r}

knitr::kable(exp(cbind(OR = coef(asthma_loss_appetite), confint(asthma_loss_appetite))))
```


# Multivariable Logistic Regression for Asthma


Adding all symptoms that showed to be associated in asthma patients. 

When adjusting for all variables,  patients showing covid-19 symptoms/of patients with positive covid test, the results show strong evidence for an association between variables such as chills, nausea and vomiting, shortness of breath and temperature (38.1-39; 39.1-40) (p ≤ 0.05) in patients with asthma.  

When adjusting for all variables,in patients showing covid-19 symptoms/of patients with positive covid test, in patients with asthma there was: 

- 160  % increase in shortness of breath compared to those who do not suffer of asthma
- 35 % increase in sputum 
- 107 % increase in 39.1-41 temperature compared to those who do not suffer of asthma
- 1 % increase in male patients compared to those at the baseline
- 1 % increase in age compared



```{r asthma_model, echo=FALSE}
asthma_model <- glm(asthma ~ chills + cough + diarrhoea + headache + muscle_ache + nausea_vomiting 
                    + shortness_breath + sputum +  nasal_congestion + sore_throat + itchy_eyes + joint_pain + chest_pain, data = asthma_data, family = binomial)

summary(asthma_model)
```


```{r}
knitr::kable(exp(cbind(OR = coef(asthma_model), confint(asthma_model))))
```


```{r}
vif(asthma_model)
```

