---
title: "Diabetes_type_one_18_08_2020_data"
author: "Gabriel Burcea"
date: "04/09/2020"
output: word_document
---



```{r  include=FALSE, echo=TRUE}


library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(qgraph)
library(report)
library(corrplot)
library(rms)

conflict_prefer("step", "stats")

### ML for Mixed - categorical and numerica data ####

```


```{r sympt-pos}

data_categ_nosev <- readr::read_csv("/Users/gabrielburcea/rprojects/data/your.md/cleaned_data_18_08_2020_fully_cleaned_uniq_comorb.csv")

data_categ_covid <- data_categ_nosev %>%
  dplyr::filter(covid_tested != 'none') %>%
  dplyr::mutate(status_cv = dplyr::case_when(covid_tested == 'showing symptoms' ~ 0,
                                             covid_tested == 'positive' ~ 1)) %>%
  tidyr::drop_na()



```

```{r}
data_categ_covid$country <- NULL
data_categ_covid$location <- NULL
data_categ_covid$date_completed <- NULL
data_categ_covid$covid_tested <- NULL 
data_categ_covid$age_band <- NULL
data_categ_covid$status_cv <- NULL
data_categ_covid$sneezing <- NULL


###########################################################################################
### Transforming variables in factor format ###############################################
#data_categ_covid$country <- as.factor(data_categ_covid$country)
data_categ_covid$chills <- as.factor(data_categ_covid$chills)
data_categ_covid$cough  <- as.factor(data_categ_covid$cough)
data_categ_covid$gender <- as.factor(data_categ_covid$gender)
#data_categ_covid$covid_tested <- as.factor(data_categ_covid$covid_tested)
data_categ_covid$diarrhoea  <- as.factor(data_categ_covid$diarrhoea)
data_categ_covid$fatigue  <- as.factor(data_categ_covid$fatigue)
data_categ_covid$headache   <- as.factor(data_categ_covid$headache)
data_categ_covid$loss_smell_taste   <- as.factor(data_categ_covid$loss_smell_taste)
data_categ_covid$muscle_ache  <- as.factor(data_categ_covid$muscle_ache)
data_categ_covid$nasal_congestion <- as.factor(data_categ_covid$nasal_congestion)
data_categ_covid$nausea_vomiting  <- as.factor(data_categ_covid$nausea_vomiting)
data_categ_covid$self_diagnosis <- as.factor(data_categ_covid$self_diagnosis)
data_categ_covid$shortness_breath <- as.factor(data_categ_covid$shortness_breath)
data_categ_covid$sore_throat <- as.factor(data_categ_covid$sore_throat)
data_categ_covid$sputum <- as.factor(data_categ_covid$sputum)
data_categ_covid$temperature  <- as.factor(data_categ_covid$temperature)
data_categ_covid$loss_appetite <- as.factor(data_categ_covid$loss_appetite)
data_categ_covid$chest_pain <- as.factor(data_categ_covid$chest_pain)
data_categ_covid$itchy_eyes <- as.factor(data_categ_covid$itchy_eyes)
data_categ_covid$joint_pain <- as.factor(data_categ_covid$joint_pain)


### Transforming variables in numerical format  #########################################################
data_categ_covid$asthma   <- as.factor(data_categ_covid$asthma)
data_categ_covid$diabetes_type_two <- as.factor(data_categ_covid$diabetes_type_two)
data_categ_covid$obesity <- as.factor(data_categ_covid$obesity)
data_categ_covid$hypertension  <- as.factor(data_categ_covid$hypertension)
data_categ_covid$heart_disease  <- as.factor(data_categ_covid$heart_disease)
data_categ_covid$kidney_disease <- as.factor(data_categ_covid$kidney_disease)
data_categ_covid$lung_condition <- as.factor(data_categ_covid$lung_condition)
data_categ_covid$liver_disease <- as.factor(data_categ_covid$liver_disease)
data_categ_covid$diabetes_type_one <- as.factor(data_categ_covid$diabetes_type_one)
#data_categ_covid$covid_tested <- as.factor(data_categ_nose)
```


```{r}
diabetes_type_one_data <- data_categ_covid %>%
  dplyr::select(diabetes_type_one, chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, joint_pain, itchy_eyes, chest_pain, loss_appetite)


diab_t <- table(diabetes_type_one_data$diabetes_type_one)

diab_t
```






```{r}

diabetes_count <- diabetes_type_one_data %>%
  tidyr::pivot_longer(cols = 2:17, 
                      names_to = "symptoms", 
                      values_to = "yes_no") %>%
  dplyr::filter(diabetes_type_one == "Yes" & yes_no == "Yes") %>%
  dplyr::group_by(symptoms) %>%
  dplyr::tally() %>%
  dplyr::mutate(Percentage = n/sum(n)) %>%
  dplyr::arrange(desc(n))

start_date = as.Date("2020-04-09", tz = "Europe/London")
end_date = as.Date("2020-08-18")
title_stub <- "Diabetes type one across symptoms\n"
start_date_title <- format(as.Date(start_date), format = "%d %B %Y")
end_date_title <- format(as.Date(end_date), format = "%d %B %Y")
chart_title <- paste0(title_stub, start_date_title, " to ", end_date_title)

plot_diabetes_sympt <-
  ggplot2::ggplot(diabetes_count, ggplot2::aes(x = reorder(symptoms, - Percentage), y = n, fill = n)) +
  ggplot2::coord_flip() +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::scale_fill_viridis_c(option = "magma", direction = -1) +
  ggplot2::scale_x_discrete(limits = unique(diabetes_count$symptoms)) +
  #ggplot2::theme(legend.position = "bottom") +
  #ggplot2::guides(fill = ggplot2::guide_legend(nrow = 3)) +
  ggplot2::theme_minimal() +
  ggplot2::labs( title = chart_title,
                 subtitle = "Counts of patients with comorbidities accross symptoms",
                 y = "Counts",
                 x = "Symptoms",
                 caption = "Source: Dataset - Your.md Dataset") +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(margin = ggplot2::margin(
      t = 0,
      r = 21,
      b = 0,
      l = 0
    )),
    plot.title = ggplot2::element_text(size = 10, face = "bold"),
    plot.subtitle = ggplot2::element_text(size = 9),
    axis.text.x = ggplot2::element_text(angle = 55, hjust = 1)
  )

plot_diabetes_sympt

```







## Univariate analysis for diabetes type one 

The univariate analysis real that symptoms such as headaches, nasal congestion, sore throat, temperature (39.1-41) are associated with diabetes type one. 
```{r diabetes_type_one_chills, echo=FALSE}

diabetes_type_one_chills <- glm(diabetes_type_one ~ chills, data = diabetes_type_one_data, family = binomial)

summary(diabetes_type_one_chills)


coef_diabetes_type_one_chills <- coef(diabetes_type_one_chills)

# odd ratios 
odd_ratios_ob_ch <- exp(coef_diabetes_type_one_chills)
odd_ratios_ob_ch 

```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_chills), confint(diabetes_type_one_chills)))) 
```




1. Diabetes type one with cough

```{r diabetes_type_one_cough, echo=FALSE}
diabetes_type_one_cough <- glm(diabetes_type_one ~ cough, data = diabetes_type_one_data, family = binomial)

summary(diabetes_type_one_cough)


coef_diabetes_type_one_cough <- coef(diabetes_type_one_cough)

odd_ratios_ob_co <- exp(coef_diabetes_type_one_cough)

odd_ratios_ob_co 
```

`
```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_cough), confint(diabetes_type_one_cough)))) 
```








2. Diabetes type one with diarrhea


```{r diabetes_type_one_diarrhea}
diabetes_type_one_diarrhea <- glm(diabetes_type_one ~ diarrhoea, data = diabetes_type_one_data, family = binomial)

summary(diabetes_type_one_diarrhea)


# get coef
coef_ob_diarrhea <- coef(diabetes_type_one_diarrhea)

# odd ratios
odd_ratio_ob_diar <- exp(coef_ob_diarrhea)

odd_ratio_ob_diar
```

```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_diarrhea), confint(diabetes_type_one_diarrhea)))) 
```





3. Diabetes type one with headache

```{r diabetes_type_one_headache}
diabetes_type_one_headache <- glm(diabetes_type_one ~ headache, data = diabetes_type_one_data, family = binomial)

summary(diabetes_type_one_headache)

coef_ob_head <- coef(diabetes_type_one_headache)

odd_ratio_ob_head <- exp(coef_ob_head)
odd_ratio_ob_head
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_headache), confint(diabetes_type_one_headache)))) 
```




4. Diabetes type one with loss of smell and taste
```{r diabetes_type_one_loss_smell}

diabetes_type_one_loss_smell <- glm(diabetes_type_one ~ loss_smell_taste, data = diabetes_type_one_data, family = binomial)


summary(diabetes_type_one_loss_smell)

coef_ob_loss_smell <- coef(diabetes_type_one_loss_smell)

odd_ratio_ob_los <- exp(coef_ob_loss_smell)

odd_ratio_ob_los
```
 
 
```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_loss_smell), confint(diabetes_type_one_loss_smell)))) 
```


 5. Diabetes type one with with muscle ache

```{r diabetes_type_one_muscle_ache}


diabetes_type_one_muscle_ache <- glm(diabetes_type_one ~ muscle_ache, data = diabetes_type_one_data, family = binomial)
 
summary(diabetes_type_one_muscle_ache)

coef_ob_muscle_ac <- coef(diabetes_type_one_muscle_ache)

odd_ratio_ob_los <- exp(coef_ob_muscle_ac)

odd_ratio_ob_los

```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_muscle_ache), confint(diabetes_type_one_muscle_ache)))) 
```




6. Diabetes type one with nasal congestion
```{r diabetes_type_one_nasal_cong}

diabetes_type_one_nasal_cong <- glm(diabetes_type_one ~ nasal_congestion, data = diabetes_type_one_data, family = binomial)

summary(diabetes_type_one_nasal_cong)


coef_ob_nas_cong <- coef(diabetes_type_one_nasal_cong)

odd_ratio_ob_nas_cong <- exp(coef_ob_nas_cong)

odd_ratio_ob_nas_cong
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_nasal_cong), confint(diabetes_type_one_nasal_cong))))
```




7. Diabetes type one with nausea and vomiting
```{r diabetes_type_one_nausea_vomitting}

diabetes_type_one_nausea_vomitting <- glm(diabetes_type_one ~ nausea_vomiting, data = diabetes_type_one_data, family = binomial)

summary(diabetes_type_one_nausea_vomitting)


coef_ob_naus_vom <- coef(diabetes_type_one_nausea_vomitting)

odd_ratio_ob_naus_vom <- exp(coef_ob_naus_vom)

odd_ratio_ob_naus_vom
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_nausea_vomitting), confint(diabetes_type_one_nausea_vomitting))))
```




8. Diabetest type one with shortness of breath
```{r diabetes_type_one_short_breath}

diabetes_type_one_short_breath <- glm(diabetes_type_one ~ shortness_breath, data = diabetes_type_one_data, family = binomial)

summary(diabetes_type_one_short_breath)

coef_ob_sh_br <- coef(diabetes_type_one_short_breath)


odd_ratio_ob_sh_br <- exp(coef_ob_sh_br)

odd_ratio_ob_sh_br
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_short_breath), confint(diabetes_type_one_short_breath))))
```



9. Diabetes type one with sore throat

```{r diabetes_type_one_sore_thr}

diabetes_type_one_sore_thr <- glm(diabetes_type_one ~ sore_throat, data = diabetes_type_one_data, family = binomial)

summary(diabetes_type_one_sore_thr)

coef_ob_sore_thr <- coef(diabetes_type_one_sore_thr)


odd_ratio_ob_sore_thr <- exp(coef_ob_sore_thr)

odd_ratio_ob_sore_thr
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_sore_thr), confint(diabetes_type_one_sore_thr))))
```




10. Diabetes type one with sputum 

```{r diabetes_type_one_sputum}
diabetes_type_one_sputum <- glm(diabetes_type_one ~ sputum, data = diabetes_type_one_data, family = binomial)


summary(diabetes_type_one_sputum)


coef_ob_sp <- coef(diabetes_type_one_sputum)

odd_ratio_ob_sp <- exp(coef_ob_sp)

odd_ratio_ob_sp

vif(diabetes_type_one_sputum)
```



```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_sputum), confint(diabetes_type_one_sputum))))
```



11. Diabetes type one with temperature 

```{r diabetes_type_one_temperature}
diabetes_type_one_temperature <- glm(diabetes_type_one ~ temperature, data = diabetes_type_one_data, family = binomial)


summary(diabetes_type_one_temperature)

coef_ob_temp <- coef(diabetes_type_one_temperature)

odd_ratio_ob_temp <- exp(coef_ob_temp)

odd_ratio_ob_temp

vif(diabetes_type_one_temperature)
```
 
 
```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_temperature), confint(diabetes_type_one_temperature))))
```
 
 

```{r}
diab_one_itchy <- glm(diabetes_type_one ~ itchy_eyes, data = diabetes_type_one_data, family = binomial)

summary(diab_one_itchy)

```


```{r}
knitr::kable(exp(cbind(OR = coef(diab_one_itchy), confint(diab_one_itchy))))
```



```{r}
diabetes_one_joint_pain <- glm(diabetes_type_one ~ joint_pain, data = diabetes_type_one_data, family = binomial)

summary(diabetes_one_joint_pain)
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_one_joint_pain), confint(diabetes_one_joint_pain))))
```



```{r}
diabetes_one_chest_pain <- glm(diabetes_type_one ~ chest_pain, data = diabetes_type_one_data, family = binomial)

summary(diabetes_one_chest_pain)
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_one_chest_pain), confint(diabetes_one_chest_pain))))
```



```{r}
diabetes_one_loss_appetite <- glm(diabetes_type_one ~ loss_appetite, data = diabetes_type_one_data, family = binomial)


summary(diabetes_one_loss_appetite)
```

 
```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_one_loss_appetite), confint(diabetes_one_loss_appetite))))
```
 
 
 
## Multivariate analysis for diabetest type one

When adding all variables that showed an association with the heart disease model, the model shows something different.

When adjusting for all variables,  patients showing covid-19 symptoms/of patients with positive covid test, the results show strong evidence for an association between variables such as headaches and temperature(39.1-41) (p ≤ 0.01) in patients with diabetes type one.  
When adjusting for all variables,in patients showing covid-19 symptpms/of patients with positive covid test, in respondent with diabetes type one there was: 
- 54 % decrease in odds of experiencing headaches  compared to those who do not suffer of diabetes type one
- 406 % increase in temperature compared to those who do not suffer of heart disease

```{r diabetes_type_one_model}
diabetes_type_one_model <- glm(diabetes_type_one ~ chills + cough + headache + loss_smell_taste + muscle_ache + nausea_vomiting + shortness_breath + temperature + itchy_eyes + loss_appetite + diarrhoea + nasal_congestion + sore_throat + sputum + joint_pain + chest_pain, data = diabetes_type_one_data, family = binomial)

summary(diabetes_type_one_model)

```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_one_model), confint(diabetes_type_one_model))))
```




```{r}


vif(diabetes_type_one_model)
```