---
title: "kidney_18_08_2020"
author: "Gabriel Burcea"
date: "03/09/2020"
output: word_document
---

```{r}

library(tidyverse)
library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(qgraph)
library(report)
library(corrplot)
library(rms)

conflict_prefer("step", "stats")
```


```{r sympt-pos}

data_categ_nosev <- readr::read_csv("/Users/gabrielburcea/rprojects/data/your.md/cleaned_data_18_08_2020_fully_cleaned_uniq_comorb.csv")

data_categ_covid <- data_categ_nosev %>%
  dplyr::filter(covid_tested != 'none') %>%
  dplyr::mutate(status_cv = dplyr::case_when(covid_tested == 'showing symptoms' ~ 0,
                                             covid_tested == 'positive' ~ 1)) %>%
  tidyr::drop_na()

```

```{r}
data_categ_covid$country <- NULL
data_categ_covid$location <- NULL
data_categ_covid$date_completed <- NULL
data_categ_covid$covid_tested <- NULL 
data_categ_covid$age_band <- NULL
data_categ_covid$status_cv <- NULL
data_categ_covid$sneezing <- NULL


###########################################################################################
### Transforming variables in factor format ###############################################
#data_categ_covid$country <- as.factor(data_categ_covid$country)
data_categ_covid$chills <- as.factor(data_categ_covid$chills)
data_categ_covid$cough  <- as.factor(data_categ_covid$cough)
data_categ_covid$gender <- as.factor(data_categ_covid$gender)
#data_categ_covid$covid_tested <- as.factor(data_categ_covid$covid_tested)
data_categ_covid$diarrhoea  <- as.factor(data_categ_covid$diarrhoea)
data_categ_covid$fatigue  <- as.factor(data_categ_covid$fatigue)
data_categ_covid$headache   <- as.factor(data_categ_covid$headache)
data_categ_covid$loss_smell_taste   <- as.factor(data_categ_covid$loss_smell_taste)
data_categ_covid$muscle_ache  <- as.factor(data_categ_covid$muscle_ache)
data_categ_covid$nasal_congestion <- as.factor(data_categ_covid$nasal_congestion)
data_categ_covid$nausea_vomiting  <- as.factor(data_categ_covid$nausea_vomiting)
data_categ_covid$self_diagnosis <- as.factor(data_categ_covid$self_diagnosis)
data_categ_covid$shortness_breath <- as.factor(data_categ_covid$shortness_breath)
data_categ_covid$sore_throat <- as.factor(data_categ_covid$sore_throat)
data_categ_covid$sputum <- as.factor(data_categ_covid$sputum)
data_categ_covid$temperature  <- as.factor(data_categ_covid$temperature)
data_categ_covid$loss_appetite <- as.factor(data_categ_covid$loss_appetite)
data_categ_covid$chest_pain <- as.factor(data_categ_covid$chest_pain)
data_categ_covid$itchy_eyes <- as.factor(data_categ_covid$itchy_eyes)
data_categ_covid$joint_pain <- as.factor(data_categ_covid$joint_pain)


### Transforming variables in numerical format  #########################################################
data_categ_covid$asthma   <- as.factor(data_categ_covid$asthma)
data_categ_covid$diabetes_type_two <- as.factor(data_categ_covid$diabetes_type_two)
data_categ_covid$obesity <- as.factor(data_categ_covid$obesity)
data_categ_covid$hypertension  <- as.factor(data_categ_covid$hypertension)
data_categ_covid$heart_disease  <- as.factor(data_categ_covid$heart_disease)
data_categ_covid$kidney_disease <- as.factor(data_categ_covid$kidney_disease)
data_categ_covid$lung_condition <- as.factor(data_categ_covid$lung_condition)
data_categ_covid$liver_disease <- as.factor(data_categ_covid$liver_disease)
data_categ_covid$diabetes_type_one <- as.factor(data_categ_covid$diabetes_type_one)
#data_categ_covid$covid_tested <- as.factor(data_categ_nose)
```




```{r}
kidney_data <- data_categ_covid %>%
  dplyr::select(kidney_disease, chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, chest_pain, joint_pain, loss_appetite, itchy_eyes) %>%
  tidyr::drop_na()
```


```{r}
kidney_count <- kidney_data %>%
  tidyr::pivot_longer(cols = 2:17, 
                      names_to = "symptoms", 
                      values_to = "yes_no") %>%
  dplyr::filter(kidney_disease == "Yes" & yes_no == "Yes") %>%
  dplyr::group_by(symptoms) %>%
  dplyr::tally() %>%
  dplyr::mutate(Percentage = n/sum(n)) %>%
  dplyr::arrange(desc(n))

start_date = as.Date("2020-04-09", tz = "Europe/London")
end_date = as.Date("2020-08-18")
title_stub <- "Kidney disease across symptoms\n"
start_date_title <- format(as.Date(start_date), format = "%d %B %Y")
end_date_title <- format(as.Date(end_date), format = "%d %B %Y")
chart_title <- paste0(title_stub, start_date_title, " to ", end_date_title)

plot_kidney_sympt <-
  ggplot2::ggplot(kidney_count, ggplot2::aes(x = reorder(symptoms, - Percentage), y = n, fill = n)) +
  ggplot2::coord_flip() +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::scale_fill_viridis_c(option = "magma", direction = -1) +
  ggplot2::scale_x_discrete(limits = unique(kidney_count$symptoms)) +
  #ggplot2::theme(legend.position = "bottom") +
  #ggplot2::guides(fill = ggplot2::guide_legend(nrow = 3)) +
  ggplot2::theme_minimal() +
  ggplot2::labs( title = chart_title,
                 subtitle = "Counts of patients with comorbidities accross symptoms",
                 y = "Counts",
                 x = "Symptoms",
                 caption = "Source: Dataset - Your.md Dataset") +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(margin = ggplot2::margin(
      t = 0,
      r = 21,
      b = 0,
      l = 0
    )),
    plot.title = ggplot2::element_text(size = 10, face = "bold"),
    plot.subtitle = ggplot2::element_text(size = 9),
    axis.text.x = ggplot2::element_text(angle = 55, hjust = 1)
  )

plot_kidney_sympt
```

# Univariate analysis for kidney disease and Covid-19 symptoms

The most Covid symptoms that are associated with kidney disease are shorthness and breath and temperature.


1. Kidney disease and chills

```{r }

kidney_chills <- glm(kidney_disease ~ chills, data = kidney_data, family = binomial)

summary(kidney_chills)


coef_kidney_chills <- coef(kidney_chills)

# odd ratios 
odd_ratios_ob_ch <- exp(coef_kidney_chills)
odd_ratios_ob_ch 

```

```{r}
knitr::kable(exp(cbind(OR = coef(kidney_chills), confint(kidney_chills))))
```


2. Kidney disease and cough
```{r  echo=FALSE}
kidney_cough <- glm(kidney_disease ~ cough, data = kidney_data, family = binomial)

summary(kidney_cough)


coef_kidney_cough <- coef(kidney_cough)

odd_ratios_ob_co <- exp(coef_kidney_cough)

odd_ratios_ob_co 
```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_cough), confint(kidney_cough))))
```



3. Kidney disease and diarrhoea
```{r}
kidney_diarrhea <- glm(kidney_disease ~ diarrhoea, data = kidney_data, family = binomial)

summary(kidney_diarrhea)


# get coef
coef_ob_diarrhea <- coef(kidney_diarrhea)

# odd ratios
odd_ratio_ob_diar <- exp(coef_ob_diarrhea)

odd_ratio_ob_diar
```



4. Kidney disease and headache

```{r}
kidney_headache <- glm(kidney_disease ~ headache, data = kidney_data, family = binomial)

summary(kidney_headache)

coef_ob_head <- coef(kidney_headache)

odd_ratio_ob_head <- exp(coef_ob_head)

odd_ratio_ob_head
```

```{r}

knitr::kable(exp(cbind(OR = coef(kidney_headache), confint(kidney_headache))))
```


5. Kidney disease and loss of smell and taste
```{r}

kidney_loss_smell <- glm(kidney_disease ~ loss_smell_taste, data = kidney_data, family = binomial)


summary(kidney_loss_smell)

coef_ob_loss_smell <- coef(kidney_loss_smell)

odd_ratio_ob_los <- exp(coef_ob_loss_smell)

odd_ratio_ob_los
```



```{r}
knitr::kable(exp(cbind(OR = coef(kidney_loss_smell), confint(kidney_loss_smell))))
```




6. Kidney disease and muscle ache

```{r}


kidney_muscle_ache <- glm(kidney_disease ~ muscle_ache, data = kidney_data, family = binomial)
 
summary(kidney_muscle_ache)

coef_ob_muscle_ac <- coef(kidney_muscle_ache)

odd_ratio_ob_los <- exp(coef_ob_muscle_ac)

odd_ratio_ob_los

```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_muscle_ache), confint(kidney_muscle_ache))))
```



7. Kidney disease and nasal congestion
```{r}

kidney_nasal_cong <- glm(kidney_disease ~ nasal_congestion, data = kidney_data, family = binomial)

summary(kidney_nasal_cong)


coef_ob_nas_cong <- coef(kidney_nasal_cong)

odd_ratio_ob_nas_cong <- exp(coef_ob_nas_cong)

odd_ratio_ob_nas_cong
```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_nasal_cong), confint(kidney_nasal_cong))))
```




8. Kidney disease and nausea and vomiting

```{r}

kidney_nausea_vomitting <- glm(kidney_disease ~ nausea_vomiting, data = kidney_data, family = binomial)

summary(kidney_nausea_vomitting)


coef_ob_naus_vom <- coef(kidney_nausea_vomitting)

odd_ratio_ob_naus_vom <- exp(coef_ob_naus_vom)

odd_ratio_ob_naus_vom
```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_nausea_vomitting), confint(kidney_nausea_vomitting))))
```




9. Kidney disease and shorthness of breath

```{r}

kidney_short_breath <- glm(kidney_disease ~ shortness_breath, data = kidney_data, family = binomial)

summary(kidney_short_breath)

coef_ob_sh_br <- coef(kidney_short_breath)


odd_ratio_ob_sh_br <- exp(coef_ob_sh_br)

odd_ratio_ob_sh_br
```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_short_breath), confint(kidney_short_breath))))
```




10. Kidney disease and sore throat
```{r}

kidney_sore_thr <- glm(kidney_disease ~ sore_throat, data = kidney_data, family = binomial)

summary(kidney_sore_thr)

coef_ob_sore_thr <- coef(kidney_sore_thr)


odd_ratio_ob_sore_thr <- exp(coef_ob_sore_thr)

odd_ratio_ob_sore_thr
```

```{r}
knitr::kable(exp(cbind(OR = coef(kidney_sore_thr), confint(kidney_sore_thr))))
```




11. Kidney disease and sputum
```{r}
kidney_sputum <- glm(kidney_disease ~ sputum, data = kidney_data, family = binomial)


summary(kidney_sputum)


coef_ob_sp <- coef(kidney_sputum)

odd_ratio_ob_sp <- exp(coef_ob_sp)

odd_ratio_ob_sp
vif
vif(kidney_sputum)
```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_sputum), confint(kidney_sputum))))
```




12. Kidney disease and temperature
```{r}
kidney_temperature <- glm(kidney_disease ~ temperature, data = kidney_data, family = binomial)


summary(kidney_temperature)

coef_ob_temp <- coef(kidney_temperature)

odd_ratio_ob_temp <- exp(coef_ob_temp)

odd_ratio_ob_temp

vif(kidney_temperature)
```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_temperature), confint(kidney_temperature))))
```



```{r }

kidney_itchy_eyes <- glm(kidney_disease ~ itchy_eyes, data = kidney_data, family = binomial)

summary(kidney_itchy_eyes)

```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_itchy_eyes), confint(kidney_itchy_eyes))))
```





```{r }

kidney_joint_pain <- glm(kidney_disease ~ joint_pain, data = kidney_data, family = binomial)

summary(kidney_joint_pain)

```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_joint_pain), confint(kidney_joint_pain))))
```




```{r}
kidney_chest_pain <- glm(kidney_disease ~ chest_pain, data = kidney_data, family = binomial)

summary(kidney_chest_pain)
```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_chest_pain), confint(kidney_chest_pain))))
```




```{r}
kidney_loss_appetite <- glm(kidney_disease ~ loss_appetite, data = kidney_data, family = binomial)

summary(kidney_loss_appetite)

```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_loss_appetite), confint(kidney_loss_appetite))))
```



# Multivariate analysis for Kidney disease

The selected variables for the final model are: shortness of breath, temperature. 

In patients showing covid-19 symptoms/of patients with a positive covid test,when adjusting for all relevant variables, in respondents with kidney disease there was a: 
- 64% increase in the odds of experiencing shortness of breaht compared to those who do not have kidney disease 
- 33 % increase in the odds of experiencing 38.1 -39 temperature compared to those who do not have kidney disease
- 305 % ?? not sure - increase in odds of experiencing 39.1-41 temperature compared to those who do not have kidney disease

```{r}
kidney_model <- glm(kidney_disease ~  chills + cough + muscle_ache + nausea_vomiting + shortness_breath + sputum + temperature + joint_pain + chest_pain, data = kidney_data, family = binomial)

summary(kidney_model)
```


```{r}
knitr::kable(exp(cbind(OR = coef(kidney_model), confint(kidney_model))))
```



Multicolinearity
```{r}
vif(kidney_model)
```

