---
title: "18_08_2020_obesity"
author: "Gabriel Burcea"
date: "03/09/2020"
output: word_document
---
---
title: "18_08_2020_logistic_unque_comorbid"
author: "Gabriel Burcea"
date: "02/09/2020"
output: word_document
---





```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
library(tidyverse)
library(magrittr)
```



```{r sympt-pos}

data_categ_nosev <- readr::read_csv("/Users/gabrielburcea/rprojects/data/your.md/cleaned_data_18_08_2020_fully_cleaned_uniq_comorb.csv")

data_categ_covid <- data_categ_nosev %>%
  dplyr::filter(covid_tested != 'none') %>%
  dplyr::mutate(status_cv = dplyr::case_when(covid_tested == 'showing symptoms' ~ 0,
                                             covid_tested == 'positive' ~ 1)) %>%
  tidyr::drop_na()

```


How many male and female we have in our dataset? There are 5083 male accounting for 53 percent whilst female are 4321 accounting for 45 percent. Also, we have very low percent of other group.
```{r, gender-numbers}
gender_tb <- data_categ_covid %>%
  dplyr::select(id, gender) %>%
  dplyr::group_by(gender) %>%
  dplyr::tally() %>%
  dplyr::mutate(percent = n/sum(n)*100)

knitr::kable(gender_tb)
```


```{r, gender-pie, echo=F, results= 'asis', fig.height=5, fig.width=7}



bp <- ggplot2::ggplot(gender_tb, ggplot2::aes(x = "", y = percent, fill = gender)) + 
  ggplot2::geom_bar(width = 1, stat = "identity")

pie <- bp + ggplot2::coord_polar("y", start = 0) + 
  ggplot2::scale_fill_brewer(palette = "Blues") +
  ggplot2::theme(axis.text.x = ggplot2::element_blank())

pie
```



```{r}

library(report)

# data_categ_nosev <- data_categ_nosev %>%
#   dplyr::filter(covid_tested != 'none') %>%
#   dplyr::mutate(status_cv = dplyr::case_when(
#                                              covid_tested == 'showing symptoms' ~ 0,
#                                              covid_tested == 'positive' ~ 1), 
#                 number_comorbidities = dplyr::case_when(number_morbidities == 1 ~ 'one', 
#                                                         number_morbidities >= 2 ~ 'more than 2')) %>%
#   
#   tidyr::drop_na()
# 
# data_categ_nosev <- data_categ_nosev %>% dplyr::rename(id = ID, covid_tested = Covid_tested, gender = Gender, age = Age)

show_sympt_positive <- data_categ_covid %>%
  dplyr::select(id, status_cv) %>%
  dplyr::group_by(status_cv) %>%
  dplyr::tally()

knitr::kable(show_sympt_positive)
```


```{r  include=FALSE, echo=TRUE}


library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(qgraph)
library(report)
library(corrplot)
library(rms)

conflict_prefer("step", "stats")

### ML for Mixed - categorical and numerica data ####

```


```{r}
data_categ_covid$country <- NULL
data_categ_covid$location <- NULL
data_categ_covid$date_completed <- NULL
data_categ_covid$covid_tested <- NULL 
data_categ_covid$age_band <- NULL
data_categ_covid$status_cv <- NULL
data_categ_covid$sneezing <- NULL


###########################################################################################
### Transforming variables in factor format ###############################################
#data_categ_covid$country <- as.factor(data_categ_covid$country)
data_categ_covid$chills <- as.factor(data_categ_covid$chills)
data_categ_covid$cough  <- as.factor(data_categ_covid$cough)
data_categ_covid$gender <- as.factor(data_categ_covid$gender)
#data_categ_covid$covid_tested <- as.factor(data_categ_covid$covid_tested)
data_categ_covid$diarrhoea  <- as.factor(data_categ_covid$diarrhoea)
data_categ_covid$fatigue  <- as.factor(data_categ_covid$fatigue)
data_categ_covid$headache   <- as.factor(data_categ_covid$headache)
data_categ_covid$loss_smell_taste   <- as.factor(data_categ_covid$loss_smell_taste)
data_categ_covid$muscle_ache  <- as.factor(data_categ_covid$muscle_ache)
data_categ_covid$nasal_congestion <- as.factor(data_categ_covid$nasal_congestion)
data_categ_covid$nausea_vomiting  <- as.factor(data_categ_covid$nausea_vomiting)
data_categ_covid$self_diagnosis <- as.factor(data_categ_covid$self_diagnosis)
data_categ_covid$shortness_breath <- as.factor(data_categ_covid$shortness_breath)
data_categ_covid$sore_throat <- as.factor(data_categ_covid$sore_throat)
data_categ_covid$sputum <- as.factor(data_categ_covid$sputum)
data_categ_covid$temperature  <- as.factor(data_categ_covid$temperature)
data_categ_covid$loss_appetite <- as.factor(data_categ_covid$loss_appetite)
data_categ_covid$chest_pain <- as.factor(data_categ_covid$chest_pain)
data_categ_covid$itchy_eyes <- as.factor(data_categ_covid$itchy_eyes)
data_categ_covid$joint_pain <- as.factor(data_categ_covid$joint_pain)


### Transforming variables in numerical format  #########################################################
data_categ_covid$asthma   <- as.factor(data_categ_covid$asthma)
data_categ_covid$diabetes_type_two <- as.factor(data_categ_covid$diabetes_type_two)
data_categ_covid$obesity <- as.factor(data_categ_covid$obesity)
data_categ_covid$hypertension  <- as.factor(data_categ_covid$hypertension)
data_categ_covid$heart_disease  <- as.factor(data_categ_covid$heart_disease)
data_categ_covid$kidney_disease <- as.factor(data_categ_covid$kidney_disease)
data_categ_covid$lung_condition <- as.factor(data_categ_covid$lung_condition)
data_categ_covid$liver_disease <- as.factor(data_categ_covid$liver_disease)
data_categ_covid$diabetes_type_one <- as.factor(data_categ_covid$diabetes_type_one)
#data_categ_covid$covid_tested <- as.factor(data_categ_nose)
```


```{r}
obesity_data <- data_categ_covid %>%
  dplyr::select(id, obesity, chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, loss_appetite, chest_pain, itchy_eyes, joint_pain) %>%
  tidyr::drop_na()
```


```{r}

obesity_count <- obesity_data %>%
  tidyr::pivot_longer(cols = 3:18, 
                      names_to = "symptoms", 
                      values_to = "yes_no") %>%
  dplyr::filter(obesity == "Yes" & yes_no == "Yes")%>%
  group_by(symptoms) %>%
  dplyr::tally() %>%
  dplyr::mutate(Percentage = n/sum(n)) %>%
  dplyr::arrange(desc(n))

start_date = as.Date("2020-04-09", tz = "Europe/London")
end_date = as.Date("2020-08-18")
title_stub <- "Obesity across symptoms\n"
start_date_title <- format(as.Date(start_date), format = "%d %B %Y")
end_date_title <- format(as.Date(end_date), format = "%d %B %Y")
chart_title <- paste0(title_stub, start_date_title, " to ", end_date_title)

plot_obesity_sympt <-
  ggplot2::ggplot(obesity_count, ggplot2::aes(x = reorder(symptoms, - Percentage), y = n, fill = n)) +
  ggplot2::coord_flip() +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::scale_fill_viridis_c(option = "magma", direction = -1) +
  ggplot2::scale_x_discrete(limits = unique(obesity_count$symptoms)) +
  #ggplot2::theme(legend.position = "bottom") +
  #ggplot2::guides(fill = ggplot2::guide_legend(nrow = 3)) +
  ggplot2::theme_minimal() +
  ggplot2::labs( title = chart_title,
                 subtitle = "Counts of patients with comorbidities accross symptoms",
                 y = "Counts",
                 x = "Symptoms",
                 caption = "Source: Dataset - Your.md Dataset") +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(margin = ggplot2::margin(
      t = 0,
      r = 21,
      b = 0,
      l = 0
    )),
    plot.title = ggplot2::element_text(size = 10, face = "bold"),
    plot.subtitle = ggplot2::element_text(size = 9),
    axis.text.x = ggplot2::element_text(angle = 55, hjust = 1)
  )

plot_obesity_sympt


```

## Univariate analysis 

Univariate analysis reveal that cough, diarhea, muscle ache, nausea and vomiting, sputum, temperature are associated factors in obese patients. 

```{r }

obesity_data <- obesity_data %>%
  dplyr::select(-id)

obesity_data$obesity <- as.factor(obesity_data$obesity)
obesity_chills <- glm(obesity ~ chills, data = obesity_data, family = binomial)

summary(obesity_chills)


```



```{r}
coef_obesity_chills <- coef(obesity_chills)

# odd ratios 
odd_ratios_ob_ch <- exp(coef_obesity_chills)
odd_ratios_ob_ch 

```
OR and CI 
```{r}

knitr::kable(exp(cbind(OR = coef(obesity_chills), confint(obesity_chills))))
```


```{r pressure, echo=FALSE}
obesity_cough <- glm(obesity ~ cough, data = obesity_data, family = binomial)

summary(obesity_cough)


coef_obesity_cough <- coef(obesity_cough)

odd_ratios_ob_co <- exp(coef_obesity_cough)

odd_ratios_ob_co 
```


```{r}
knitr::kable(exp(cbind(OR = coef(obesity_cough), confint(obesity_cough))))
```


```{r}
obesity_diarrhea <- glm(obesity ~ diarrhoea, data = obesity_data, family = binomial)

summary(obesity_diarrhea)


# get coef
coef_ob_diarrhea <- coef(obesity_diarrhea)

# odd ratios
odd_ratio_ob_diar <- exp(coef_ob_diarrhea)

odd_ratio_ob_diar
```


```{r}
knitr::kable(exp(cbind(OR = coef(obesity_diarrhea), confint(obesity_diarrhea))))
```



```{r}
obesity_headache <- glm(obesity ~ headache, data = obesity_data, family = binomial)

summary(obesity_headache)

coef_ob_head <- coef(obesity_headache)

odd_ratio_ob_head <- exp(coef_ob_head)

odd_ratio_ob_head
```

OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_headache), confint(obesity_headache))))
```




```{r}

obesity_loss_smell <- glm(obesity ~ loss_smell_taste, data = obesity_data, family = binomial)


summary(obesity_loss_smell)



coef_ob_loss_smell <- coef(obesity_loss_smell)

odd_ratio_ob_los <- exp(coef_ob_loss_smell)

odd_ratio_ob_los
```


OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_loss_smell), confint(obesity_loss_smell))))
```


```{r}
library(fmsb)

obesity_muscle_ache <- glm(obesity ~ muscle_ache, data = obesity_data, family = binomial)
 
summary(obesity_muscle_ache)




coef_ob_muscle_ac <- coef(obesity_muscle_ache)

odd_ratio_ob_los <- exp(coef_ob_muscle_ac)

odd_ratio_ob_los

```


OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_muscle_ache), confint(obesity_muscle_ache))))
```





```{r}

obesity_nasal_cong <- glm(obesity ~ nasal_congestion, data = obesity_data, family = binomial)

summary(obesity_nasal_cong)


coef_ob_nas_cong <- coef(obesity_nasal_cong)

odd_ratio_ob_nas_cong <- exp(coef_ob_nas_cong)

odd_ratio_ob_nas_cong
```



OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_nasal_cong), confint(obesity_nasal_cong))))
```






```{r}

obesity_nausea_vomitting <- glm(obesity ~ nausea_vomiting, data = obesity_data, family = binomial)

summary(obesity_nausea_vomitting)


coef_ob_naus_vom <- coef(obesity_nausea_vomitting)

odd_ratio_ob_naus_vom <- exp(coef_ob_naus_vom)

odd_ratio_ob_naus_vom
```


OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_nausea_vomitting), confint(obesity_nausea_vomitting))))
```




```{r}

obesity_short_breath <- glm(obesity ~ shortness_breath, data = obesity_data, family = binomial)

summary(obesity_short_breath)

coef_ob_sh_br <- coef(obesity_short_breath)


odd_ratio_ob_sh_br <- exp(coef_ob_sh_br)

odd_ratio_ob_sh_br
```


OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_short_breath), confint(obesity_short_breath))))
```








```{r}

obesity_sore_thr <- glm(obesity ~ sore_throat, data = obesity_data, family = binomial)

summary(obesity_sore_thr)

coef_ob_sore_thr <- coef(obesity_sore_thr)


odd_ratio_ob_sore_thr <- exp(coef_ob_sore_thr)

odd_ratio_ob_sore_thr
```



OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_sore_thr), confint(obesity_sore_thr))))
```





```{r}
obesity_sputum <- glm(obesity ~ sputum, data = obesity_data, family = binomial)


summary(obesity_sputum)


coef_ob_sp <- coef(obesity_sputum)

odd_ratio_ob_sp <- exp(coef_ob_sp)

odd_ratio_ob_sp

vif(obesity_sputum)
```



OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_sputum), confint(obesity_sputum))))
```





```{r}
obesity_temperature <- glm(obesity ~ temperature, data = obesity_data, family = binomial)


summary(obesity_temperature)

coef_ob_temp <- coef(obesity_temperature)

odd_ratio_ob_temp <- exp(coef_ob_temp)

odd_ratio_ob_temp

vif(obesity_temperature)
```



OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_temperature), confint(obesity_temperature))))
```


```{r, itchy_eyes}
obesity_itchy_eyes <- glm(obesity ~ itchy_eyes, data = obesity_data, family = binomial)

summary(obesity_itchy_eyes)

coef_ob_itchy <- coef(obesity_itchy_eyes)

odd_ratio_ob_itchy <- exp(coef_ob_itchy)

odd_ratio_ob_itchy

vif(obesity_itchy_eyes)

```



OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_itchy_eyes), confint(obesity_itchy_eyes))))
```



```{r, chest_pain}
obesity_chest_pain <- glm(obesity ~ chest_pain, data = obesity_data, family = binomial)

summary(obesity_chest_pain)
```

OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_chest_pain), confint(obesity_chest_pain))))
```



```{r}
obesity_loss_appetite <- glm(obesity ~ loss_appetite, data = obesity_data, family = binomial)

summary(obesity_loss_appetite)
```


OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_loss_appetite), confint(obesity_loss_appetite))))
```




```{r, joint_pain}
obesity_joint_pain <- glm(obesity ~ joint_pain, data = obesity_data, family = binomial)


summary(obesity_joint_pain)
```



OR and CI 
```{r}
knitr::kable(exp(cbind(OR = coef(obesity_joint_pain), confint(obesity_joint_pain))))
```

Adding all variables that showed an association with obesity. 

When adjusting for all variables,  patients showing covid-19 symptoms/of patients with positive covid test, the results show strong evidence for an association between variables such as cough, diarrhea, sputum and temperature (37.5-38) (p ≤ 0.05) in obese respondents.
When adjusting for all variables,in patients showing covid-19 symptpms/of patients with positive covid test, in obese respondents there was: 
- 15 % increase in odds of experiencing cough compared to those who aren't obese
- 35 % increase in diarrhea compared to those who aren't obese
- 23 % increase in soutum compared to those who aren't obese
- 24 % decrease ??? in 37.5-38 temperature compared to those who do not suffer of heart disease




```{r}
obesity_model <- glm(obesity ~ chills +  cough + diarrhoea + headache + loss_smell_taste + muscle_ache + nasal_congestion + sore_throat + sputum + itchy_eyes + chest_pain + loss_appetite,  data = obesity_data, family = binomial)

summary(obesity_model)




```

```{r}
# odds ratio and 95% CL

knitr::kable(exp(cbind(OR = coef(obesity_model), confint(obesity_model))))
```




Multicolinearity

```{r}
vif(obesity_model)
```


