---
title: "R Notebook"
output:
  word_document: default
  html_notebook: default
---


```{r}

library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(tidyverse)
library(rms)


conflict_prefer("step", "stats")
```




```{r}
data_categ_no_sev <- readr::read_csv("/Users/gabrielburcea/Rprojects/data/data_no_sev_stats.csv")


data_categ_no_sev$gender <- as.factor(data_categ_no_sev$gender)
data_categ_no_sev$country <- as.factor(data_categ_no_sev$country)
data_categ_no_sev$chills <- as.factor(data_categ_no_sev$chills)
data_categ_no_sev$cough  <- as.factor(data_categ_no_sev$cough)
data_categ_no_sev$diarrhoea  <- as.factor(data_categ_no_sev$diarrhoea)
data_categ_no_sev$fatigue  <- as.factor(data_categ_no_sev$fatigue)
data_categ_no_sev$headache   <- as.factor(data_categ_no_sev$headache)
data_categ_no_sev$loss_smell_taste   <- as.factor(data_categ_no_sev$loss_smell_taste)
data_categ_no_sev$muscle_ache  <- as.factor(data_categ_no_sev$muscle_ache)
data_categ_no_sev$nasal_congestion <- as.factor(data_categ_no_sev$nasal_congestion)
data_categ_no_sev$nausea_vomiting  <- as.factor(data_categ_no_sev$nausea_vomiting)
data_categ_no_sev$self_diagnosis <- as.factor(data_categ_no_sev$self_diagnosis)
data_categ_no_sev$shortness_breath <- as.factor(data_categ_no_sev$shortness_breath)
data_categ_no_sev$sore_throat <- as.factor(data_categ_no_sev$sore_throat)
data_categ_no_sev$sputum <- as.factor(data_categ_no_sev$sputum)
data_categ_no_sev$temperature  <- as.factor(data_categ_no_sev$temperature)
data_categ_no_sev$health_care_worker <- as.factor(data_categ_no_sev$health_care_worker)
data_categ_no_sev$care_home_worker <- as.factor(data_categ_no_sev$care_home_worker)

data_categ_no_sev$asthma   <- as.factor(data_categ_no_sev$asthma)
data_categ_no_sev$diabetes_type_two <- as.factor(data_categ_no_sev$diabetes_type_two)
data_categ_no_sev$obesity <- as.factor(data_categ_no_sev$obesity)
data_categ_no_sev$hypertension  <- as.factor(data_categ_no_sev$hypertension)
data_categ_no_sev$heart_disease  <- as.factor(data_categ_no_sev$heart_disease)
data_categ_no_sev$kidney_disease <- as.factor(data_categ_no_sev$kidney_disease)
data_categ_no_sev$lung_condition <- as.factor(data_categ_no_sev$lung_condition)
data_categ_no_sev$liver_disease <- as.factor(data_categ_no_sev$liver_disease)
data_categ_no_sev$diabetes_type_one <- as.factor(data_categ_no_sev$diabetes_type_one)
data_categ_no_sev$how_unwell <- as.factor(data_categ_no_sev$how_unwell)
data_categ_no_sev$age <- as.factor(data_categ_no_sev$age)
data_categ_no_sev$covid_tested <- as.factor(data_categ_no_sev$covid_tested)




```


```{r}

asthma_data <- data_categ_no_sev %>%
  dplyr::select(asthma, diabetes_type_one, diabetes_type_two, obesity, hypertension, heart_disease, lung_condition, 
                liver_disease, kidney_disease, gender, age, chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature) %>%
  tidyr::drop_na()

```

## Asthma 

## Univariate analysis

Unvivariate analysis reveal chills, cough, diarrhea, headache, muschle ache, sore throat, nausea and vomiting, shortness of breath, sputum, temperature are the associated Covid symptoms in respondents with asthma. 


1. Asthma and chills
```{r }

asthma_chills <- glm(asthma ~ chills, data = asthma_data, family = binomial)

summary(asthma_chills)


coef_asthma_chills <- coef(asthma_chills)

# odd ratios 
odd_ratios_ob_ch <- (exp(coef_asthma_chills)-1)*100
odd_ratios_ob_ch 

```

2. Asthma and cough
```{r pressure, echo=FALSE}
asthma_cough <- glm(asthma ~ cough, data = asthma_data, family = binomial)

summary(asthma_cough)


coef_asthma_cough <- coef(asthma_cough)

odd_ratios_ob_co <- (exp(coef_asthma_cough)-1)*100

odd_ratios_ob_co 
```


3. Asthma and diarrhea
```{r}
asthma_diarrhea <- glm(asthma ~ diarrhoea, data = asthma_data, family = binomial)

summary(asthma_diarrhea)


# get coef
coef_ob_diarrhea <- coef(asthma_diarrhea)

# odd ratios
odd_ratio_ob_diar <- (exp(coef_ob_diarrhea)-1)*100

odd_ratio_ob_diar
```


4. Asthma and headache

```{r}
asthma_headache <- glm(asthma ~ headache, data = asthma_data, family = binomial)

summary(asthma_headache)

coef_ob_head <- coef(asthma_headache)

odd_ratio_ob_head <- (exp(coef_ob_head)-1)*100

odd_ratio_ob_head
```

5. Asthma and loss of smell and taste


```{r}

asthma_loss_smell <- glm(asthma ~ loss_smell_taste, data = asthma_data, family = binomial)


summary(asthma_loss_smell)

coef_ob_loss_smell <- coef(asthma_loss_smell)

odd_ratio_ob_los <- (exp(coef_ob_loss_smell)-1)*100

odd_ratio_ob_los
```


6. Asthma and muscle ache

```{r}


asthma_muscle_ache <- glm(asthma ~ muscle_ache, data = asthma_data, family = binomial)
 
summary(asthma_muscle_ache)

coef_ob_muscle_ac <- coef(asthma_muscle_ache)

odd_ratio_ob_los <- (exp(coef_ob_muscle_ac)-1)*100

odd_ratio_ob_los

```

7. Asthma and nasal congestion

```{r}

asthma_nasal_cong <- glm(asthma ~ nasal_congestion, data = asthma_data, family = binomial)

summary(asthma_nasal_cong)


coef_ob_nas_cong <- coef(asthma_nasal_cong)

odd_ratio_ob_nas_cong <- (exp(coef_ob_nas_cong))

odd_ratio_ob_nas_cong
```

8. Athma and nausea and vomiting 
```{r}

asthma_nausea_vomitting <- glm(asthma ~ nausea_vomiting, data = asthma_data, family = binomial)

summary(asthma_nausea_vomitting)


coef_ob_naus_vom <- coef(asthma_nausea_vomitting)

odd_ratio_ob_naus_vom <- (exp(coef_ob_naus_vom)-1)*100

odd_ratio_ob_naus_vom
```


9. Asthma and shortness of breath

```{r}

asthma_short_breath <- glm(asthma ~ shortness_breath, data = asthma_data, family = binomial)

summary(asthma_short_breath)

coef_ob_sh_br <- coef(asthma_short_breath)


odd_ratio_ob_sh_br <- (exp(coef_ob_sh_br)-1)*100

odd_ratio_ob_sh_br
```


10. Asthma and sore throat

```{r}

asthma_sore_thr <- glm(asthma ~ sore_throat, data = asthma_data, family = binomial)

summary(asthma_sore_thr)

coef_ob_sore_thr <- coef(asthma_sore_thr)


odd_ratio_ob_sore_thr <- (exp(coef_ob_sore_thr)-1)*100

odd_ratio_ob_sore_thr
```

11. Asthma and sputum 

```{r}
asthma_sputum <- glm(asthma ~ sputum, data = asthma_data, family = binomial)


summary(asthma_sputum)


coef_ob_sp <- coef(asthma_sputum)

odd_ratio_ob_sp <- (exp(coef_ob_sp)-1)*100

odd_ratio_ob_sp


vif(asthma_sputum)
```

12. Asthma and temperature
```{r}
asthma_temperature <- glm(asthma ~ temperature, data = asthma_data, family = binomial)


summary(asthma_temperature)

coef_ob_temp <- coef(asthma_temperature)

odd_ratio_ob_temp <- (exp(coef_ob_temp)-1)*100

odd_ratio_ob_temp

vif(asthma_temperature)
```





# Multivariable Logistic Regression 


Adding all symptoms that showed to be associated in asthma patients. 

When adjusting for all variables,  patients showing covid-19 symptoms/of patients with positive covid test, the results show strong evidence for an association between variables such as chills, nausea and vomiting, shortness of breath and temperature (38.1-39; 39.1-40) (p ≤ 0.05) in patients with asthma.  

When adjusting for all variables,in patients showing covid-19 symptoms/of patients with positive covid test, in patients with asthma there was: 

- 160  % increase in shortness of breath compared to those who do not suffer of asthma
- 35 % increase in sputum 
- 107 % increase in 39.1-41 temperature compared to those who do not suffer of asthma
- 1 % increase in male patients compared to those at the baseline
- 1 % increase in age compared



```{r}
asthma_model <- glm(asthma ~ chills + cough + diarrhoea + headache + muscle_ache + nausea_vomiting 
                    + shortness_breath + sputum + temperature, data = asthma_data, family = binomial)

summary(asthma_model)

coef_asthma_model <- coef(asthma_model)

odd_ratio_asthma <- (exp(coef_asthma_model)-1)*100

odd_ratio_asthma

vif(asthma_model)

coef_ob_asthma <- coef(asthma_model)
# Confidence intervals 
confint(asthma_model)

#Put the coefficients and confidence intervals onto a useful scale

conf_int_ast <- exp(confint(asthma_model)) 
conf_int_ast

```



