---
title: "clustering"
author: "Gabriel Burcea"
date: "24/07/2020"
output: word_document
---


```{r}
library(tidyverse)
library(cluster)
library(plotly)
library(fpc)
library(dendextend)
library(factorextra)
```


```{r setup, include=FALSE}

data_cluster <- read_csv("/Users/gabrielburcea/rprojects/data/data_no_sev.csv")

data_select <- data_cluster %>%
  dplyr::select(id, covid_tested, country, chills, cough, diarrhoea, fatigue, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature) %>%
  dplyr::filter(covid_tested != "none") 


covid_tested_levels <- c("positive" = "showing symptoms")
level_key_temperature <- c("Yes" = "37.5-38", 
                           "Yes" = "38.1-39", 
                           "Yes" =  "38.2-39",
                           "Yes" = "39.1-41")



levels_country <- c ('USA' = "United States of America", 
                    'United Kingdom' = "Great Britain")

data_transf <- data_select %>% 
  dplyr::mutate(covid_tested = forcats::fct_recode(covid_tested, !!!covid_tested_levels), 
                temperature = forcats::fct_recode(temperature, !!!level_key_temperature), 
                country = forcats::fct_recode(country, !!!levels_country))

data_transf$covid_tested <- as.factor(data_transf$covid_tested)
data_transf$country <- as.factor(data_transf$country)
data_transf$chills <- as.factor(data_transf$chills)
data_transf$cough <- as.factor(data_transf$cough)
data_transf$diarrhoea <- as.factor(data_transf$diarrhoea)
data_transf$fatigue <- as.factor(data_transf$fatigue)
data_transf$headache <- as.factor(data_transf$headache)
data_transf$loss_smell_taste <- as.factor(data_transf$loss_smell_taste)
data_transf$muscle_ache <- as.factor(data_transf$muscle_ache)
data_transf$ nasal_congestion <- as.factor(data_transf$ nasal_congestion)
data_transf$nausea_vomiting <- as.factor(data_transf$nausea_vomiting)
data_transf$shortness_breath <- as.factor(data_transf$shortness_breath)
data_transf$sore_throat <- as.factor(data_transf$sore_throat)
data_transf$sputum <- as.factor(data_transf$sputum)
data_transf$temperature <- as.factor(data_transf$temperature)

gather_divided <- data_transf %>%
  tidyr::pivot_longer(cols = 4:16,
                      names_to = "Symptom",
                      values_to = "Severity") %>%
  dplyr::filter(Severity != "No") %>%
  dplyr::group_by(Symptom, country) %>%
  dplyr::summarise(Count = n()) 


test_data <-  gather_divided %>% pivot_wider(names_from = Symptom, values_from = Count)

#test_data <- test_data %>% mutate_if(is.numeric, funs(replace_na(., 0)))

test_data <- na.omit(test_data)

test_data$chills  <- as.numeric(test_data$chills) 
test_data$cough  <- as.numeric(test_data$cough)
test_data$diarrhoea  <- as.numeric(test_data$diarrhoea)
test_data$fatigue  <- as.numeric(test_data$fatigue)
test_data$headache  <- as.numeric(test_data$headache)
test_data$loss_smell_taste  <- as.numeric(test_data$loss_smell_taste)
test_data$muscle_ache  <- as.numeric(test_data$muscle_ache)
test_data$nasal_congestion  <- as.numeric(test_data$nasal_congestion)
test_data$nausea_vomiting  <- as.numeric(test_data$nausea_vomiting)
test_data$shortness_breath  <- as.numeric(test_data$shortness_breath)
test_data$sore_throat  <- as.numeric(test_data$sore_throat)
test_data$sputum <- as.numeric(test_data$sputum)
test_data$temperature <- as.numeric(test_data$temperature)


df_scaled <- scale(test_data[2:14])

rownames(df_scaled) <- test_data$country


```

Get the gower distance - to calculate the disimilarity matrix
```{r}
my.seed <- set.seed(22)

gower_distance <- cluster::daisy(df_scaled, metric = "gower")

gower_distance

class(gower_distance)
```


Agglomerative clustering vs. divisive clustering 
Agglomerative clustering is better in discovering small clusters
```{r}
# The main input for the code below is dissimilarity (distance matrix)
# After dissimilarity matrix was calculated, the further steps will be the same for all data types
# I prefer to look at the dendrogram and fine the most appealing one first - in this case, I was looking for a more balanced one - to further continue with #assessment

divisive_clustering <- diana(as.matrix(gower_distance), diss = TRUE, keep.diss = TRUE)


 
plotly::ggplotly(plot(divisive_clustering, main = "Divisive"))  



```


Assesing

```{r}
agglomerative_clustering <- hclust(gower_distance, method = "complete")

plot(agglomerative_clustering, main = "Agglomerative, complete linkeges")

```
Assesing clusters 

- working with categorical variables, I might end up with non-sense clusters because the combination of their values is limited 0 they are discrete, s
so is the number of their combinations. However, I do not want to have a very small number of clusters either - they are likely to be too general. 
- I am interested in distinctive groups of data points, such that the distance between them within clusters (or compactness) is mininaly, while
the distance between groups(separation) is large as possible,
- distance btween points is a measure of their disimilarity derived from dissimilarity matrix
- the assessment of clustering is built around evaluation of compactness and separation 

I will go for  approaches:

- elbow method: start with it when the compactness of clusters, or similarities within group are most important for my analysis
- silhouette method: as a measure of data consistency, the silhouette plot displays a measure of how close each point in one cluster is to points in the neighboring clusters

Different number of clusters will correspond to the most compact / most distinctively separated clusters 


```{r}

cstats.table <- function(dist, tree, k) {
  clust.assess <-
    c(
      "cluster.number",
      "n",
      "within.cluster.ss",
      "average.within",
      "average.between",
      "wb.ratio",
      "dunn2",
      "avg.silwidth"
    )
  
  clust.size <- c("cluster.size")
  
  stats.names <- c()
  
  row.clust <- c()
  
  output.stats <- matrix(ncol = k, nrow = length(clust.assess))
  
  cluster.sizes <- matrix(ncol = k, nrow = k)
  for (i in c(1:k)) {
    row.clust[i] <- paste("Cluster-", i, " size")
  }
  for (i in c(2:k)) {
    stats.names[i] <- paste("Test", i - 1)
    
    for (j in seq_along(clust.assess)) {
      output.stats[j, i] <-
        unlist(cluster.stats(d = dist, clustering = cutree(tree, k = i))[clust.assess])[j]
      
    }
    
    for (d in 1:k) {
      cluster.sizes[d, i] <-
        unlist(cluster.stats(d = dist, clustering = cutree(tree, k = i))[clust.size])[d]
      dim(cluster.sizes[d, i]) <- c(length(cluster.sizes[i]), 1)
      cluster.sizes[d, i]
      
    }
  }
  
  output.stats.df <- data.frame(output.stats)
  cluster.sizes <- data.frame(cluster.sizes)
  cluster.sizes[is.na(cluster.sizes)] <- 0
  rows.all <- c(clust.assess, row.clust)
  # rownames(output.stats.df) <- clust.assess
  output <- rbind(output.stats.df, cluster.sizes)[, -1]
  colnames(output) <- stats.names[2:k]
  rownames(output) <- rows.all
  is.num <- sapply(output, is.numeric)
  output[is.num] <- lapply(output[is.num], round, 2)
  output
}

```



```{r}

stats_divisive <- cstats.table(gower_distance, divisive_clustering, 7)

stats_divisive

```

average.within - which is average distance among observations within clusters, is shrinking, so does within cluster ss. Avrage
silhouette width is also decreasing. 
```{r}
stats_agglomerative <- cstats.table(gower_distance, agglomerative_clustering, 7)

stats_agglomerative
```

I am using Elbow and Silhouette methods to indetifu the best number of clusters to better picture the trend. 


Divisive clustering. 
I have produces the elbow graph. It shows how the within sum of squares - as a measure of closeness of observations: the lower it is the closer the obesrvations wtihin the clusters are - changed for the different number of clusers. Distinctive bend in the elbow where splitting clusters further gives only minor decrease in the SS. Probably 11 clusters? 
```{r}

elb_div <-
  ggplot(data = data.frame(t(
    cstats.table(gower_distance, divisive_clustering, 17)
  )),
  aes(x = cluster.number, y = within.cluster.ss)) +
  geom_point() +
  geom_line() +
  ggtitle("Divisive clustering") +
  labs(x = "Number of clusters", y = "Within clusters sum of squares(SS)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_minimal()

elb_div
```


Agglomerative "elbow" - tells me I shall have 5 clusters. Isn't as smooth as the previous one. 
```{r}
elb_agglomerative <-
  ggplot(data = data.frame(t(
    cstats.table(gower_distance, agglomerative_clustering, 17)
  )),
  aes(x = cluster.number, y = within.cluster.ss)) +
  geom_point() +
  geom_line() +
  ggtitle("Aglomerative clustering") +
  labs(x = "Number of clusters", y = "Within clusters sum of squares(SS)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_minimal()

elb_agglomerative
```

Silhouette - the rule is to choose the number that maximized the silhoutte coefficient because clusters should be distinctive
(far) enough to be considered separate. The silhouette coefficient ranges between -1 and 1, with 1 indicating good consistency
within clusters, -1 - not so good. This plot is a bit confusing - but will go for 4 ? Not sure
```{r}
sil_div <-
  ggplot(data = data.frame(t(
    cstats.table(gower_distance, divisive_clustering, 17)
  )),
  aes(x = cluster.number, y = avg.silwidth)) +
  geom_point() +
  geom_line() +
  ggtitle("Divisive clustering") +
  labs(x = "Number of clusters", y = "Average silhouette width") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_minimal()

sil_div
```


```{r}
sil_agglomerative <-
  ggplot(data = data.frame(t(
    cstats.table(gower_distance, agglomerative_clustering, 17)
  )),
  aes(x = cluster.number, y = avg.silwidth)) +
  geom_point() +
  geom_line() +
  ggtitle("Aglomerative clustering") +
  labs(x = "Number of clusters", y = "Average silhouette width") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_minimal()

sil_agglomerative
```