---
title: "lung_condition_18082020_40_59"
author: "Gabriel Burcea"
date: "14/09/2020"
output: word_document
---

```{r  include=FALSE, echo=TRUE}

library(tidyverse)
library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(qgraph)
library(report)
library(corrplot)
library(rms)

conflict_prefer("step", "stats")

### ML for Mixed - categorical and numerica data ####

```



```{r sympt-pos}

data_categ_nosev <- readr::read_csv("/Users/gabrielburcea/rprojects/data/your.md/cleaned_data_18_08_2020_fully_cleaned_uniq_comorb.csv")


covid_tested_levels <- c("positive" = "showing symptoms")

data_age_band <- data_categ_nosev %>%
   dplyr::mutate(age_band = dplyr::case_when(
     age == 0 | age <= 19 ~ '0-19',
     age == 20 | age <= 39 ~ '20-39',
     age == 40 | age <= 59 ~ '40-59',
     age >= 60 ~ "60+")) %>%
  dplyr::filter(number_morbidities <= 1) %>%
  dplyr::mutate(covid_tested = forcats::fct_recode(covid_tested, !!!covid_tested_levels))


data_covid_only <- data_age_band %>%
#dplyr::filter(number_morbidities <= 1) %>% # added this line on the 09/09/2020 as I want to check the analysis - do I get a different output, See report delivered  ...  compare this with the previous report generated on the date ....
  dplyr::select(id, age, gender, covid_tested, chills, cough, diarrhoea, fatigue, headache, loss_smell_taste, muscle_ache,
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, loss_appetite, chest_pain, itchy_eyes, joint_pain, 
                asthma, diabetes_type_one, diabetes_type_two, obesity, hypertension, heart_disease, lung_condition, liver_disease, kidney_disease, age_band, number_morbidities)%>% 
  dplyr::filter(covid_tested != "negative") %>%
  tidyr::drop_na()


data_age <- data_covid_only %>% 
  dplyr::filter(age_band == "40-59")


data_categ_covid <- data_age %>%
  #dplyr::filter(number_morbidities <= 1) %>% # added this line on the 09/09/2020 as I want to check the analysis - do I get a different output, See report delivered  ...  compare this with the previous report generated on the date ....
 dplyr::select(id, age, gender, covid_tested, chills, cough, diarrhoea, fatigue, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, loss_appetite, chest_pain, itchy_eyes, joint_pain, 
                asthma, diabetes_type_one, diabetes_type_two, obesity, hypertension, heart_disease, lung_condition, liver_disease, kidney_disease) %>%
  dplyr::filter(covid_tested != "negative") %>%
  tidyr::drop_na()


```



```{r}
data_categ_covid$country <- NULL
data_categ_covid$location <- NULL
data_categ_covid$date_completed <- NULL
data_categ_covid$covid_tested <- NULL 
data_categ_covid$age_band <- NULL
data_categ_covid$status_cv <- NULL
data_categ_covid$sneezing <- NULL


###########################################################################################
### Transforming variables in factor format ###############################################
#data_categ_covid$country <- as.factor(data_categ_covid$country)
data_categ_covid$chills <- as.factor(data_categ_covid$chills)
data_categ_covid$cough  <- as.factor(data_categ_covid$cough)
data_categ_covid$gender <- as.factor(data_categ_covid$gender)
#data_categ_covid$covid_tested <- as.factor(data_categ_covid$covid_tested)
data_categ_covid$diarrhoea  <- as.factor(data_categ_covid$diarrhoea)
data_categ_covid$fatigue  <- as.factor(data_categ_covid$fatigue)
data_categ_covid$headache   <- as.factor(data_categ_covid$headache)
data_categ_covid$loss_smell_taste   <- as.factor(data_categ_covid$loss_smell_taste)
data_categ_covid$muscle_ache  <- as.factor(data_categ_covid$muscle_ache)
data_categ_covid$nasal_congestion <- as.factor(data_categ_covid$nasal_congestion)
data_categ_covid$nausea_vomiting  <- as.factor(data_categ_covid$nausea_vomiting)
#data_categ_covid$self_diagnosis <- as.factor(data_categ_covid$self_diagnosis)
data_categ_covid$shortness_breath <- as.factor(data_categ_covid$shortness_breath)
data_categ_covid$sore_throat <- as.factor(data_categ_covid$sore_throat)
data_categ_covid$sputum <- as.factor(data_categ_covid$sputum)
data_categ_covid$temperature  <- as.factor(data_categ_covid$temperature)
data_categ_covid$loss_appetite <- as.factor(data_categ_covid$loss_appetite)
data_categ_covid$chest_pain <- as.factor(data_categ_covid$chest_pain)
data_categ_covid$itchy_eyes <- as.factor(data_categ_covid$itchy_eyes)
data_categ_covid$joint_pain <- as.factor(data_categ_covid$joint_pain)


### Transforming variables in numerical format  #########################################################
data_categ_covid$asthma   <- as.factor(data_categ_covid$asthma)
data_categ_covid$diabetes_type_two <- as.factor(data_categ_covid$diabetes_type_two)
data_categ_covid$obesity <- as.factor(data_categ_covid$obesity)
data_categ_covid$hypertension  <- as.factor(data_categ_covid$hypertension)
data_categ_covid$heart_disease  <- as.factor(data_categ_covid$heart_disease)
data_categ_covid$kidney_disease <- as.factor(data_categ_covid$kidney_disease)
data_categ_covid$lung_condition <- as.factor(data_categ_covid$lung_condition)
data_categ_covid$liver_disease <- as.factor(data_categ_covid$liver_disease)
data_categ_covid$diabetes_type_one <- as.factor(data_categ_covid$diabetes_type_one)
#data_categ_covid$covid_tested <- as.factor(data_categ_nose)
```




```{r}
lung_condition_data <- data_categ_covid %>%
  dplyr::select(lung_condition, chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature,  joint_pain, chest_pain, itchy_eyes, loss_appetite) %>%
  tidyr::drop_na()
```



```{r}
lung_count <- lung_condition_data %>%
  tidyr::pivot_longer(cols = 2:17, 
                      names_to = "symptoms", 
                      values_to = "yes_no") %>%
  dplyr::filter(lung_condition== "Yes" & yes_no == "Yes") %>%
  dplyr::group_by(symptoms) %>%
  dplyr::tally() %>%
  dplyr::mutate(Percentage = n/sum(n)) %>%
  dplyr::arrange(desc(n))

start_date = as.Date("2020-04-09", tz = "Europe/London")
end_date = as.Date("2020-08-18")
title_stub <- "Age Group 40-59: Lung condition across symptoms\n"
start_date_title <- format(as.Date(start_date), format = "%d %B %Y")
end_date_title <- format(as.Date(end_date), format = "%d %B %Y")
chart_title <- paste0(title_stub, start_date_title, " to ", end_date_title)

plot_lung_sympt <-
  ggplot2::ggplot(lung_count, ggplot2::aes(x = reorder(symptoms, - Percentage), y = n, fill = n)) +
  ggplot2::coord_flip() +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::scale_fill_viridis_c(option = "magma", direction = -1) +
  ggplot2::scale_x_discrete(limits = unique(lung_count$symptoms)) +
  #ggplot2::theme(legend.position = "bottom") +
  #ggplot2::guides(fill = ggplot2::guide_legend(nrow = 3)) +
  ggplot2::theme_minimal() +
  ggplot2::labs( title = chart_title,
                 subtitle = "Counts of patients with comorbidities accross symptoms",
                 y = "Counts",
                 x = "Symptoms",
                 caption = "Source: Dataset - Your.md Dataset") +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(margin = ggplot2::margin(
      t = 0,
      r = 21,
      b = 0,
      l = 0
    )),
    plot.title = ggplot2::element_text(size = 10, face = "bold"),
    plot.subtitle = ggplot2::element_text(size = 9),
    axis.text.x = ggplot2::element_text(angle = 55, hjust = 1)
  )

plot_lung_sympt
```


# Univariate analysis for lung condition and Covid-19 symptoms


Univariate logistic regression for lung condition and covid symptoms reveal: 
- nausea and vomiting, shortness of breath, sputum and 39.1- 41 temperature are statistically significant by looking at p values


1. Lung condition and chills
```{r}


lung_condition_data$lung_condition <- as.factor(lung_condition_data$lung_condition)
lung_condition_chills <- glm(lung_condition ~ chills, data = lung_condition_data, family = binomial)

summary(lung_condition_chills)
```

```{r}
coef_lung_condition_chills <- coef(lung_condition_chills)


```

```{r}
lung_condition_chills_or_ci <- exp(cbind(OR = coef(lung_condition_chills), confint(lung_condition_chills)))
```

P-values adjusted 

```{r}
lung_condition_chills_pval <- summary(lung_condition_chills)$coefficients[,4]

lung_condition_chills_pval <- lung_condition_chills_pval[-1]

lung_condition_chills_padj <- p.adjust(lung_condition_chills_pval, method = "bonferroni")

lung_condition_chills_padj
```


OR, CI and pval adjusted  
```{r}

lung_condition_chills_or_ci_pval <- cbind(lung_condition_chills_or_ci, data.frame(pvalues = lung_condition_chills_padj))

knitr::kable(lung_condition_chills_or_ci_pval)
```



```{r pressure, echo=FALSE}
lung_condition_cough <- glm(lung_condition ~ cough, data = lung_condition_data, family = binomial)

summary(lung_condition_cough)


coef_lung_condition_cough <- coef(lung_condition_cough)

odd_ratios_ob_co <- exp(coef_lung_condition_cough)

odd_ratios_ob_co 
```


```{r}
lung_condition_cough_or_ci <- exp(cbind(OR = coef(lung_condition_cough), confint(lung_condition_cough)))
```

P-values adjusted 

```{r}
lung_condition_cough_pval <- summary(lung_condition_cough)$coefficients[,4]

lung_condition_cough_pval <- lung_condition_cough_pval[-1]

lung_condition_cough_padj <- p.adjust(lung_condition_cough_pval, method = "bonferroni")

lung_condition_cough_padj
```


OR, CI and pval adjusted  
```{r}

lung_condition_cough_or_ci_pval <- cbind(lung_condition_cough_or_ci, data.frame(pvalues = lung_condition_cough_padj))

knitr::kable(lung_condition_cough_or_ci_pval)
```

```{r}
lung_condition_diarrhea <- glm(lung_condition ~ diarrhoea, data = lung_condition_data, family = binomial)

summary(lung_condition_diarrhea)


# get coef
coef_ob_diarrhea <- coef(lung_condition_diarrhea)

# odd ratios
odd_ratio_ob_diar <- exp(coef_ob_diarrhea)

odd_ratio_ob_diar
```


```{r}
lung_condition_diarrhea_or_ci <- exp(cbind(OR = coef(lung_condition_diarrhea), confint(lung_condition_diarrhea)))
```
P-values adjusted 

```{r}
lung_condition_diarrhea_pval <- summary(lung_condition_diarrhea)$coefficients[,4]

lung_condition_diarrhea_pval <- lung_condition_diarrhea_pval[-1]

lung_condition_diarrhea_padj <- p.adjust(lung_condition_diarrhea_pval, method = "bonferroni")

lung_condition_diarrhea_padj
```
OR, CI and pval adjusted  
```{r}

lung_condition_diarrhea_or_ci_pval <- cbind(lung_condition_diarrhea_or_ci, data.frame(pvalues = lung_condition_diarrhea_padj))

knitr::kable(lung_condition_diarrhea_or_ci_pval)
```


```{r}
lung_condition_headache <- glm(lung_condition ~ headache, data = lung_condition_data, family = binomial)

summary(lung_condition_headache)

```

OR and CI 
```{r}
lung_condition_headache_or_ci <- exp(cbind(OR = coef(lung_condition_headache), confint(lung_condition_headache)))

```



P-values adjusted 

```{r}
lung_condition_headache_pval <- summary(lung_condition_headache)$coefficients[,4]

lung_condition_headache_pval <- lung_condition_headache_pval[-1]

lung_condition_headache_padj <- p.adjust(lung_condition_headache_pval, method = "bonferroni")

lung_condition_headache_padj 
```


OR, CI and pval adjusted  
```{r}

lung_condition_headache_or_ci_pval <- cbind(lung_condition_headache_or_ci, data.frame(pvalues = lung_condition_headache_padj))

knitr::kable(lung_condition_headache_or_ci_pval)

```






```{r}

lung_condition_loss_smell <- glm(lung_condition ~ loss_smell_taste, data = lung_condition_data, family = binomial)


summary(lung_condition_loss_smell)



```


OR and CI 
```{r}
lung_condition_loss_smell_or_ci <-    exp(cbind(OR = coef(lung_condition_loss_smell), confint(lung_condition_loss_smell)))

```





```{r}
lung_condition_loss_smell_pval <- summary(lung_condition_loss_smell)$coefficients[,4]

lung_condition_loss_smell_pval <- lung_condition_loss_smell_pval[-1]

lung_condition_loss_smell_padj <- p.adjust(lung_condition_loss_smell_pval, method = "bonferroni")

lung_condition_loss_smell_padj

```


OR, CI and pval adjusted  
```{r}

lung_condition_loss_smell_or_ci_pval <- cbind(lung_condition_loss_smell_or_ci, data.frame(pvalues = lung_condition_loss_smell_padj))

knitr::kable(lung_condition_loss_smell_or_ci_pval)

```





```{r}
library(fmsb)

lung_condition_muscle_ache <- glm(lung_condition ~ muscle_ache, data = lung_condition_data, family = binomial)
 
summary(lung_condition_muscle_ache)




coef_ob_muscle_ac <- coef(lung_condition_muscle_ache)

odd_ratio_ob_los <- exp(coef_ob_muscle_ac)

odd_ratio_ob_los


```


OR and CI 
```{r}
lung_condition_muscle_ache_or_ci <- exp(cbind(OR = coef(lung_condition_muscle_ache), confint(lung_condition_muscle_ache)))

```




```{r}
lung_condition_muscle_ache_pval <- summary(lung_condition_muscle_ache)$coefficients[,4]

lung_condition_muscle_ache_pval <- lung_condition_muscle_ache_pval[-1]

lung_condition_muscle_ache_padj <- p.adjust(lung_condition_muscle_ache_pval, method = "bonferroni")

lung_condition_muscle_ache_padj

```


OR, CI and pval adjusted  
```{r}

lung_condition_muscle_ache_or_ci_pval <- cbind(lung_condition_muscle_ache_or_ci, data.frame(pvalues = lung_condition_muscle_ache_padj))

knitr::kable(lung_condition_muscle_ache_or_ci_pval)

```



```{r}

lung_condition_nasal_cong <- glm(lung_condition ~ nasal_congestion, data = lung_condition_data, family = binomial)

summary(lung_condition_nasal_cong)


coef_ob_nas_cong <- coef(lung_condition_nasal_cong)

odd_ratio_ob_nas_cong <- exp(coef_ob_nas_cong)

odd_ratio_ob_nas_cong

```



OR and CI 
```{r}
lung_condition_nasal_cong_or_ci <- exp(cbind(OR = coef(lung_condition_nasal_cong), confint(lung_condition_nasal_cong)))

```



```{r}
lung_condition_nasal_cong_pval <- summary(lung_condition_nasal_cong)$coefficients[,4]

lung_condition_nasal_cong_pval <- lung_condition_nasal_cong_pval[-1]

lung_condition_nasal_cong_padj <- p.adjust(lung_condition_nasal_cong_pval, method = "bonferroni")

lung_condition_nasal_cong_padj

```


OR, CI and pval adjusted  
```{r}

lung_condition_nasal_cong_or_ci_pval <- cbind(lung_condition_nasal_cong_or_ci, data.frame(pvalues = lung_condition_nasal_cong_padj))

knitr::kable(lung_condition_nasal_cong_or_ci_pval)

```




```{r}

lung_condition_nausea_vomitting <- glm(lung_condition ~ nausea_vomiting, data = lung_condition_data, family = binomial)

summary(lung_condition_nausea_vomitting)


coef_ob_naus_vom <- coef(lung_condition_nausea_vomitting)

odd_ratio_ob_naus_vom <- exp(coef_ob_naus_vom)


odd_ratio_ob_naus_vom
```


OR and CI 
```{r}
lung_condition_nausea_vomitting_or_ci <- exp(cbind(OR = coef(lung_condition_nausea_vomitting), confint(lung_condition_nausea_vomitting)))

```



```{r}
lung_condition_nausea_vomitting_pval <- summary(lung_condition_nausea_vomitting)$coefficients[,4]

lung_condition_nausea_vomitting_pval <- lung_condition_nausea_vomitting_pval[-1]

lung_condition_nausea_vomitting_padj <- p.adjust(lung_condition_nausea_vomitting_pval, method = "bonferroni")

lung_condition_nausea_vomitting_padj

```


OR, CI and pval adjusted  
```{r}

lung_condition_nausea_vomitting_or_ci_pval <- cbind(lung_condition_nausea_vomitting_or_ci, data.frame(pvalues = lung_condition_nausea_vomitting_padj))

knitr::kable(lung_condition_nausea_vomitting_or_ci_pval)

```





```{r}

lung_condition_short_breath <- glm(lung_condition ~ shortness_breath, data = lung_condition_data, family = binomial)

summary(lung_condition_short_breath)



```


OR and CI 
```{r}
lung_condition_short_breath_or_ci <- exp(cbind(OR = coef(lung_condition_short_breath), confint(lung_condition_short_breath)))

```




```{r}
lung_condition_short_breath_pval <- summary(lung_condition_short_breath)$coefficients[,4]

lung_condition_short_breath_pval <- lung_condition_short_breath_pval[-1]

lung_condition_short_breath_padj <- p.adjust(lung_condition_short_breath_pval, method = "bonferroni")

lung_condition_short_breath_padj
```



OR, CI and pval adjusted  
```{r}

lung_condition_short_breath_or_ci_pval <- cbind(lung_condition_short_breath_or_ci, data.frame(pvalues = lung_condition_short_breath_padj))

knitr::kable(lung_condition_short_breath_or_ci_pval)

```







```{r}

lung_condition_sore_thr <- glm(lung_condition ~ sore_throat, data = lung_condition_data, family = binomial)

summary(lung_condition_sore_thr)


```



OR and CI 
```{r}
lung_condition_sore_thr_or_ci <- exp(cbind(OR = coef(lung_condition_sore_thr), confint(lung_condition_sore_thr)))
```





```{r}
lung_condition_sore_thr_pval <- summary(lung_condition_sore_thr)$coefficients[,4]

lung_condition_sore_thr_pval <- lung_condition_sore_thr_pval[-1]

lung_condition_sore_thr_padj <- p.adjust(lung_condition_sore_thr_pval, method = "bonferroni")

lung_condition_sore_thr_padj

```


OR, CI and pval adjusted  
```{r}

lung_condition_sore_thr_or_ci_pval <- cbind(lung_condition_sore_thr_or_ci, data.frame(pvalues = lung_condition_sore_thr_padj))

knitr::kable(lung_condition_sore_thr_or_ci_pval)

```






```{r}
lung_condition_sputum <- glm(lung_condition ~ sputum, data = lung_condition_data, family = binomial)


summary(lung_condition_sputum)



```



OR and CI 
```{r}
lung_condition_sputum_or_ci <- exp(cbind(OR = coef(lung_condition_sputum), confint(lung_condition_sputum)))
```




```{r}
lung_condition_sputum_pval <- summary(lung_condition_sputum)$coefficients[,4]

lung_condition_sputum_pval <- lung_condition_sputum_pval[-1]

lung_condition_sputum_padj <- p.adjust(lung_condition_sputum_pval, method = "bonferroni")

lung_condition_sputum_padj

```


OR, CI and pval adjusted  
```{r}

lung_condition_sputum_or_ci_pval <- cbind(lung_condition_sputum_or_ci, data.frame(pvalues = lung_condition_sputum_padj))

knitr::kable(lung_condition_sputum_or_ci_pval)
```



```{r}
lung_condition_temperature <- glm(lung_condition ~ temperature, data = lung_condition_data, family = binomial)


summary(lung_condition_temperature)



```



OR and CI 
```{r}
lung_condition_temperature_or_ci <- exp(cbind(OR = coef(lung_condition_temperature), confint(lung_condition_temperature)))

```




```{r}
lung_condition_temperature_pval <- summary(lung_condition_temperature)$coefficients[,4]

lung_condition_temperature_pval <- lung_condition_temperature_pval[-1]

lung_condition_temperature_padj <- p.adjust(lung_condition_temperature_pval, method = "bonferroni")

lung_condition_temperature_padj

```


OR, CI and pval adjusted  
```{r}

lung_condition_temperature_or_ci_pval <- cbind(lung_condition_temperature_or_ci, data.frame(pvalues = lung_condition_temperature_padj))

knitr::kable(lung_condition_temperature_or_ci_pval)

```



```{r, itchy_eyes}
lung_condition_itchy_eyes <- glm(lung_condition ~ itchy_eyes, data = lung_condition_data, family = binomial)

summary(lung_condition_itchy_eyes)


```



OR and CI 
```{r}
lung_condition_itchy_eyes_or_ci <- exp(cbind(OR = coef(lung_condition_itchy_eyes), confint(lung_condition_itchy_eyes)))

```



```{r}
lung_condition_itchy_eyes_pval <- summary(lung_condition_itchy_eyes)$coefficients[,4]

lung_condition_itchy_eyes_pval <- lung_condition_itchy_eyes_pval[-1]

lung_condition_itchy_eyes_padj <- p.adjust(lung_condition_itchy_eyes_pval, method = "bonferroni")

lung_condition_itchy_eyes_padj

```


OR, CI and pval adjusted  
```{r}

lung_condition_itchy_eyes_or_ci_pval <- cbind(lung_condition_itchy_eyes_or_ci, data.frame(pvalues = lung_condition_itchy_eyes_padj))

knitr::kable(lung_condition_itchy_eyes_or_ci_pval)

```



```{r, chest_pain}
lung_condition_chest_pain <- glm(lung_condition ~ chest_pain, data = lung_condition_data, family = binomial)

summary(lung_condition_chest_pain)

```

OR and CI 
```{r}
lung_condition_chest_pain_or_ci <- exp(cbind(OR = coef(lung_condition_chest_pain), confint(lung_condition_chest_pain)))

```




```{r}
lung_condition_chest_pain_pval <- summary(lung_condition_chest_pain)$coefficients[,4]

lung_condition_chest_pain_pval <- lung_condition_chest_pain_pval[-1]

lung_condition_chest_pain_padj <- p.adjust(lung_condition_chest_pain_pval, method = "bonferroni")

lung_condition_chest_pain_padj

```


OR, CI and pval adjusted  
```{r}

lung_condition_chest_pain_or_ci_pval <- cbind(lung_condition_chest_pain_or_ci, data.frame(pvalues = lung_condition_chest_pain_padj))

knitr::kable(lung_condition_chest_pain_or_ci_pval)

```



```{r}
lung_condition_loss_appetite <- glm(lung_condition ~ loss_appetite, data = lung_condition_data, family = binomial)

summary(lung_condition_loss_appetite)

```


OR and CI 
```{r}
lung_condition_loss_appetite_or_ci <- exp(cbind(OR = coef(lung_condition_loss_appetite), confint(lung_condition_loss_appetite)))

```


```{r}
lung_condition_loss_appetite_pval <- summary(lung_condition_loss_appetite)$coefficients[,4]

lung_condition_loss_appetite_pval <- lung_condition_loss_appetite_pval[-1]

lung_condition_loss_appetite_padj <- p.adjust(lung_condition_loss_appetite_pval, method = "bonferroni")

lung_condition_loss_appetite_padj

```


OR, CI and pval adjusted  
```{r}

lung_condition_loss_appetite_or_ci_pval <- cbind(lung_condition_loss_appetite_or_ci, data.frame(pvalues = lung_condition_loss_appetite_padj))

knitr::kable(lung_condition_loss_appetite_or_ci_pval)

```



```{r, joint_pain}
lung_condition_joint_pain <- glm(lung_condition ~ joint_pain, data = lung_condition_data, family = binomial)


summary(lung_condition_joint_pain)

```


OR and CI 
```{r}
lung_condition_joint_pain_or_ci <- exp(cbind(OR = coef(lung_condition_joint_pain), confint(lung_condition_joint_pain)))

```



```{r}
lung_condition_joint_pain_pval <- summary(lung_condition_joint_pain)$coefficients[,4]

lung_condition_joint_pain_pval <- lung_condition_joint_pain_pval[-1]

lung_condition_joint_pain_padj <- p.adjust(lung_condition_joint_pain_pval, method = "bonferroni")

lung_condition_joint_pain_padj

```


OR, CI and pval adjusted  
```{r}

lung_condition_joint_pain_or_ci_pval <- cbind(lung_condition_joint_pain_or_ci, data.frame(pvalues = lung_condition_joint_pain_padj))

knitr::kable(lung_condition_joint_pain_or_ci_pval)

```



# Multivariate analysis for lung condition 


Adding all variables that showed an association with the lung diseease. 

When adjusting for all variables,  patients showing covid-19 symptoms/of patients with positive covid test, the results show strong evidence for an association between variables such as nausea and vomiting, shortness of breath and temperature (38.1-39; 39.1-40) (p ≤ 0.05) and sputum in patients with lung disease.  


When adjusting for the above variables, in patients showing covid-19 symptoms/of patients with positivie covid test, there was:
- 88 % increase in the odds of experiencing nausea and vomiting compared to those who did not have lung disease; 
- 63 % increase in odds of experiencing shortness of breath  compared to those who did not have lung disease;
- 146 % increase in 39.1-41 temperature compared to those who did not have lung disease;
- 33 % increase in the odds of experiencing sputum in patients with lung disease compared to those who did not have lung disease


```{r}
lung_condition_model <- glm(lung_condition ~   chills + cough + loss_smell_taste +  shortness_breath +
                              sputum + chest_pain, data = lung_condition_data, family = binomial)

summary(lung_condition_model)

exp(cbind(OR = coef(lung_condition_model), confint(lung_condition_model)))


vif(lung_condition_model)
```



```{r}
# odds ratio and 95% CL

lung_condition_model_or_ci <- exp(cbind(OR = coef(lung_condition_model), confint(lung_condition_model)))

lung_condition_model_or_ci
```



```{r}
lung_condition_model_pval <- summary(lung_condition_model)$coefficients[,4]



lung_condition_model_padj <- p.adjust(lung_condition_model_pval, method = "bonferroni")

lung_condition_model_padj
```


OR, CI and pval adjusted  
```{r}

lung_condition_model_or_ci_pval <- cbind(lung_condition_model_or_ci, data.frame(pvalues = lung_condition_model_padj))

knitr::kable(lung_condition_model_or_ci_pval)
```


Multicolinearity 

```{r}
vif(lung_condition_model)
```


