---
title: "hypertension_18082020_60plus"
author: "Gabriel Burcea"
date: "14/09/2020"
output: word_document
---
```{r  include=FALSE, echo=TRUE}

library(tidyverse)
library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(qgraph)
library(report)
library(corrplot)
library(rms)

conflict_prefer("step", "stats")

### ML for Mixed - categorical and numerica data ####

```



```{r sympt-pos}

data_categ_nosev <- readr::read_csv("/Users/gabrielburcea/rprojects/data/your.md/cleaned_data_18_08_2020_fully_cleaned_uniq_comorb.csv")


covid_tested_levels <- c("positive" = "showing symptoms")

data_age_band <- data_categ_nosev %>%
   dplyr::mutate(age_band = dplyr::case_when(
     age == 0 | age <= 19 ~ '0-19',
     age == 20 | age <= 39 ~ '20-39',
     age == 40 | age <= 59 ~ '40-59',
     age >= 60 ~ "60+")) %>%
  dplyr::filter(number_morbidities <= 1) %>%
  dplyr::mutate(covid_tested = forcats::fct_recode(covid_tested, !!!covid_tested_levels))


data_covid_only <- data_age_band %>%
#dplyr::filter(number_morbidities <= 1) %>% # added this line on the 09/09/2020 as I want to check the analysis - do I get a different output, See report delivered  ...  compare this with the previous report generated on the date ....
  dplyr::select(id, age, gender, covid_tested, chills, cough, diarrhoea, fatigue, headache, loss_smell_taste, muscle_ache,
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, loss_appetite, chest_pain, itchy_eyes, joint_pain, 
                asthma, diabetes_type_one, diabetes_type_two, obesity, hypertension, heart_disease, lung_condition, liver_disease, kidney_disease, age_band, number_morbidities)%>% 
  dplyr::filter(covid_tested != "negative") %>%
  tidyr::drop_na()


data_age <- data_covid_only %>% 
  dplyr::filter(age_band == "60+")


data_categ_covid <- data_age %>%
  #dplyr::filter(number_morbidities <= 1) %>% # added this line on the 09/09/2020 as I want to check the analysis - do I get a different output, See report delivered  ...  compare this with the previous report generated on the date ....
 dplyr::select(id, age, gender, covid_tested, chills, cough, diarrhoea, fatigue, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, loss_appetite, chest_pain, itchy_eyes, joint_pain, 
                asthma, diabetes_type_one, diabetes_type_two, obesity, hypertension, heart_disease, lung_condition, liver_disease, kidney_disease) %>%
  dplyr::filter(covid_tested != "negative") %>%
  tidyr::drop_na()


```



```{r}
data_categ_covid$country <- NULL
data_categ_covid$location <- NULL
data_categ_covid$date_completed <- NULL
data_categ_covid$covid_tested <- NULL 
data_categ_covid$age_band <- NULL
data_categ_covid$status_cv <- NULL
data_categ_covid$sneezing <- NULL


###########################################################################################
### Transforming variables in factor format ###############################################
#data_categ_covid$country <- as.factor(data_categ_covid$country)
data_categ_covid$chills <- as.factor(data_categ_covid$chills)
data_categ_covid$cough  <- as.factor(data_categ_covid$cough)
data_categ_covid$gender <- as.factor(data_categ_covid$gender)
#data_categ_covid$covid_tested <- as.factor(data_categ_covid$covid_tested)
data_categ_covid$diarrhoea  <- as.factor(data_categ_covid$diarrhoea)
data_categ_covid$fatigue  <- as.factor(data_categ_covid$fatigue)
data_categ_covid$headache   <- as.factor(data_categ_covid$headache)
data_categ_covid$loss_smell_taste   <- as.factor(data_categ_covid$loss_smell_taste)
data_categ_covid$muscle_ache  <- as.factor(data_categ_covid$muscle_ache)
data_categ_covid$nasal_congestion <- as.factor(data_categ_covid$nasal_congestion)
data_categ_covid$nausea_vomiting  <- as.factor(data_categ_covid$nausea_vomiting)
#data_categ_covid$self_diagnosis <- as.factor(data_categ_covid$self_diagnosis)
data_categ_covid$shortness_breath <- as.factor(data_categ_covid$shortness_breath)
data_categ_covid$sore_throat <- as.factor(data_categ_covid$sore_throat)
data_categ_covid$sputum <- as.factor(data_categ_covid$sputum)
data_categ_covid$temperature  <- as.factor(data_categ_covid$temperature)
data_categ_covid$loss_appetite <- as.factor(data_categ_covid$loss_appetite)
data_categ_covid$chest_pain <- as.factor(data_categ_covid$chest_pain)
data_categ_covid$itchy_eyes <- as.factor(data_categ_covid$itchy_eyes)
data_categ_covid$joint_pain <- as.factor(data_categ_covid$joint_pain)


### Transforming variables in numerical format  #########################################################
data_categ_covid$asthma   <- as.factor(data_categ_covid$asthma)
data_categ_covid$diabetes_type_two <- as.factor(data_categ_covid$diabetes_type_two)
data_categ_covid$obesity <- as.factor(data_categ_covid$obesity)
data_categ_covid$hypertension  <- as.factor(data_categ_covid$hypertension)
data_categ_covid$heart_disease  <- as.factor(data_categ_covid$heart_disease)
data_categ_covid$kidney_disease <- as.factor(data_categ_covid$kidney_disease)
data_categ_covid$lung_condition <- as.factor(data_categ_covid$lung_condition)
data_categ_covid$liver_disease <- as.factor(data_categ_covid$liver_disease)
data_categ_covid$diabetes_type_one <- as.factor(data_categ_covid$diabetes_type_one)
#data_categ_covid$covid_tested <- as.factor(data_categ_nose)
```



```{r}

hypertension_data <- data_categ_covid %>%
  dplyr::select(hypertension,  chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, joint_pain, chest_pain, itchy_eyes, loss_appetite) %>%
  tidyr::drop_na()

hypertension_data$hypertension <- as.factor(hypertension_data$hypertension)

```





```{r}
hypertension_count <- hypertension_data %>%
  tidyr::pivot_longer(cols = 2:17, 
                      names_to = "symptoms", 
                      values_to = "yes_no") %>%
  dplyr::filter(hypertension == "Yes" & yes_no == "Yes") %>%
  dplyr::group_by(symptoms) %>%
  dplyr::tally() %>%
  dplyr::mutate(Percentage = n/sum(n)) %>%
  dplyr::arrange(desc(n))

start_date = as.Date("2020-04-09", tz = "Europe/London")
end_date = as.Date("2020-08-18")
title_stub <- "Age group 40-49: Hypertension across symptoms\n"
start_date_title <- format(as.Date(start_date), format = "%d %B %Y")
end_date_title <- format(as.Date(end_date), format = "%d %B %Y")
chart_title <- paste0(title_stub, start_date_title, " to ", end_date_title)

plot_hypertension_sympt <-
  ggplot2::ggplot(hypertension_count, ggplot2::aes(x = reorder(symptoms, - Percentage), y = n, fill = n)) +
  ggplot2::coord_flip() +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::scale_fill_viridis_c(option = "magma", direction = -1) +
  ggplot2::scale_x_discrete(limits = unique(hypertension_count$symptoms)) +
  #ggplot2::theme(legend.position = "bottom") +
  #ggplot2::guides(fill = ggplot2::guide_legend(nrow = 3)) +
  ggplot2::theme_minimal() +
  ggplot2::labs( title = chart_title,
                 subtitle = "Counts of patients with comorbidities accross symptoms",
                 y = "Counts",
                 x = "Symptoms",
                 caption = "Source: Dataset - Your.md Dataset") +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(margin = ggplot2::margin(
      t = 0,
      r = 21,
      b = 0,
      l = 0
    )),
    plot.title = ggplot2::element_text(size = 10, face = "bold"),
    plot.subtitle = ggplot2::element_text(size = 9),
    axis.text.x = ggplot2::element_text(angle = 55, hjust = 1)
  )

plot_hypertension_sympt
```


# Univariate analysis for hypertension and Covid symptoms

Univariate analysis reveal cough, diarrhea, headache, loss of smell and taste, nasal congestion, muscle ache, shortness of breath, joint pain and temperature are Covid-19 symptoms associated in patients with hypertension.


1.Hypertension and chills
```{r }



hypertension_data$hypertension <- as.factor(hypertension_data$hypertension)
hypertension_chills <- glm(hypertension ~ chills, data = hypertension_data, family = binomial)

summary(hypertension_chills)


```



```{r}
coef_hypertension_chills <- coef(hypertension_chills)


```


```{r}
hypertension_chills_or_ci <- exp(cbind(OR = coef(hypertension_chills), confint(hypertension_chills)))
```



P-values adjusted 

```{r}
hypertension_chills_pval <- summary(hypertension_chills)$coefficients[,4]

hypertension_chills_pval <- hypertension_chills_pval[-1]

hypertension_chills_padj <- p.adjust(hypertension_chills_pval, method = "bonferroni")

hypertension_chills_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_chills_or_ci_pval <- cbind(hypertension_chills_or_ci, data.frame(pvalues = hypertension_chills_padj))

knitr::kable(hypertension_chills_or_ci_pval)
```


```{r pressure, echo=FALSE}
hypertension_cough <- glm(hypertension ~ cough, data = hypertension_data, family = binomial)

summary(hypertension_cough)


coef_hypertension_cough <- coef(hypertension_cough)

odd_ratios_ob_co <- exp(coef_hypertension_cough)

odd_ratios_ob_co 
```


```{r}
hypertension_cough_or_ci <- exp(cbind(OR = coef(hypertension_cough), confint(hypertension_cough)))
```




P-values adjusted 

```{r}
hypertension_cough_pval <- summary(hypertension_cough)$coefficients[,4]

hypertension_cough_pval <- hypertension_cough_pval[-1]

hypertension_cough_padj <- p.adjust(hypertension_cough_pval, method = "bonferroni")

hypertension_cough_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_cough_or_ci_pval <- cbind(hypertension_cough_or_ci, data.frame(pvalues = hypertension_cough_padj))

knitr::kable(hypertension_cough_or_ci_pval)
```




```{r}
hypertension_diarrhea <- glm(hypertension ~ diarrhoea, data = hypertension_data, family = binomial)

summary(hypertension_diarrhea)


# get coef
coef_ob_diarrhea <- coef(hypertension_diarrhea)

# odd ratios
odd_ratio_ob_diar <- exp(coef_ob_diarrhea)

odd_ratio_ob_diar
```


```{r}
hypertension_diarrhea_or_ci <- exp(cbind(OR = coef(hypertension_diarrhea), confint(hypertension_diarrhea)))
```


P-values adjusted 

```{r}
hypertension_diarrhea_pval <- summary(hypertension_diarrhea)$coefficients[,4]

hypertension_diarrhea_pval <- hypertension_diarrhea_pval[-1]

hypertension_diarrhea_padj <- p.adjust(hypertension_diarrhea_pval, method = "bonferroni")

hypertension_diarrhea_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_diarrhea_or_ci_pval <- cbind(hypertension_diarrhea_or_ci, data.frame(pvalues = hypertension_diarrhea_padj))

knitr::kable(hypertension_diarrhea_or_ci_pval)
```




```{r}
hypertension_headache <- glm(hypertension ~ headache, data = hypertension_data, family = binomial)

summary(hypertension_headache)

```

OR and CI 
```{r}
hypertension_headache_or_ci <- exp(cbind(OR = coef(hypertension_headache), confint(hypertension_headache)))
```



P-values adjusted 

```{r}
hypertension_headache_pval <- summary(hypertension_headache)$coefficients[,4]

hypertension_headache_pval <- hypertension_headache_pval[-1]

hypertension_headache_padj <- p.adjust(hypertension_headache_pval, method = "bonferroni")

hypertension_headache_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_headache_or_ci_pval <- cbind(hypertension_headache_or_ci, data.frame(pvalues = hypertension_headache_padj))

knitr::kable(hypertension_headache_or_ci_pval)
```






```{r}

hypertension_loss_smell <- glm(hypertension ~ loss_smell_taste, data = hypertension_data, family = binomial)


summary(hypertension_loss_smell)


```


OR and CI 
```{r}
hypertension_loss_smell_or_ci <-    exp(cbind(OR = coef(hypertension_loss_smell), confint(hypertension_loss_smell)))
```





```{r}
hypertension_loss_smell_pval <- summary(hypertension_loss_smell)$coefficients[,4]

hypertension_loss_smell_pval <- hypertension_loss_smell_pval[-1]

hypertension_loss_smell_padj <- p.adjust(hypertension_loss_smell_pval, method = "bonferroni")

hypertension_loss_smell_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_loss_smell_or_ci_pval <- cbind(hypertension_loss_smell_or_ci, data.frame(pvalues = hypertension_loss_smell_padj))

knitr::kable(hypertension_loss_smell_or_ci_pval)
```





```{r}
library(fmsb)

hypertension_muscle_ache <- glm(hypertension ~ muscle_ache, data = hypertension_data, family = binomial)
 
summary(hypertension_muscle_ache)




coef_ob_muscle_ac <- coef(hypertension_muscle_ache)

odd_ratio_ob_los <- exp(coef_ob_muscle_ac)

odd_ratio_ob_los

```


OR and CI 
```{r}
hypertension_muscle_ache_or_ci <- exp(cbind(OR = coef(hypertension_muscle_ache), confint(hypertension_muscle_ache)))
```




```{r}
hypertension_muscle_ache_pval <- summary(hypertension_muscle_ache)$coefficients[,4]

hypertension_muscle_ache_pval <- hypertension_muscle_ache_pval[-1]

hypertension_muscle_ache_padj <- p.adjust(hypertension_muscle_ache_pval, method = "bonferroni")

hypertension_muscle_ache_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_muscle_ache_or_ci_pval <- cbind(hypertension_muscle_ache_or_ci, data.frame(pvalues = hypertension_muscle_ache_padj))

knitr::kable(hypertension_muscle_ache_or_ci_pval)
```



```{r}

hypertension_nasal_cong <- glm(hypertension ~ nasal_congestion, data = hypertension_data, family = binomial)

summary(hypertension_nasal_cong)


coef_ob_nas_cong <- coef(hypertension_nasal_cong)

odd_ratio_ob_nas_cong <- exp(coef_ob_nas_cong)

odd_ratio_ob_nas_cong
```



OR and CI 
```{r}
hypertension_nasal_cong_or_ci <- exp(cbind(OR = coef(hypertension_nasal_cong), confint(hypertension_nasal_cong)))
```



```{r}
hypertension_nasal_cong_pval <- summary(hypertension_nasal_cong)$coefficients[,4]

hypertension_nasal_cong_pval <- hypertension_nasal_cong_pval[-1]

hypertension_nasal_cong_padj <- p.adjust(hypertension_nasal_cong_pval, method = "bonferroni")

hypertension_nasal_cong_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_nasal_cong_or_ci_pval <- cbind(hypertension_nasal_cong_or_ci, data.frame(pvalues = hypertension_nasal_cong_padj))

knitr::kable(hypertension_nasal_cong_or_ci_pval)
```




```{r}

hypertension_nausea_vomitting <- glm(hypertension ~ nausea_vomiting, data = hypertension_data, family = binomial)

summary(hypertension_nausea_vomitting)


coef_ob_naus_vom <- coef(hypertension_nausea_vomitting)

odd_ratio_ob_naus_vom <- exp(coef_ob_naus_vom)

odd_ratio_ob_naus_vom
```


OR and CI 
```{r}
hypertension_nausea_vomitting_or_ci <- exp(cbind(OR = coef(hypertension_nausea_vomitting), confint(hypertension_nausea_vomitting)))
```



```{r}
hypertension_nausea_vomitting_pval <- summary(hypertension_nausea_vomitting)$coefficients[,4]

hypertension_nausea_vomitting_pval <- hypertension_nausea_vomitting_pval[-1]

hypertension_nausea_vomitting_padj <- p.adjust(hypertension_nausea_vomitting_pval, method = "bonferroni")

hypertension_nausea_vomitting_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_nausea_vomitting_or_ci_pval <- cbind(hypertension_nausea_vomitting_or_ci, data.frame(pvalues = hypertension_nausea_vomitting_padj))

knitr::kable(hypertension_nausea_vomitting_or_ci_pval)
```





```{r}

hypertension_short_breath <- glm(hypertension ~ shortness_breath, data = hypertension_data, family = binomial)

summary(hypertension_short_breath)


```


OR and CI 
```{r}
hypertension_short_breath_or_ci <- exp(cbind(OR = coef(hypertension_short_breath), confint(hypertension_short_breath)))
```




```{r}
hypertension_short_breath_pval <- summary(hypertension_short_breath)$coefficients[,4]

hypertension_short_breath_pval <- hypertension_short_breath_pval[-1]

hypertension_short_breath_padj <- p.adjust(hypertension_short_breath_pval, method = "bonferroni")

hypertension_short_breath_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_short_breath_or_ci_pval <- cbind(hypertension_short_breath_or_ci, data.frame(pvalues = hypertension_short_breath_padj))

knitr::kable(hypertension_short_breath_or_ci_pval)
```







```{r}

hypertension_sore_thr <- glm(hypertension ~ sore_throat, data = hypertension_data, family = binomial)

summary(hypertension_sore_thr)

```



OR and CI 
```{r}
hypertension_sore_thr_or_ci <- exp(cbind(OR = coef(hypertension_sore_thr), confint(hypertension_sore_thr)))
```




```{r}
hypertension_sore_thr_pval <- summary(hypertension_sore_thr)$coefficients[,4]

hypertension_sore_thr_pval <- hypertension_sore_thr_pval[-1]

hypertension_sore_thr_padj <- p.adjust(hypertension_sore_thr_pval, method = "bonferroni")

hypertension_sore_thr_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_sore_thr_or_ci_pval <- cbind(hypertension_sore_thr_or_ci, data.frame(pvalues = hypertension_sore_thr_padj))

knitr::kable(hypertension_sore_thr_or_ci_pval)
```






```{r}
hypertension_sputum <- glm(hypertension ~ sputum, data = hypertension_data, family = binomial)


summary(hypertension_sputum)


```



OR and CI 
```{r}
hypertension_sputum_or_ci <- exp(cbind(OR = coef(hypertension_sputum), confint(hypertension_sputum)))
```




```{r}
hypertension_sputum_pval <- summary(hypertension_sputum)$coefficients[,4]

hypertension_sputum_pval <- hypertension_sputum_pval[-1]

hypertension_sputum_padj <- p.adjust(hypertension_sputum_pval, method = "bonferroni")

hypertension_sputum_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_sputum_or_ci_pval <- cbind(hypertension_sputum_or_ci, data.frame(pvalues = hypertension_sputum_padj))

knitr::kable(hypertension_sputum_or_ci_pval)
```


```{r}
hypertension_temperature <- glm(hypertension ~ temperature, data = hypertension_data, family = binomial)


summary(hypertension_temperature)


```



OR and CI 
```{r}
hypertension_temperature_or_ci <- exp(cbind(OR = coef(hypertension_temperature), confint(hypertension_temperature)))
```




```{r}
hypertension_temperature_pval <- summary(hypertension_temperature)$coefficients[,4]

hypertension_temperature_pval <- hypertension_temperature_pval[-1]

hypertension_temperature_padj <- p.adjust(hypertension_temperature_pval, method = "bonferroni")

hypertension_temperature_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_temperature_or_ci_pval <- cbind(hypertension_temperature_or_ci, data.frame(pvalues = hypertension_temperature_padj))

knitr::kable(hypertension_temperature_or_ci_pval)
```



```{r, itchy_eyes}
hypertension_itchy_eyes <- glm(hypertension ~ itchy_eyes, data = hypertension_data, family = binomial)

summary(hypertension_itchy_eyes)

```



OR and CI 
```{r}
hypertension_itchy_eyes_or_ci <- exp(cbind(OR = coef(hypertension_itchy_eyes), confint(hypertension_itchy_eyes)))
```



```{r}
hypertension_itchy_eyes_pval <- summary(hypertension_itchy_eyes)$coefficients[,4]

hypertension_itchy_eyes_pval <- hypertension_itchy_eyes_pval[-1]

hypertension_itchy_eyes_padj <- p.adjust(hypertension_itchy_eyes_pval, method = "bonferroni")

hypertension_itchy_eyes_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_itchy_eyes_or_ci_pval <- cbind(hypertension_itchy_eyes_or_ci, data.frame(pvalues = hypertension_itchy_eyes_padj))

knitr::kable(hypertension_itchy_eyes_or_ci_pval)
```



```{r, chest_pain}
hypertension_chest_pain <- glm(hypertension ~ chest_pain, data = hypertension_data, family = binomial)

summary(hypertension_chest_pain)
```

OR and CI 
```{r}
hypertension_chest_pain_or_ci <- exp(cbind(OR = coef(hypertension_chest_pain), confint(hypertension_chest_pain)))
```




```{r}
hypertension_chest_pain_pval <- summary(hypertension_chest_pain)$coefficients[,4]

hypertension_chest_pain_pval <- hypertension_chest_pain_pval[-1]

hypertension_chest_pain_padj <- p.adjust(hypertension_chest_pain_pval, method = "bonferroni")

hypertension_chest_pain_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_chest_pain_or_ci_pval <- cbind(hypertension_chest_pain_or_ci, data.frame(pvalues = hypertension_chest_pain_padj))

knitr::kable(hypertension_chest_pain_or_ci_pval)
```



```{r}
hypertension_loss_appetite <- glm(hypertension ~ loss_appetite, data = hypertension_data, family = binomial)

summary(hypertension_loss_appetite)
```


OR and CI 
```{r}
hypertension_loss_appetite_or_ci <- exp(cbind(OR = coef(hypertension_loss_appetite), confint(hypertension_loss_appetite)))
```




```{r}
hypertension_loss_appetite_pval <- summary(hypertension_loss_appetite)$coefficients[,4]

hypertension_loss_appetite_pval <- hypertension_loss_appetite_pval[-1]

hypertension_loss_appetite_padj <- p.adjust(hypertension_loss_appetite_pval, method = "bonferroni")

hypertension_loss_appetite_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_loss_appetite_or_ci_pval <- cbind(hypertension_loss_appetite_or_ci, data.frame(pvalues = hypertension_loss_appetite_padj))

knitr::kable(hypertension_loss_appetite_or_ci_pval)
```



```{r, joint_pain}
hypertension_joint_pain <- glm(hypertension ~ joint_pain, data = hypertension_data, family = binomial)


summary(hypertension_joint_pain)
```



OR and CI 
```{r}
hypertension_joint_pain_or_ci <- exp(cbind(OR = coef(hypertension_joint_pain), confint(hypertension_joint_pain)))
```



```{r}
hypertension_joint_pain_pval <- summary(hypertension_joint_pain)$coefficients[,4]

hypertension_joint_pain_pval <- hypertension_joint_pain_pval[-1]

hypertension_joint_pain_padj <- p.adjust(hypertension_joint_pain_pval, method = "bonferroni")

hypertension_joint_pain_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_joint_pain_or_ci_pval <- cbind(hypertension_joint_pain_or_ci, data.frame(pvalues = hypertension_joint_pain_padj))

knitr::kable(hypertension_joint_pain_or_ci_pval)
```



# Multivariable analysis for hypertension 


Adding all variables that showed an association with the hypertension variable. 

When adjusting for all variables,  patients showing covid-19 symptoms/of patients with positive covid test, the results show strong evidence for an association between variables such as cough,  muscle ache, shortness of breath, sputum and temperature (37.1- 38 ; 38.1-39) (p ≤ 0.05) in patients with hypertension.  
When adjusting for all variables,in patients showing covid-19 symptpms/of patients with positive covid test, in patients with hypertension there was: 
- 24 % increase in odds of experiencing cough  compared to those who do not suffer of hypertension
- 15 % increase in diarrhea compared to those who do not suffer of hypertension
- 12 % increase in muscle ache compared to those who do not suffer of hypertension
- 5 % increase in sputum compared to those who do not suffer of hypertension
- 51 % increase in 38.1-39 in temperature to those who do not suffer of hypertension
- 21 % increase in 39.1-41 in temperature compared to those who do not suffer of hypertension


Multivariable analysis for hypertension

When adjusting for all variables that showed to be associated with hypertension, patients showing covid-19 symptoms/of patients with positive Covid -19 test, the results show strong evidence for an association with: joint pain, muscle ache, diarrhea, cough (p < 0.5).



```{r}
hypertension_model <- glm(hypertension ~  chills + headache + loss_smell_taste + nausea_vomiting + shortness_breath + 
                            sore_throat + sputum + loss_appetite + joint_pain,   data = hypertension_data, family = binomial)

summary(hypertension_model)

```


```{r}
# odds ratio and 95% CL

hypertension_model_or_ci <- exp(cbind(OR = coef(hypertension_model), confint(hypertension_model)))

hypertension_model_or_ci
```



```{r}
hypertension_model_pval <- summary(hypertension_model)$coefficients[,4]



hypertension_model_padj <- p.adjust(hypertension_model_pval, method = "bonferroni")

hypertension_model_padj
```


OR, CI and pval adjusted  
```{r}

hypertension_model_or_ci_pval <- cbind(hypertension_model_or_ci, data.frame(pvalues = hypertension_model_padj))

knitr::kable(hypertension_model_or_ci_pval)
```


Multicolinearity 

```{r}
vif(hypertension_model)
```



