---
title: "Diabetest_type_two_18_08_2020_data"
author: "Gabriel Burcea"
date: "04/09/2020"
output: word_document
---



```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
library(tidyverse)
library(magrittr)
```



```{r sympt-pos}

data_categ_nosev <- readr::read_csv("/Users/gabrielburcea/rprojects/data/your.md/cleaned_data_18_08_2020_fully_cleaned_uniq_comorb.csv")

data_categ_covid <- data_categ_nosev %>%
  dplyr::filter(covid_tested != 'none') %>%
  dplyr::mutate(status_cv = dplyr::case_when(covid_tested == 'showing symptoms' ~ 0,
                                             covid_tested == 'positive' ~ 1)) %>%
  tidyr::drop_na()

```



```{r}
data_categ_covid$country <- NULL
data_categ_covid$location <- NULL
data_categ_covid$date_completed <- NULL
data_categ_covid$covid_tested <- NULL 
data_categ_covid$age_band <- NULL
data_categ_covid$status_cv <- NULL
data_categ_covid$sneezing <- NULL


###########################################################################################
### Transforming variables in factor format ###############################################
#data_categ_covid$country <- as.factor(data_categ_covid$country)
data_categ_covid$chills <- as.factor(data_categ_covid$chills)
data_categ_covid$cough  <- as.factor(data_categ_covid$cough)
data_categ_covid$gender <- as.factor(data_categ_covid$gender)
#data_categ_covid$covid_tested <- as.factor(data_categ_covid$covid_tested)
data_categ_covid$diarrhoea  <- as.factor(data_categ_covid$diarrhoea)
data_categ_covid$fatigue  <- as.factor(data_categ_covid$fatigue)
data_categ_covid$headache   <- as.factor(data_categ_covid$headache)
data_categ_covid$loss_smell_taste   <- as.factor(data_categ_covid$loss_smell_taste)
data_categ_covid$muscle_ache  <- as.factor(data_categ_covid$muscle_ache)
data_categ_covid$nasal_congestion <- as.factor(data_categ_covid$nasal_congestion)
data_categ_covid$nausea_vomiting  <- as.factor(data_categ_covid$nausea_vomiting)
data_categ_covid$self_diagnosis <- as.factor(data_categ_covid$self_diagnosis)
data_categ_covid$shortness_breath <- as.factor(data_categ_covid$shortness_breath)
data_categ_covid$sore_throat <- as.factor(data_categ_covid$sore_throat)
data_categ_covid$sputum <- as.factor(data_categ_covid$sputum)
data_categ_covid$temperature  <- as.factor(data_categ_covid$temperature)
data_categ_covid$loss_appetite <- as.factor(data_categ_covid$loss_appetite)
data_categ_covid$chest_pain <- as.factor(data_categ_covid$chest_pain)
data_categ_covid$itchy_eyes <- as.factor(data_categ_covid$itchy_eyes)
data_categ_covid$joint_pain <- as.factor(data_categ_covid$joint_pain)


### Transforming variables in numerical format  #########################################################
data_categ_covid$asthma   <- as.factor(data_categ_covid$asthma)
data_categ_covid$diabetes_type_two <- as.factor(data_categ_covid$diabetes_type_two)
data_categ_covid$obesity <- as.factor(data_categ_covid$obesity)
data_categ_covid$hypertension  <- as.factor(data_categ_covid$hypertension)
data_categ_covid$heart_disease  <- as.factor(data_categ_covid$heart_disease)
data_categ_covid$kidney_disease <- as.factor(data_categ_covid$kidney_disease)
data_categ_covid$lung_condition <- as.factor(data_categ_covid$lung_condition)
data_categ_covid$liver_disease <- as.factor(data_categ_covid$liver_disease)
data_categ_covid$diabetes_type_one <- as.factor(data_categ_covid$diabetes_type_one)
#data_categ_covid$covid_tested <- as.factor(data_categ_nose)
```



```{r  include=FALSE, echo=TRUE}


library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(qgraph)
library(report)
library(corrplot)
library(rms)

conflict_prefer("step", "stats")

### ML for Mixed - categorical and numerica data ####

```



```{r diabetes_type_two_data}
diabetes_type_two_data <- data_categ_covid %>%
  dplyr::select(diabetes_type_two,  chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, joint_pain, chest_pain, itchy_eyes, loss_appetite) %>%
  tidyr::drop_na()
```



```{r}
diabetes_two_count <- diabetes_type_two_data %>%
  tidyr::pivot_longer(cols = 2:17, 
                      names_to = "symptoms", 
                      values_to = "yes_no") %>%
  dplyr::filter(diabetes_type_two == "Yes" & yes_no == "Yes") %>%
  dplyr::group_by(symptoms) %>%
  dplyr::tally() %>%
  dplyr::mutate(Percentage = n/sum(n)) %>%
  dplyr::arrange(desc(n))

start_date = as.Date("2020-04-09", tz = "Europe/London")
end_date = as.Date("2020-08-18")
title_stub <- "Diabetes type two across symptoms\n"
start_date_title <- format(as.Date(start_date), format = "%d %B %Y")
end_date_title <- format(as.Date(end_date), format = "%d %B %Y")
chart_title <- paste0(title_stub, start_date_title, " to ", end_date_title)

plot_diabetes_two_sympt <-
  ggplot2::ggplot(diabetes_two_count, ggplot2::aes(x = reorder(symptoms, - Percentage), y = n, fill = n)) +
  ggplot2::coord_flip() +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::scale_fill_viridis_c(option = "magma", direction = -1) +
  ggplot2::scale_x_discrete(limits = unique(diabetes_two_count$symptoms)) +
  #ggplot2::theme(legend.position = "bottom") +
  #ggplot2::guides(fill = ggplot2::guide_legend(nrow = 3)) +
  ggplot2::theme_minimal() +
  ggplot2::labs( title = chart_title,
                 subtitle = "Counts of patients with comorbidities accross symptoms",
                 y = "Counts",
                 x = "Symptoms",
                 caption = "Source: Dataset - Your.md Dataset") +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(margin = ggplot2::margin(
      t = 0,
      r = 21,
      b = 0,
      l = 0
    )),
    plot.title = ggplot2::element_text(size = 10, face = "bold"),
    plot.subtitle = ggplot2::element_text(size = 9),
    axis.text.x = ggplot2::element_text(angle = 55, hjust = 1)
  )

plot_diabetes_two_sympt
```





## Univariate analysis for diabetes type one
Univariate analysis reveal Covid symptoms such as headaches, shortness of breath, sore throat, sputum and temperature are associated wit diabetes type two respondents.

1. Diabetes type two 

```{r diabetes_type_two_chills}

diabetes_type_two_chills <- glm(diabetes_type_two ~ chills, data = diabetes_type_two_data, family = binomial)

summary(diabetes_type_two_chills)


coef_diabetes_type_two_chills <- coef(diabetes_type_two_chills)

# odd ratios 
odd_ratios_ob_ch <- exp(coef_diabetes_type_two_chills)
odd_ratios_ob_ch 

```


```{r}

knitr::kable(exp(cbind(OR = coef(diabetes_type_two_chills), confint(diabetes_type_two_chills)))) 
```




```{r diabetes_type_two_cough,echo=FALSE}
diabetes_type_two_cough <- glm(diabetes_type_two ~ cough, data = diabetes_type_two_data, family = binomial)

summary(diabetes_type_two_cough)


coef_diabetes_type_two_cough <- coef(diabetes_type_two_cough)

odd_ratios_ob_co <- exp(coef_diabetes_type_two_cough)

odd_ratios_ob_co 
```


```{r}

knitr::kable(exp(cbind(OR = coef(diabetes_type_two_cough), confint(diabetes_type_two_cough)))) 


```




```{r, diabetes_type_two_diarrhea}
diabetes_type_two_diarrhea <- glm(diabetes_type_two ~ diarrhoea, data = diabetes_type_two_data, family = binomial)

summary(diabetes_type_two_diarrhea)


# get coef
coef_ob_diarrhea <- coef(diabetes_type_two_diarrhea)

# odd ratios
odd_ratio_ob_diar <- exp(coef_ob_diarrhea)

odd_ratio_ob_diar
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_two_diarrhea), confint(diabetes_type_two_diarrhea)))) 
```




```{r}
diabetes_type_two_headache <- glm(diabetes_type_two ~ headache, data = diabetes_type_two_data, family = binomial)

summary(diabetes_type_two_headache)

coef_ob_head <- coef(diabetes_type_two_headache)

odd_ratio_ob_head <- exp(coef_ob_head)

odd_ratio_ob_head
```



```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_two_headache), confint(diabetes_type_two_headache)))) 
```





```{r}

diabetes_type_two_loss_smell <- glm(diabetes_type_two ~ loss_smell_taste, data = diabetes_type_two_data, family = binomial)


summary(diabetes_type_two_loss_smell)

coef_ob_loss_smell <- coef(diabetes_type_two_loss_smell)

odd_ratio_ob_los <- exp(coef_ob_loss_smell)

odd_ratio_ob_los
```



```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_two_loss_smell), confint(diabetes_type_two_loss_smell)))) 
```




```{r}


diabetes_type_two_muscle_ache <- glm(diabetes_type_two ~ muscle_ache, data = diabetes_type_two_data, family = binomial)
 
summary(diabetes_type_two_muscle_ache)

coef_ob_muscle_ac <- coef(diabetes_type_two_muscle_ache)

odd_ratio_ob_los <- exp(coef_ob_muscle_ac)

odd_ratio_ob_los

```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_two_muscle_ache), confint(diabetes_type_two_muscle_ache)))) 
```




```{r}

diabetes_type_two_nasal_cong <- glm(diabetes_type_two ~ nasal_congestion, data = diabetes_type_two_data, family = binomial)

summary(diabetes_type_two_nasal_cong)


coef_ob_nas_cong <- coef(diabetes_type_two_nasal_cong)

odd_ratio_ob_nas_cong <- exp(coef_ob_nas_cong)

odd_ratio_ob_nas_cong
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_two_nasal_cong), confint(diabetes_type_two_nasal_cong)))) 
```





```{r}

diabetes_type_two_nausea_vomitting <- glm(diabetes_type_two ~ nausea_vomiting, data = diabetes_type_two_data, family = binomial)

summary(diabetes_type_two_nausea_vomitting)


coef_ob_naus_vom <- coef(diabetes_type_two_nausea_vomitting)

odd_ratio_ob_naus_vom <- exp(coef_ob_naus_vom)

odd_ratio_ob_naus_vom
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_two_nausea_vomitting), confint(diabetes_type_two_nausea_vomitting)))) 
```




```{r}

diabetes_type_two_short_breath <- glm(diabetes_type_two ~ shortness_breath, data = diabetes_type_two_data, family = binomial)

summary(diabetes_type_two_short_breath)

coef_ob_sh_br <- coef(diabetes_type_two_short_breath)


odd_ratio_ob_sh_br <- exp(coef_ob_sh_br)

odd_ratio_ob_sh_br
```



```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_two_short_breath), confint(diabetes_type_two_short_breath)))) 
```




```{r}

diabetes_type_two_sore_thr <- glm(diabetes_type_two ~ sore_throat, data = diabetes_type_two_data, family = binomial)

summary(diabetes_type_two_sore_thr)

coef_ob_sore_thr <- coef(diabetes_type_two_sore_thr)


odd_ratio_ob_sore_thr <- exp(coef_ob_sore_thr)

odd_ratio_ob_sore_thr
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_two_sore_thr), confint(diabetes_type_two_sore_thr)))) 
```




```{r}
diabetes_type_two_sputum <- glm(diabetes_type_two ~ sputum, data = diabetes_type_two_data, family = binomial)


summary(diabetes_type_two_sputum)


coef_ob_sp <- coef(diabetes_type_two_sputum)

odd_ratio_ob_sp <- exp(coef_ob_sp)

odd_ratio_ob_sp

vif(diabetes_type_two_sputum)
```



```{r}

knitr::kable(exp(cbind(OR = coef(diabetes_type_two_sputum), confint(diabetes_type_two_sputum)))) 
```




```{r}
diabetes_type_two_temperature <- glm(diabetes_type_two ~ temperature, data = diabetes_type_two_data, family = binomial)


summary(diabetes_type_two_temperature)

coef_ob_temp <- coef(diabetes_type_two_temperature)

odd_ratio_ob_temp <- exp(coef_ob_temp)

odd_ratio_ob_temp

vif(diabetes_type_two_temperature)
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_type_two_temperature), confint(diabetes_type_two_temperature)))) 
```


```{r}
diab_two_itchy <- glm(diabetes_type_two ~ itchy_eyes, data = diabetes_type_two_data, family = binomial)

summary(diab_two_itchy)

```


```{r}
knitr::kable(exp(cbind(OR = coef(diab_two_itchy), confint(diab_two_itchy)))) 
```




```{r}
diabetes_two_joint_pain <- glm(diabetes_type_two ~ joint_pain, data = diabetes_type_two_data, family = binomial)

summary(diabetes_two_joint_pain)
```


```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_two_joint_pain), confint(diabetes_two_joint_pain)))) 
```




```{r}
diabetes_two_chest_pain <- glm(diabetes_type_two ~ chest_pain, data = diabetes_type_two_data, family = binomial)

summary(diabetes_two_chest_pain)
```

```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_two_chest_pain), confint(diabetes_two_chest_pain)))) 
```



```{r }
diabetes_two_loss_appetite <- glm(diabetes_type_two ~ loss_appetite, data = diabetes_type_two_data, family = binomial)


summary(diabetes_two_loss_appetite)
```

```{r}
knitr::kable(exp(cbind(OR = coef(diabetes_two_loss_appetite), confint(diabetes_two_loss_appetite)))) 
```
 




## Multivariable analysis for diabetes type two


Adding all variables that showed an association with diabetes type two variable. 

When adjusting for all variables,  patients showing covid-19 symptoms/of patients with positive covid test, the results show strong evidence for an association between variables such as headache, shortness of breath, sore throat, sputum, temperature age and gender (p ≤ 0.05) in patients with heart disease.  
When adjusting for all variables,in patients showing covid-19 symptpms/of patients with positive covid test, in patients with diabetes type two there was: 
- 26 % decrease in odds of experiencing headaches 
- 21 % decrease in shortness of breath 
- 28 % decrease in sputum compared to those who do not suffer of patientss of diabetes type two
- 50 % increase in 37.5-38 temperature compared to those who do not suffer of diabetes type two
- 87 % increase in 38.1-39 temperature compared to those who do not suffer of diabetes type two
- 222 % increase ?? in 39.1-41 temperature
- 79 % for gender ? 


```{r}
diabetes_type_two_model <- glm(diabetes_type_two ~ cough + diarrhoea + headache + muscle_ache + nasal_congestion + nausea_vomiting + sore_throat + sputum +  temperature +  joint_pain +   loss_appetite, data = diabetes_type_two_data, family = binomial)

summary(diabetes_type_two_model)
```



Multicolinearity 

```{r}
vif(diabetes_type_two_model)
```



Odd Ratios and 95 % CL for

```{r}

knitr::kable(exp(cbind(OR = coef(diabetes_type_two_model), confint(diabetes_type_two_model))))


```
