---
title: "Hypertension"
author: "Gabriel Burcea"
date: "04/09/2020"
output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
library(tidyverse)
library(magrittr)
```


```{r}
library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(qgraph)
library(report)
library(corrplot)
library(rms)

conflict_prefer("step", "stats")

### ML for Mixed - categorical and numerica data ####
```


```{r sympt-pos}

data_categ_nosev <- readr::read_csv("/Users/gabrielburcea/rprojects/data/your.md/cleaned_data_18_08_2020_fully_cleaned_uniq_comorb.csv")

data_categ_covid <- data_categ_nosev %>%
  dplyr::filter(covid_tested != 'none') %>%
  dplyr::mutate(status_cv = dplyr::case_when(covid_tested == 'showing symptoms' ~ 0,
                                             covid_tested == 'positive' ~ 1)) %>%
  tidyr::drop_na()

```



```{r}

hypertension_data <- data_categ_covid %>%
  dplyr::select(hypertension,  chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, joint_pain, chest_pain, itchy_eyes, loss_appetite) %>%
  tidyr::drop_na()

hypertension_data$hypertension <- as.factor(hypertension_data$hypertension)

```



```{r}

data_categ_covid$country <- NULL
data_categ_covid$location <- NULL
data_categ_covid$date_completed <- NULL
data_categ_covid$covid_tested <- NULL 
data_categ_covid$age_band <- NULL
data_categ_covid$status_cv <- NULL
data_categ_covid$sneezing <- NULL


###########################################################################################
### Transforming variables in factor format ###############################################
#data_categ_covid$country <- as.factor(data_categ_covid$country)
data_categ_covid$chills <- as.factor(data_categ_covid$chills)
data_categ_covid$cough  <- as.factor(data_categ_covid$cough)
data_categ_covid$gender <- as.factor(data_categ_covid$gender)
#data_categ_covid$covid_tested <- as.factor(data_categ_covid$covid_tested)
data_categ_covid$diarrhoea  <- as.factor(data_categ_covid$diarrhoea)
data_categ_covid$fatigue  <- as.factor(data_categ_covid$fatigue)
data_categ_covid$headache   <- as.factor(data_categ_covid$headache)
data_categ_covid$loss_smell_taste   <- as.factor(data_categ_covid$loss_smell_taste)
data_categ_covid$muscle_ache  <- as.factor(data_categ_covid$muscle_ache)
data_categ_covid$nasal_congestion <- as.factor(data_categ_covid$nasal_congestion)
data_categ_covid$nausea_vomiting  <- as.factor(data_categ_covid$nausea_vomiting)
data_categ_covid$self_diagnosis <- as.factor(data_categ_covid$self_diagnosis)
data_categ_covid$shortness_breath <- as.factor(data_categ_covid$shortness_breath)
data_categ_covid$sore_throat <- as.factor(data_categ_covid$sore_throat)
data_categ_covid$sputum <- as.factor(data_categ_covid$sputum)
data_categ_covid$temperature  <- as.factor(data_categ_covid$temperature)
data_categ_covid$loss_appetite <- as.factor(data_categ_covid$loss_appetite)
data_categ_covid$chest_pain <- as.factor(data_categ_covid$chest_pain)
data_categ_covid$itchy_eyes <- as.factor(data_categ_covid$itchy_eyes)
data_categ_covid$joint_pain <- as.factor(data_categ_covid$joint_pain)


### Transforming variables in numerical format  #########################################################
data_categ_covid$asthma   <- as.factor(data_categ_covid$asthma)
data_categ_covid$diabetes_type_two <- as.factor(data_categ_covid$diabetes_type_two)
data_categ_covid$obesity <- as.factor(data_categ_covid$obesity)
data_categ_covid$hypertension  <- as.factor(data_categ_covid$hypertension)
data_categ_covid$heart_disease  <- as.factor(data_categ_covid$heart_disease)
data_categ_covid$kidney_disease <- as.factor(data_categ_covid$kidney_disease)
data_categ_covid$lung_condition <- as.factor(data_categ_covid$lung_condition)
data_categ_covid$liver_disease <- as.factor(data_categ_covid$liver_disease)
data_categ_covid$diabetes_type_one <- as.factor(data_categ_covid$diabetes_type_one)
#data_categ_covid$covid_tested <- as.factor(data_categ_nose)
```




```{r}
hypertension_count <- hypertension_data %>%
  tidyr::pivot_longer(cols = 2:17, 
                      names_to = "symptoms", 
                      values_to = "yes_no") %>%
  dplyr::filter(hypertension == "Yes" & yes_no == "Yes") %>%
  dplyr::group_by(symptoms) %>%
  dplyr::tally() %>%
  dplyr::mutate(Percentage = n/sum(n)) %>%
  dplyr::arrange(desc(n))

start_date = as.Date("2020-04-09", tz = "Europe/London")
end_date = as.Date("2020-08-18")
title_stub <- "Hypertension across symptoms\n"
start_date_title <- format(as.Date(start_date), format = "%d %B %Y")
end_date_title <- format(as.Date(end_date), format = "%d %B %Y")
chart_title <- paste0(title_stub, start_date_title, " to ", end_date_title)

plot_hypertension_sympt <-
  ggplot2::ggplot(hypertension_count, ggplot2::aes(x = reorder(symptoms, - Percentage), y = n, fill = n)) +
  ggplot2::coord_flip() +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::scale_fill_viridis_c(option = "magma", direction = -1) +
  ggplot2::scale_x_discrete(limits = unique(hypertension_count$symptoms)) +
  #ggplot2::theme(legend.position = "bottom") +
  #ggplot2::guides(fill = ggplot2::guide_legend(nrow = 3)) +
  ggplot2::theme_minimal() +
  ggplot2::labs( title = chart_title,
                 subtitle = "Counts of patients with comorbidities accross symptoms",
                 y = "Counts",
                 x = "Symptoms",
                 caption = "Source: Dataset - Your.md Dataset") +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(margin = ggplot2::margin(
      t = 0,
      r = 21,
      b = 0,
      l = 0
    )),
    plot.title = ggplot2::element_text(size = 10, face = "bold"),
    plot.subtitle = ggplot2::element_text(size = 9),
    axis.text.x = ggplot2::element_text(angle = 55, hjust = 1)
  )

plot_hypertension_sympt
```


# Univariate analysis for hypertension and Covid symptoms

Univariate analysis reveal cough, diarrhea, headache, loss of smell and taste, nasal congestion, muscle ache, shortness of breath, joint pain and temperature are Covid-19 symptoms associated in patients with hypertension.


1.Hypertension and chills

```{r }

hypertension_chills <- glm(hypertension ~ chills, data = hypertension_data, family = binomial)

summary(hypertension_chills)


coef_hypertension_chills <- coef(hypertension_chills)

# odd ratios 
odd_ratios_ob_ch <- exp(coef_hypertension_chills)
odd_ratios_ob_ch 

```



```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_chills), confint(hypertension_chills))))
```






2. Hypertension and cough 
```{r  echo=FALSE}
hypertension_cough <- glm(hypertension ~ cough, data = hypertension_data, family = binomial)

summary(hypertension_cough)


coef_hypertension_cough <- coef(hypertension_cough)

odd_ratios_ob_co <- exp(coef_hypertension_cough)

odd_ratios_ob_co 
```



```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_cough), confint(hypertension_cough))))
```



3. Hypertension and diarrhea 
```{r}
hypertension_diarrhea <- glm(hypertension ~ diarrhoea, data = hypertension_data, family = binomial)

summary(hypertension_diarrhea)


# get coef
coef_ob_diarrhea <- coef(hypertension_diarrhea)

# odd ratios
odd_ratio_ob_diar <- exp(coef_ob_diarrhea)

odd_ratio_ob_diar
```



```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_diarrhea), confint(hypertension_diarrhea))))
```





4. Hypertension and headache
```{r}
hypertension_headache <- glm(hypertension ~ headache, data = hypertension_data, family = binomial)

summary(hypertension_headache)

coef_ob_head <- coef(hypertension_headache)

odd_ratio_ob_head <- exp(coef_ob_head)

odd_ratio_ob_head
```


```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_headache), confint(hypertension_headache))))
```




5. Hypertension and loss of smell and taste 
```{r}

hypertension_loss_smell <- glm(hypertension ~ loss_smell_taste, data = hypertension_data, family = binomial)


summary(hypertension_loss_smell)

coef_ob_loss_smell <- coef(hypertension_loss_smell)

odd_ratio_ob_los <- exp(coef_ob_loss_smell)

odd_ratio_ob_los
```


```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_loss_smell), confint(hypertension_loss_smell))))
```





6. Hypertension and muscle ache

```{r}

hypertension_muscle_ache <- glm(hypertension ~ muscle_ache, data = hypertension_data, family = binomial)
 
summary(hypertension_muscle_ache)

coef_ob_muscle_ac <- coef(hypertension_muscle_ache)

odd_ratio_ob_los <- exp(coef_ob_muscle_ac)

odd_ratio_ob_los

```

```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_muscle_ache), confint(hypertension_muscle_ache))))
```






7. Hypertension and nasal congestion
```{r}

hypertension_nasal_cong <- glm(hypertension ~ nasal_congestion, data = hypertension_data, family = binomial)

summary(hypertension_nasal_cong)


coef_ob_nas_cong <- coef(hypertension_nasal_cong)

odd_ratio_ob_nas_cong <- exp(coef_ob_nas_cong)

odd_ratio_ob_nas_cong
```


```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_nasal_cong), confint(hypertension_nasal_cong))))
```





8. Hypertension and nausea and vomiting 
```{r}

hypertension_nausea_vomitting <- glm(hypertension ~ nausea_vomiting, data = hypertension_data, family = binomial)

summary(hypertension_nausea_vomitting)


coef_ob_naus_vom <- coef(hypertension_nausea_vomitting)

odd_ratio_ob_naus_vom <- exp(coef_ob_naus_vom)

odd_ratio_ob_naus_vom
```


```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_nausea_vomitting), confint(hypertension_nausea_vomitting))))
```




9. Hypertension and shortness of breath

```{r}

hypertension_short_breath <- glm(hypertension ~ shortness_breath, data = hypertension_data, family = binomial)

summary(hypertension_short_breath)

coef_ob_sh_br <- coef(hypertension_short_breath)


odd_ratio_ob_sh_br <- exp(coef_ob_sh_br)

odd_ratio_ob_sh_br
```

```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_short_breath), confint(hypertension_short_breath))))
```






10. Hypertension and sore throat
```{r}

hypertension_sore_thr <- glm(hypertension ~ sore_throat, data = hypertension_data, family = binomial)

summary(hypertension_sore_thr)

coef_ob_sore_thr <- coef(hypertension_sore_thr)


odd_ratio_ob_sore_thr <- exp(coef_ob_sore_thr)

odd_ratio_ob_sore_thr
```


```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_sore_thr), confint(hypertension_sore_thr))))
```





11. Hypertension and sputum 

```{r}
hypertension_sputum <- glm(hypertension ~ sputum, data = hypertension_data, family = binomial)


summary(hypertension_sputum)


coef_ob_sp <- coef(hypertension_sputum)

odd_ratio_ob_sp <- exp(coef_ob_sp)

odd_ratio_ob_sp

vif(hypertension_sputum)
```

```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_sputum), confint(hypertension_sputum))))
```



12. Hypertension and temperature 
```{r}
hypertension_temperature <- glm(hypertension ~ temperature, data = hypertension_data, family = binomial)


summary(hypertension_temperature)

coef_ob_temp <- coef(hypertension_temperature)

odd_ratio_ob_temp <- exp(coef_ob_temp)

odd_ratio_ob_temp

vif(hypertension_temperature)
```

```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_temperature), confint(hypertension_temperature))))
```




```{r}

hypertension_itchy <- glm(hypertension ~ itchy_eyes, data = hypertension_data, family = binomial)


summary(hypertension_itchy)
```


```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_itchy), confint(hypertension_itchy))))
```





```{r}

hypertension_chest_pain <- glm(hypertension ~ chest_pain, data = hypertension_data, family = binomial)

summary(hypertension_chest_pain)
```


```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_chest_pain), confint(hypertension_chest_pain))))
```





```{r}
hypertension_loss_appetite <-glm(hypertension ~ loss_appetite, data = hypertension_data, family = binomial)

summary(hypertension_loss_appetite)

```


```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_loss_appetite), confint(hypertension_loss_appetite))))
```




```{r }
hypertension_joint_pain<-glm(hypertension ~ joint_pain, data = hypertension_data, family = binomial)

summary(hypertension_joint_pain)


```


```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_joint_pain), confint(hypertension_joint_pain))))
```




# Multivariable analysis for hypertension 


Adding all variables that showed an association with the hypertension variable. 

When adjusting for all variables,  patients showing covid-19 symptoms/of patients with positive covid test, the results show strong evidence for an association between variables such as cough,  muscle ache, shortness of breath, sputum and temperature (37.1- 38 ; 38.1-39) (p ≤ 0.05) in patients with hypertension.  
When adjusting for all variables,in patients showing covid-19 symptpms/of patients with positive covid test, in patients with hypertension there was: 
- 24 % increase in odds of experiencing cough  compared to those who do not suffer of hypertension
- 15 % increase in diarrhea compared to those who do not suffer of hypertension
- 12 % increase in muscle ache compared to those who do not suffer of hypertension
- 5 % increase in sputum compared to those who do not suffer of hypertension
- 51 % increase in 38.1-39 in temperature to those who do not suffer of hypertension
- 21 % increase in 39.1-41 in temperature compared to those who do not suffer of hypertension


Multivariable analysis for hypertension

When adjusting for all variables that showed to be associated with hypertension, patients showing covid-19 symptoms/of patients with positive Covid -19 test, the results show strong evidence for an association with: joint pain, muscle ache, diarrhea, cough (p < 0.5).



```{r}
hypertension_model <- glm(hypertension ~ cough + diarrhoea + headache + loss_smell_taste + nasal_congestion + muscle_ache + shortness_breath + joint_pain + temperature + loss_appetite,  data = hypertension_data, family = binomial)

summary(hypertension_model)

```


```{r}
knitr::kable(exp(cbind(OR = coef(hypertension_model), confint(hypertension_model))))
```

Multicolinearity 

```{r}
vif(hypertension_model)
```




