---
title: "Liver_disease_18_08_2020_data"
author: "Gabriel Burcea"
date: "04/09/2020"
output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
library(tidyverse)
library(magrittr)
```


```{r}
library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(qgraph)
library(report)
library(corrplot)
library(rms)

conflict_prefer("step", "stats")

### ML for Mixed - categorical and numerica data ####
```


```{r sympt-pos}

data_categ_nosev <- readr::read_csv("/Users/gabrielburcea/rprojects/data/your.md/cleaned_data_18_08_2020_fully_cleaned_uniq_comorb.csv")

data_categ_covid <- data_categ_nosev %>%
  dplyr::filter(covid_tested != 'none') %>%
  dplyr::mutate(status_cv = dplyr::case_when(covid_tested == 'showing symptoms' ~ 0,
                                             covid_tested == 'positive' ~ 1)) %>%
  tidyr::drop_na()

```




```{r}

data_categ_covid$country <- NULL
data_categ_covid$location <- NULL
data_categ_covid$date_completed <- NULL
data_categ_covid$covid_tested <- NULL 
data_categ_covid$age_band <- NULL
data_categ_covid$status_cv <- NULL
data_categ_covid$sneezing <- NULL


###########################################################################################
### Transforming variables in factor format ###############################################
#data_categ_covid$country <- as.factor(data_categ_covid$country)
data_categ_covid$chills <- as.factor(data_categ_covid$chills)
data_categ_covid$cough  <- as.factor(data_categ_covid$cough)
data_categ_covid$gender <- as.factor(data_categ_covid$gender)
#data_categ_covid$covid_tested <- as.factor(data_categ_covid$covid_tested)
data_categ_covid$diarrhoea  <- as.factor(data_categ_covid$diarrhoea)
data_categ_covid$fatigue  <- as.factor(data_categ_covid$fatigue)
data_categ_covid$headache   <- as.factor(data_categ_covid$headache)
data_categ_covid$loss_smell_taste   <- as.factor(data_categ_covid$loss_smell_taste)
data_categ_covid$muscle_ache  <- as.factor(data_categ_covid$muscle_ache)
data_categ_covid$nasal_congestion <- as.factor(data_categ_covid$nasal_congestion)
data_categ_covid$nausea_vomiting  <- as.factor(data_categ_covid$nausea_vomiting)
data_categ_covid$self_diagnosis <- as.factor(data_categ_covid$self_diagnosis)
data_categ_covid$shortness_breath <- as.factor(data_categ_covid$shortness_breath)
data_categ_covid$sore_throat <- as.factor(data_categ_covid$sore_throat)
data_categ_covid$sputum <- as.factor(data_categ_covid$sputum)
data_categ_covid$temperature  <- as.factor(data_categ_covid$temperature)
data_categ_covid$loss_appetite <- as.factor(data_categ_covid$loss_appetite)
data_categ_covid$chest_pain <- as.factor(data_categ_covid$chest_pain)
data_categ_covid$itchy_eyes <- as.factor(data_categ_covid$itchy_eyes)
data_categ_covid$joint_pain <- as.factor(data_categ_covid$joint_pain)


### Transforming variables in numerical format  #########################################################
data_categ_covid$asthma   <- as.factor(data_categ_covid$asthma)
data_categ_covid$diabetes_type_two <- as.factor(data_categ_covid$diabetes_type_two)
data_categ_covid$obesity <- as.factor(data_categ_covid$obesity)
data_categ_covid$hypertension  <- as.factor(data_categ_covid$hypertension)
data_categ_covid$heart_disease  <- as.factor(data_categ_covid$heart_disease)
data_categ_covid$kidney_disease <- as.factor(data_categ_covid$kidney_disease)
data_categ_covid$lung_condition <- as.factor(data_categ_covid$lung_condition)
data_categ_covid$liver_disease <- as.factor(data_categ_covid$liver_disease)
data_categ_covid$diabetes_type_one <- as.factor(data_categ_covid$diabetes_type_one)
#data_categ_covid$covid_tested <- as.factor(data_categ_nose)
```



```{r}
liver_data <- data_categ_covid %>%
  dplyr::select(liver_disease, chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature, joint_pain, itchy_eyes, chest_pain, loss_appetite) %>%
  tidyr::drop_na()
```

```{r}

liver_count <- liver_data %>%
  tidyr::pivot_longer(cols = 2:17, 
                      names_to = "symptoms", 
                      values_to = "yes_no") %>%
  dplyr::filter(liver_disease == "Yes" & yes_no == "Yes") %>%
  dplyr::group_by(symptoms) %>%
  dplyr::tally() %>%
  dplyr::mutate(Percentage = n/sum(n)) %>%
  dplyr::arrange(desc(n))

start_date = as.Date("2020-04-09", tz = "Europe/London")
end_date = as.Date("2020-08-18")
title_stub <- "Liver disease across symptoms\n"
start_date_title <- format(as.Date(start_date), format = "%d %B %Y")
end_date_title <- format(as.Date(end_date), format = "%d %B %Y")
chart_title <- paste0(title_stub, start_date_title, " to ", end_date_title)

plot_liver_sympt <-
  ggplot2::ggplot(liver_count, ggplot2::aes(x = reorder(symptoms, - Percentage), y = n, fill = n)) +
  ggplot2::coord_flip() +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::scale_fill_viridis_c(option = "magma", direction = -1) +
  ggplot2::scale_x_discrete(limits = unique(liver_count$symptoms)) +
  #ggplot2::theme(legend.position = "bottom") +
  #ggplot2::guides(fill = ggplot2::guide_legend(nrow = 3)) +
  ggplot2::theme_minimal() +
  ggplot2::labs( title = chart_title,
                 subtitle = "Counts of patients with comorbidities accross symptoms",
                 y = "Counts",
                 x = "Symptoms",
                 caption = "Source: Dataset - Your.md Dataset") +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(margin = ggplot2::margin(
      t = 0,
      r = 21,
      b = 0,
      l = 0
    )),
    plot.title = ggplot2::element_text(size = 10, face = "bold"),
    plot.subtitle = ggplot2::element_text(size = 9),
    axis.text.x = ggplot2::element_text(angle = 55, hjust = 1)
  )

plot_liver_sympt

```


# Univariate analysis for liver disease and Covid-19 symptoms

Asociated Covid symptoms in respondents with liver disease are: chills, diarhoea, loss of smell and taste, muscle ache, nasal congestion, nausea and vomiting, sputum and temperature


1. Liver disease and chills 
```{r }

liver_chills <- glm(liver_disease ~ chills, data = liver_data, family = binomial)

summary(liver_chills)


coef_liver_chills <- coef(liver_chills)

# odd ratios 
odd_ratios_ob_ch <- exp(coef_liver_chills)
odd_ratios_ob_ch 

```


```{r}
knitr::kable(exp(cbind(OR = coef(liver_chills), confint(liver_chills))))
```




2. Liver disease and cough

```{r  echo=FALSE}
liver_cough <- glm(liver_disease ~ cough, data = liver_data, family = binomial)

summary(liver_cough)


coef_liver_cough <- coef(liver_cough)

odd_ratios_ob_co <- exp(coef_liver_cough)

odd_ratios_ob_co 
```


```{r}
knitr::kable(exp(cbind(OR = coef(liver_cough), confint(liver_cough))))
```






3. Liver disease and diarhoea 
```{r}
liver_diarrhea <- glm(liver_disease ~ diarrhoea, data = liver_data, family = binomial)

summary(liver_diarrhea)


# get coef
coef_ob_diarrhea <- coef(liver_diarrhea)

# odd ratios
odd_ratio_ob_diar <- exp(coef_ob_diarrhea)

odd_ratio_ob_diar
```


```{r}
knitr::kable(exp(cbind(OR = coef(liver_diarrhea), confint(liver_diarrhea))))
```



4. Liver disease and headache 

```{r}
liver_headache <- glm(liver_disease ~ headache, data = liver_data, family = binomial)

summary(liver_headache)

coef_ob_head <- coef(liver_headache)

odd_ratio_ob_head <- exp(coef_ob_head)

odd_ratio_ob_head
```


```{r}
knitr::kable(exp(cbind(OR = coef(liver_headache), confint(liver_headache))))
```




5. Liver disease and loss of smell and taste

```{r}

liver_loss_smell <- glm(liver_disease ~ loss_smell_taste, data = liver_data, family = binomial)


summary(liver_loss_smell)

coef_ob_loss_smell <- coef(liver_loss_smell)

odd_ratio_ob_los <- exp(coef_ob_loss_smell)

odd_ratio_ob_los
```



```{r}
knitr::kable(exp(cbind(OR = coef(liver_loss_smell), confint(liver_loss_smell))))
```






6. Liver disease and muscle ache
```{r}


liver_muscle_ache <- glm(liver_disease ~ muscle_ache, data = liver_data, family = binomial)
 
summary(liver_muscle_ache)

coef_ob_muscle_ac <- coef(liver_muscle_ache)

odd_ratio_ob_los <- exp(coef_ob_muscle_ac)

odd_ratio_ob_los

```

```{r}
knitr::kable(exp(cbind(OR = coef(liver_muscle_ache), confint(liver_muscle_ache))))
```




7. Liver disease and nasal congestion

```{r}

liver_nasal_cong <- glm(liver_disease ~ nasal_congestion, data = liver_data, family = binomial)

summary(liver_nasal_cong)


coef_ob_nas_cong <- coef(liver_nasal_cong)

odd_ratio_ob_nas_cong <- exp(coef_ob_nas_cong)

odd_ratio_ob_nas_cong
```


```{r}
knitr::kable(exp(cbind(OR = coef(liver_nasal_cong), confint(liver_nasal_cong))))
```




8. Liver disease and vomiting 
```{r}

liver_nausea_vomitting <- glm(liver_disease ~ nausea_vomiting, data = liver_data, family = binomial)

summary(liver_nausea_vomitting)


coef_ob_naus_vom <- coef(liver_nausea_vomitting)

odd_ratio_ob_naus_vom <- exp(coef_ob_naus_vom)

odd_ratio_ob_naus_vom
```


```{r}
knitr::kable(exp(cbind(OR = coef(liver_nausea_vomitting), confint(liver_nausea_vomitting))))
```





9. Liver disease and shortness of breath

```{r}

liver_short_breath <- glm(liver_disease ~ shortness_breath, data = liver_data, family = binomial)

summary(liver_short_breath)

coef_ob_sh_br <- coef(liver_short_breath)


odd_ratio_ob_sh_br <- exp(coef_ob_sh_br)

odd_ratio_ob_sh_br
```


```{r}
knitr::kable(exp(cbind(OR = coef(liver_short_breath), confint(liver_short_breath))))
```



9. Liver disease and sore throat
```{r}

liver_sore_thr <- glm(liver_disease ~ sore_throat, data = liver_data, family = binomial)

summary(liver_sore_thr)

coef_ob_sore_thr <- coef(liver_sore_thr)


odd_ratio_ob_sore_thr <- exp(coef_ob_sore_thr)

odd_ratio_ob_sore_thr
```


```{r}
knitr::kable(exp(cbind(OR = coef(liver_sore_thr), confint(liver_sore_thr))))
```




11. Liver disease and sputum 

```{r}
liver_sputum <- glm(liver_disease ~ sputum, data = liver_data, family = binomial)


summary(liver_sputum)


coef_ob_sp <- coef(liver_sputum)

odd_ratio_ob_sp <- exp(coef_ob_sp)

odd_ratio_ob_sp

vif(liver_sputum)
```


```{r}
knitr::kable(exp(cbind(OR = coef(liver_sputum), confint(liver_sputum))))
```




12. Liver disease and temperature 
```{r}
liver_temperature <- glm(liver_disease ~ temperature, data = liver_data, family = binomial)


summary(liver_temperature)

coef_ob_temp <- coef(liver_temperature)

odd_ratio_ob_temp <- exp(coef_ob_temp)

odd_ratio_ob_temp

vif(liver_temperature)
```


```{r}
knitr::kable(exp(cbind(OR = coef(liver_temperature), confint(liver_temperature))))
```




```{r}
liver_itchy <- glm(liver_disease ~ itchy_eyes, data = liver_data, family = binomial)

summary(liver_itchy)
```

```{r}
knitr::kable(exp(cbind(OR = coef(liver_itchy), confint(liver_itchy))))
```





```{r }

liver_chest <- glm(liver_disease ~ chest_pain, data = liver_data, family = binomial)

summary(liver_chest)

```


```{r}
knitr::kable(exp(cbind(OR = coef(liver_chest), confint(liver_chest))))
```



```{r }

liver_joint_p <- glm(liver_disease ~ joint_pain, data = liver_data, family = binomial)

summary(liver_joint_p)
```



```{r}
knitr::kable(exp(cbind(OR = coef(liver_joint_p), confint(liver_joint_p))))
```





```{r }
liver_loss_apopetite <- glm(liver_disease ~ loss_appetite, data = liver_data, family = binomial)

summary(liver_loss_apopetite)

```



```{r}
knitr::kable(exp(cbind(OR = coef(liver_loss_apopetite), confint(liver_loss_apopetite))))
```



# Multivariate analysis for liver disease   
        
When adjusting for the variables, in patients showing covid-19 symptoms/of patients with positive covid test the results show strong evidence for an association between variables such as chills, nausea and vomiting, and temperature (38.1-39; 39.1-40) (p ≤ 0.05) for patients with liver disease.  
When adjusting for all variables,in patients showing covid-19 symptpms/of patients with positive covid test, in patients with liver disease there was: 
- 103 % increase in odds of experiencing chills  compared to those who do not suffer of liver disease
- 13 % increase in loss of smell and taste compared to those who do not suffer of liver disease
- 15 % increase in muscle ache compred to those who do not suffer of liver disease
- 272 % increase in nausea and vomiting compared to those who do not suffer of liver disease 
-17 % increase in nasal congestion compared to those who do not suffer of liver disease
- 14 % increase in 37.5-38 temperature compared to those who do not suffer of liver disease
- 98 % increase in 38.1-39 temperature compared to those who do not suffer of liver disease
- 338 % increase ?? in 39.1-41 temperature
- 21 % increase in sputum compared to those who do not suffer of liver disease


```{r}
liver_model <- glm(liver_disease ~ chills + cough + loss_smell_taste + muscle_ache +  nasal_congestion + 
                     temperature + chest_pain + joint_pain + loss_appetite, data = liver_data, family = binomial)

summary(liver_model)
```

```{r}
knitr::kable(exp(cbind(OR = coef(liver_model), confint(liver_model))))
```



Multicolinearity 

```{r}
vif(liver_model)
```

