---
title: "Lung_condition_18_08_2020_data"
author: "Gabriel Burcea"
date: "04/09/2020"
output: word_document
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
library(tidyverse)
library(magrittr)
```


```{r}
library(tidymodels)
library(readr)
library(dplyr)
library(corrr)
library(tidyverse)
library(conflicted)
library(tidymodels)
library(ggrepel)
library(corrplot)
library(dplyr)
library(corrr) 
library(themis)
library(rsample)
library(caret)
library(forcats)
library(rcompanion)
library(MASS)
library(pROC)
library(ROCR)
library(data.table)
library(ggplot2)
library(qgraph)
library(report)
library(corrplot)
library(rms)

conflict_prefer("step", "stats")

### ML for Mixed - categorical and numerica data ####
```


```{r sympt-pos}

data_categ_nosev <- readr::read_csv("/Users/gabrielburcea/rprojects/data/your.md/cleaned_data_18_08_2020_fully_cleaned_uniq_comorb.csv")

data_categ_covid <- data_categ_nosev %>%
  dplyr::filter(covid_tested != 'none') %>%
  dplyr::mutate(status_cv = dplyr::case_when(covid_tested == 'showing symptoms' ~ 0,
                                             covid_tested == 'positive' ~ 1)) %>%
  tidyr::drop_na()

```




```{r}

data_categ_covid$country <- NULL
data_categ_covid$location <- NULL
data_categ_covid$date_completed <- NULL
data_categ_covid$covid_tested <- NULL 
data_categ_covid$age_band <- NULL
data_categ_covid$status_cv <- NULL
data_categ_covid$sneezing <- NULL


###########################################################################################
### Transforming variables in factor format ###############################################
#data_categ_covid$country <- as.factor(data_categ_covid$country)
data_categ_covid$chills <- as.factor(data_categ_covid$chills)
data_categ_covid$cough  <- as.factor(data_categ_covid$cough)
data_categ_covid$gender <- as.factor(data_categ_covid$gender)
#data_categ_covid$covid_tested <- as.factor(data_categ_covid$covid_tested)
data_categ_covid$diarrhoea  <- as.factor(data_categ_covid$diarrhoea)
data_categ_covid$fatigue  <- as.factor(data_categ_covid$fatigue)
data_categ_covid$headache   <- as.factor(data_categ_covid$headache)
data_categ_covid$loss_smell_taste   <- as.factor(data_categ_covid$loss_smell_taste)
data_categ_covid$muscle_ache  <- as.factor(data_categ_covid$muscle_ache)
data_categ_covid$nasal_congestion <- as.factor(data_categ_covid$nasal_congestion)
data_categ_covid$nausea_vomiting  <- as.factor(data_categ_covid$nausea_vomiting)
data_categ_covid$self_diagnosis <- as.factor(data_categ_covid$self_diagnosis)
data_categ_covid$shortness_breath <- as.factor(data_categ_covid$shortness_breath)
data_categ_covid$sore_throat <- as.factor(data_categ_covid$sore_throat)
data_categ_covid$sputum <- as.factor(data_categ_covid$sputum)
data_categ_covid$temperature  <- as.factor(data_categ_covid$temperature)
data_categ_covid$loss_appetite <- as.factor(data_categ_covid$loss_appetite)
data_categ_covid$chest_pain <- as.factor(data_categ_covid$chest_pain)
data_categ_covid$itchy_eyes <- as.factor(data_categ_covid$itchy_eyes)
data_categ_covid$joint_pain <- as.factor(data_categ_covid$joint_pain)


### Transforming variables in numerical format  #########################################################
data_categ_covid$asthma   <- as.factor(data_categ_covid$asthma)
data_categ_covid$diabetes_type_two <- as.factor(data_categ_covid$diabetes_type_two)
data_categ_covid$obesity <- as.factor(data_categ_covid$obesity)
data_categ_covid$hypertension  <- as.factor(data_categ_covid$hypertension)
data_categ_covid$heart_disease  <- as.factor(data_categ_covid$heart_disease)
data_categ_covid$kidney_disease <- as.factor(data_categ_covid$kidney_disease)
data_categ_covid$lung_condition <- as.factor(data_categ_covid$lung_condition)
data_categ_covid$liver_disease <- as.factor(data_categ_covid$liver_disease)
data_categ_covid$diabetes_type_one <- as.factor(data_categ_covid$diabetes_type_one)
#data_categ_covid$covid_tested <- as.factor(data_categ_nose)
```



```{r}
lung_condition_data <- data_categ_covid %>%
  dplyr::select(lung_condition, chills, cough, diarrhoea, headache, loss_smell_taste, muscle_ache, 
                nasal_congestion, nausea_vomiting, shortness_breath, sore_throat, sputum, temperature,  joint_pain, chest_pain, itchy_eyes, loss_appetite) %>%
  tidyr::drop_na()
```



```{r}
lung_count <- lung_condition_data %>%
  tidyr::pivot_longer(cols = 2:17, 
                      names_to = "symptoms", 
                      values_to = "yes_no") %>%
  dplyr::filter(lung_condition== "Yes" & yes_no == "Yes") %>%
  dplyr::group_by(symptoms) %>%
  dplyr::tally() %>%
  dplyr::mutate(Percentage = n/sum(n)) %>%
  dplyr::arrange(desc(n))

start_date = as.Date("2020-04-09", tz = "Europe/London")
end_date = as.Date("2020-08-18")
title_stub <- "Lung condition across symptoms\n"
start_date_title <- format(as.Date(start_date), format = "%d %B %Y")
end_date_title <- format(as.Date(end_date), format = "%d %B %Y")
chart_title <- paste0(title_stub, start_date_title, " to ", end_date_title)

plot_lung_sympt <-
  ggplot2::ggplot(lung_count, ggplot2::aes(x = reorder(symptoms, - Percentage), y = n, fill = n)) +
  ggplot2::coord_flip() +
  ggplot2::geom_bar(stat = "identity", position = "dodge") +
  ggplot2::scale_fill_viridis_c(option = "magma", direction = -1) +
  ggplot2::scale_x_discrete(limits = unique(lung_count$symptoms)) +
  #ggplot2::theme(legend.position = "bottom") +
  #ggplot2::guides(fill = ggplot2::guide_legend(nrow = 3)) +
  ggplot2::theme_minimal() +
  ggplot2::labs( title = chart_title,
                 subtitle = "Counts of patients with comorbidities accross symptoms",
                 y = "Counts",
                 x = "Symptoms",
                 caption = "Source: Dataset - Your.md Dataset") +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(margin = ggplot2::margin(
      t = 0,
      r = 21,
      b = 0,
      l = 0
    )),
    plot.title = ggplot2::element_text(size = 10, face = "bold"),
    plot.subtitle = ggplot2::element_text(size = 9),
    axis.text.x = ggplot2::element_text(angle = 55, hjust = 1)
  )

plot_lung_sympt
```


# Univariate analysis for lung condition and Covid-19 symptoms


Univariate logistic regression for lung condition and covid symptoms reveal: 
- nausea and vomiting, shortness of breath, sputum and 39.1- 41 temperature are statistically significant by looking at p values


1. Lung condition and chills

```{r }

lung_condition_chills <- glm(lung_condition ~ chills, data = lung_condition_data, family = binomial)

summary(lung_condition_chills)


coef_lung_condition_chills <- coef(lung_condition_chills)

# odd ratios 
odd_ratios_ob_ch <- exp(coef_lung_condition_chills)
odd_ratios_ob_ch 

```


```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_chills), confint(lung_condition_chills))))
```





2. Lung condition and cough
```{r  echo=FALSE}
lung_condition_cough <- glm(lung_condition ~ cough, data = lung_condition_data, family = binomial)

summary(lung_condition_cough)


coef_lung_condition_cough <- coef(lung_condition_cough)

odd_ratios_ob_co <- exp(coef_lung_condition_cough)

odd_ratios_ob_co 
```


```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_cough), confint(lung_condition_cough))))
```




3. Lung condition and diarhoea
```{r}
lung_condition_diarrhea <- glm(lung_condition ~ diarrhoea, data = lung_condition_data, family = binomial)

summary(lung_condition_diarrhea)


# get coef
coef_ob_diarrhea <- coef(lung_condition_diarrhea)

# odd ratios
odd_ratio_ob_diar <- exp(coef_ob_diarrhea)

odd_ratio_ob_diar
```


```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_diarrhea), confint(lung_condition_diarrhea))))
```



4. Lung condition and headache
```{r}
lung_condition_headache <- glm(lung_condition ~ headache, data = lung_condition_data, family = binomial)

summary(lung_condition_headache)

coef_ob_head <- coef(lung_condition_headache)

odd_ratio_ob_head <- exp(coef_ob_head)

odd_ratio_ob_head
```



```{r}

knitr::kable(exp(cbind(OR = coef(lung_condition_headache), confint(lung_condition_headache))))
```



5. Lung condition and loss of smell and taste

```{r}

lung_condition_loss_smell <- glm(lung_condition ~ loss_smell_taste, data = lung_condition_data, family = binomial)


summary(lung_condition_loss_smell)

coef_ob_loss_smell <- coef(lung_condition_loss_smell)

odd_ratio_ob_los <- exp(coef_ob_loss_smell)

odd_ratio_ob_los
```

```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_loss_smell), confint(lung_condition_loss_smell))))
```



6. Lung condition and muscle ache
```{r}


lung_condition_muscle_ache <- glm(lung_condition ~ muscle_ache, data = lung_condition_data, family = binomial)
 
summary(lung_condition_muscle_ache)

coef_ob_muscle_ac <- coef(lung_condition_muscle_ache)

odd_ratio_ob_los <- exp(coef_ob_muscle_ac)

odd_ratio_ob_los

```

```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_muscle_ache), confint(lung_condition_muscle_ache))))
```


7. Lung condition and nasal congestion

```{r}

lung_condition_nasal_cong <- glm(lung_condition ~ nasal_congestion, data = lung_condition_data, family = binomial)

summary(lung_condition_nasal_cong)


coef_ob_nas_cong <- coef(lung_condition_nasal_cong)

odd_ratio_ob_nas_cong <- exp(coef_ob_nas_cong)

odd_ratio_ob_nas_cong
```



```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_nasal_cong), confint(lung_condition_nasal_cong))))
```



8. Lung condition and nausea and vomiting

```{r}

lung_condition_nausea_vomitting <- glm(lung_condition ~ nausea_vomiting, data = lung_condition_data, family = binomial)

summary(lung_condition_nausea_vomitting)


coef_ob_naus_vom <- coef(lung_condition_nausea_vomitting)

odd_ratio_ob_naus_vom <- exp(coef_ob_naus_vom)

odd_ratio_ob_naus_vom
```


```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_nausea_vomitting), confint(lung_condition_nausea_vomitting))))
```



9. Lung condition and shorthness of breath
```{r}

lung_condition_short_breath <- glm(lung_condition ~ shortness_breath, data = lung_condition_data, family = binomial)

summary(lung_condition_short_breath)

coef_ob_sh_br <- coef(lung_condition_short_breath)


odd_ratio_ob_sh_br <- exp(coef_ob_sh_br)

odd_ratio_ob_sh_br
```


```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_short_breath), confint(lung_condition_short_breath))))
```


10. Lung condition and sore throat
```{r}

lung_condition_sore_thr <- glm(lung_condition ~ sore_throat, data = lung_condition_data, family = binomial)

summary(lung_condition_sore_thr)

coef_ob_sore_thr <- coef(lung_condition_sore_thr)


odd_ratio_ob_sore_thr <- exp(coef_ob_sore_thr)

odd_ratio_ob_sore_thr
```


```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_sore_thr), confint(lung_condition_sore_thr))))
```

11. Lung condition and sputum


```{r}
lung_condition_sputum <- glm(lung_condition ~ sputum, data = lung_condition_data, family = binomial)


summary(lung_condition_sputum)


coef_ob_sp <- coef(lung_condition_sputum)

odd_ratio_ob_sp <- exp(coef_ob_sp)

odd_ratio_ob_sp

vif(lung_condition_sputum)
```


```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_sputum), confint(lung_condition_sputum))))
```



12. Lung condition and temperature

```{r}
lung_condition_temperature <- glm(lung_condition ~ temperature, data = lung_condition_data, family = binomial)


summary(lung_condition_temperature)

coef_ob_temp <- coef(lung_condition_temperature)

odd_ratio_ob_temp <- exp(coef_ob_temp)

odd_ratio_ob_temp

vif(lung_condition_temperature)
```



```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_temperature), confint(lung_condition_temperature))))
```




```{r }
lung_condition_itchy_eyes <- glm(lung_condition ~ itchy_eyes, data = lung_condition_data, family = binomial)

summary(lung_condition_itchy_eyes)

```


```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_itchy_eyes), confint(lung_condition_itchy_eyes))))
```




```{r }

lung_condition_joint_pain <- glm(lung_condition ~ joint_pain, data = lung_condition_data, family = binomial)
summary(lung_condition_joint_pain)
```


```{r }
lung_condition_chest_pain <- glm(lung_condition ~ chest_pain, data = lung_condition_data, family = binomial)

summary(lung_condition_chest_pain)
```


```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_chest_pain), confint(lung_condition_chest_pain))))
```


```{r }
lung_condition_loss_appetite <- glm(lung_condition ~ loss_appetite, data = lung_condition_data, family = binomial)

summary(lung_condition_loss_appetite)

```


```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_loss_appetite), confint(lung_condition_loss_appetite))))
```



```{r}
lung_joint_pain <- glm(lung_condition ~ joint_pain, data = lung_condition_data, family = binomial)

summary(lung_joint_pain)
```


```{r}
knitr::kable(exp(cbind(OR = coef(lung_joint_pain), confint(lung_joint_pain))))
```


# Multivariate analysis for lung condition 


Adding all variables that showed an association with the lung diseease. 

When adjusting for all variables,  patients showing covid-19 symptoms/of patients with positive covid test, the results show strong evidence for an association between variables such as nausea and vomiting, shortness of breath and temperature (38.1-39; 39.1-40) (p ≤ 0.05) and sputum in patients with lung disease.  


When adjusting for the above variables, in patients showing covid-19 symptoms/of patients with positivie covid test, there was:
- 88 % increase in the odds of experiencing nausea and vomiting compared to those who did not have lung disease; 
- 63 % increase in odds of experiencing shortness of breath  compared to those who did not have lung disease;
- 146 % increase in 39.1-41 temperature compared to those who did not have lung disease;
- 33 % increase in the odds of experiencing sputum in patients with lung disease compared to those who did not have lung disease


```{r}
lung_condition_model <- glm(lung_condition ~  chills + cough  + diarrhoea + loss_smell_taste + nausea_vomiting + shortness_breath +
                              sputum + joint_pain + chest_pain , data = lung_condition_data, family = binomial)

summary(lung_condition_model)

exp(cbind(OR = coef(lung_condition_model), confint(lung_condition_model)))


vif(lung_condition_model)
```



```{r}
knitr::kable(exp(cbind(OR = coef(lung_condition_model), confint(lung_condition_model))))
```


Multicolinearity 

```{r}
vif(lung_condition_model)
```

